---
title: "ANLY515 Group Project Saurabh v3"
author: "Saurabh Shirish Prabhu"
date: "`r Sys.Date()`"
output: word_document
---


```{r setup, include=FALSE}
rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE)
dir.create(tempdir())
```

Importing data from Yahoo finance:

```{r}
getwd()
setwd('F:/a_Harrisburg_University_Academics/ANLY 515-51- A-2024Spring - Risk Modeling and Assessment/Final Project/Code')
getwd()
```
This section contains
Part A – Markowitz Mean-Variance Optimization
Part B – Suitable distributions for returns

Select two market sectors from the 11 sectors identified on this
reference o <https://www.bloomberg.com/markets/sectors>

Answer:

[1]Information Technology<br>

1.1 Semiconductors & Semiconductor Equipment: NVIDIA Corporation (NVDA)<br>
1.2 Software & Services: Microsoft Corporation (MSFT)<br>
1.3 Software & Services: Apple Inc. (AAPL)<br>
1.4 Software & Services: Netflix Inc. (NFLX)<br>


[2]Financials<br>

2.1 Insurance: Berkshire Hathaway Inc. (BRK.B)<br>
2.2 Banks: JPMorgan Chase & Co. (JPM)<br>
2.3 Banks: CitiGroup Inc. (C)<br>
2.4 Insurance: BlackRock Inc. (BLK)<br>



[3]Consumer Discretionary:<br>

3.1 Retailing: McDonald's Corporation (MCD)<br>
3.2 Consumer Durables & Apparel: Skechers U.S.A., Inc. (SKX)<br>
3.3 Retailing: Starbucks Corp. (SBUX) <br>
3.4 Consumer Durables & Apparel: Nike Inc. (NKE)



[4]Industrials: <br>

4.1 Capital Goods: Cummins Inc. (CMI)<br>
4.2 Capital Goods:Deere & Company (DE)<br>


References: <br>
[1]<https://stockanalysis.com/stocks/industry/><br>
[2]<https://medium.com/\@sil.soham/importing-and-visualising-stock-market-data-in-r-ac5a22e23cd><br>


Import all necessary libraries

```{r}
library(quantmod)
library(xts)
library(dplyr)
library(corrplot)
```

Load all stocks



• Confirm that there is no missing data<br> 
• Check the dimensions to
verify that the data covers 5 years<br>
```{r}

start <- as.Date("2014-12-31",format="%Y-%m-%d")
end <- as.Date("2023-12-31",format="%Y-%m-%d")

# Use getSymbols to retrieve the data

# [1]Information Technology
data.NVDA <- getSymbols("NVDA", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.MSFT <- getSymbols("MSFT", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.AAPL <- getSymbols("AAPL", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NFLX <- getSymbols("NFLX", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [2]Financials
data.BRK_B <- getSymbols("BRK-B", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.JPM <- getSymbols("JPM", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.C <- getSymbols("C", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.BLK <- getSymbols("BLK", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [3]Consumer Discretionary:
data.MCD <- getSymbols("MCD", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SKX <- getSymbols("SKX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SBUX <- getSymbols("SBUX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NKE <- getSymbols("NKE", src = "yahoo", from = start, to = end, auto.assign = FALSE)
# Assign the class "xts" and "zoo" explicitly
# class(data.NVDA) <- c("xts", "zoo")
# Print the class of the assigned variable
class(data.NVDA)



names(data.BRK_B)
names(data.BRK_B) <- paste(c("BRK_B.Open","BRK_B.High","BRK_B.Low","BRK_B.Close","BRK_B.Volume","BRK_B.Adjusted"))
names(data.BRK_B)

```
```{r}
### Sector 1: Information Technology: MSFT and NVDA
Infotech.Adjusted.Prices <- data.NVDA$NVDA.Adjusted
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.MSFT$MSFT.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.AAPL$AAPL.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.NFLX$NFLX.Adjusted)
# Infotech.Adjusted.Prices[c(1:3,nrow(Infotech.Adjusted.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Adjusted.Prices <- data.BRK_B$BRK_B.Adjusted
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.JPM$JPM.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.C$C.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.BLK$BLK.Adjusted)
# Financials.Adjusted.Prices[c(1:3,nrow(Financials.Adjusted.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Adjusted.Prices <- data.MCD$MCD.Adjusted
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SKX$SKX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SBUX$SBUX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.NKE$NKE.Adjusted)
# Consumer.Adjusted.Prices[c(1:3,nrow(Consumer.Adjusted.Prices)),]


########
### Entire portfolio
Portfolio.Adj.all <- cbind(Infotech.Adjusted.Prices,Financials.Adjusted.Prices,Consumer.Adjusted.Prices)
Portfolio.Adj.all[c(1:3,nrow(Portfolio.Adj.all)),]

str(Portfolio.Adj.all)
summary(Portfolio.Adj.all)
```
Variance covariance matrix: 

Part A – Risks

```{r}

multi <- Portfolio.Adj.all

mat.price <- matrix(multi,nrow(multi))
prc2ret <- function(x) Delt(x)


mat.ret1 <- apply(mat.price,2,function(x) {prc2ret(c(x))})



mat.ret <- mat.ret1[-1,]
colnames(mat.ret1) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
# mat.ret[1:4,]


mat.ret[c(1:2,nrow(mat.ret)),]

# # Create a vector of weights AMZN: 25% IBM: 75%
# 
# WGT.12asset <- rep(1/12, 12)   ###EQUALLY WEIGHTED
# WGT.12asset <- matrix(WGT.12asset,1)
# # WGT.12asset
# # Create a transposed vector of weights (command: t)
# 
# tWGT.12asset <- t(WGT.12asset)
# tWGT.12asset


## Calculate annualize and annualize variance-covariance matrix
VCOV <- cov(mat.ret)
VCOV.annual <- nrow(mat.ret)*VCOV   ## 252 is nrow of mat.ret 
VCOV.annual

# Check the range of values in the covariance matrix
min_value <- min(VCOV.annual)
max_value <- max(VCOV.annual)


# Convert covariance matrix to correlation matrix
COR.annual <- cov2cor(VCOV.annual)
corrplot(COR.annual, method = "circle")
```

Import Returns Data and Convert it Into a Matrix

Calculate return time series 

```{r}
port.df <- data.frame(date = index(Portfolio.Adj.all), coredata(Portfolio.Adj.all))
port.df[c(1:3,nrow(port.df)),]


Port.rets <-port.df
date<-Port.rets$date
# str(date)

PortRet.price <- Port.rets[,-1]


attr(PortRet.price, 'time')<-date   ##add time attribute to dataset
# str(PortRet.price)

prc2ret <- function(x) Delt(x)


Port.rets.all <- apply(PortRet.price,2,function(x) {prc2ret(c(x))})



colnames(Port.rets.all) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )

## Add date column


Port.rets.all = data.frame(Port.rets.all)
Port.rets.all$date <- port.df$date

# summary(PortRet_2013)
# str(PortRet_2013)
# head(PortRet_2013)
attr(Port.rets.all, 'time')<-date
# str(Port.rets.all)
head(Port.rets.all)


### reorder to get date in first column
# Get the index of the 'date' column
date_column_index <- which(names(Port.rets.all) == "date")

# Move 'date' column to the first position
new_order <- c(date_column_index, 1:(ncol(Port.rets.all)-1)[-date_column_index+1])

# Rearrange the columns of the data frame
Port.rets.df <- Port.rets.all[, new_order]
head(Port.rets.df)


```


CORRECT CODE FOR MONTHLY RETURNS




Monthly returns: 

```{r}
# date <- as.Date(data.NVDA$Date,format="%Y-%m-%d")
# NVDA <- cbind(date,data.NVDA[,-1])
# NVDA <- NVDA[order(NVDA$date),]
# NVDA <- xts(NVDA[,2:7],order.by=NVDA[,1])
# names(NVDA) <- paste(c("NVDA.Open","NVDA.High","NVDA.Low","NVDA.Close","NVDA.Volume","NVDA.Adjusted"))

NVDA <- data.NVDA
MSFT <- data.MSFT
AAPL <- data.AAPL
NFLX <- data.NFLX

BRK_B <- data.BRK_B
JPM   <- data.JPM
C     <- data.C
BLK   <- data.BLK

MCD   <- data.MCD
SKX   <- data.SKX
SBUX  <- data.SBUX
NKE   <- data.NKE


NVDA.monthly <- to.monthly(NVDA)
MSFT.monthly <- to.monthly(MSFT)
AAPL.monthly <- to.monthly(AAPL)
NFLX.monthly <- to.monthly(NFLX)

BRK_B.monthly <- to.monthly(BRK_B)
JPM.monthly  <- to.monthly(JPM)
C.monthly     <- to.monthly(C)
BLK.monthly   <- to.monthly(BLK)

MCD.monthly   <- to.monthly(MCD)
SKX.monthly   <- to.monthly(SKX)
SBUX.monthly  <- to.monthly(SBUX)
NKE.monthly   <- to.monthly(NKE)

NVDA.ret <- Delt(NVDA.monthly$NVDA.Adjusted)
MSFT.ret <- Delt(MSFT.monthly$MSFT.Adjusted)
AAPL.ret <- Delt(AAPL.monthly$AAPL.Adjusted)
NFLX.ret <- Delt(NFLX.monthly$NFLX.Adjusted)

names(NVDA.ret) <- paste("NVDA.Ret")
names(MSFT.ret) <- paste("MSFT.Ret")
names(AAPL.ret) <- paste("AAPL.Ret")
names(NFLX.ret) <- paste("NFLX.Ret")

BRK_B.ret <- Delt(BRK_B.monthly$BRK_B.Adjusted)
JPM.ret   <- Delt(JPM.monthly$JPM.Adjusted)
C.ret     <- Delt(C.monthly$C.Adjusted)
BLK.ret   <- Delt(BLK.monthly$BLK.Adjusted)

names(BRK_B.ret) <- paste("BRK_B.Ret")
names(JPM.ret)   <- paste("JPM.Ret")
names(C.ret)     <- paste("C.Ret")
names(BLK.ret)  <- paste("BLK.Ret")

MCD.ret <- Delt(MCD.monthly$MCD.Adjusted)
SKX.ret <- Delt(SKX.monthly$SKX.Adjusted)
SBUX.ret<- Delt(SBUX.monthly$SBUX.Adjusted)
NKE.ret <- Delt(NKE.monthly$NKE.Adjusted)

names(MCD.ret)  <- paste("MCD.Ret")
names(SKX.ret)  <- paste("SKX.Ret")
names(SBUX.ret) <- paste("SBUX.Ret")
names(NKE.ret)  <- paste("NKE.Ret")

Ret.monthly <- cbind(NVDA.ret[-1,],MSFT.ret[-1,],AAPL.ret[-1,],NFLX.ret[-1,],
                     BRK_B.ret[-1,],JPM.ret[-1,],C.ret[-1,],BLK.ret[-1,],
                     MCD.ret[-1,],SKX.ret[-1,],SBUX.ret[-1,],NKE.ret[-1,])
Ret.monthly[c(1:3,nrow(Ret.monthly)),]



# NVDA.ret[c(1:3,nrow(NVDA.ret)),]


```
```{r}
str(Ret.monthly)
summary(Ret.monthly)

# Row names for stocks
stock_names <- c(
  "NVDA", "MSFT", "AAPL", "NFLX",
  "BRK_B", "JPM", "C", "BLK",
  "MCD", "SKX", "SBUX", "NKE"
)

# Plot boxplot with customized axis labels
boxplot(Ret.monthly*100,
        main = "Average Monthly Returns",
        ylab = "Percentage",
        xlab = "Stocks",
        names = stock_names,
        las = 2,
        ylim = c(-50, 50),# Assuming your returns range from -50% to 50%
        yaxt = "n")  # Suppress y-axis ticks)  
# Customize y-axis ticks with "%" symbol
axis(side = 2, at = seq(-50, 50, by = 5), labels = paste0(seq(-50, 50, by = 5), "%"))
# Add horizontal dashed line at 0%
abline(h = 0, lty = 2)
```

Matrix command to convert the combined data into a matrix. We rename the column headers using the colnames command with the relevant ticker to better identify the return series.

```{r}
mat.ret <- matrix(Ret.monthly,nrow(Ret.monthly))
# mat.ret[1:3,]
colnames(mat.ret) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
head(mat.ret,2)
tail(mat.ret,2)


## covariance matrix

VCOV <- cov(mat.ret)
# VCOV

VCOV_rounded <- round(VCOV, digits = 4)

# Display the rounded covariance matrix
VCOV_rounded





## Average erturns
avg.ret <- matrix(apply(mat.ret,2,mean))
rownames(avg.ret) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
colnames(avg.ret) <- c("Avg.Ret")
avg.ret


min.ret <- min(avg.ret)
min.ret
max.ret <- max(avg.ret)
max.ret
```
```{r}
VCOV.annual <- nrow(mat.ret)*VCOV   ## 252 is nrow of mat.ret 
VCOV.annual

# Check the range of values in the covariance matrix
min_value <- min(VCOV.annual)
max_value <- max(VCOV.annual)


# Convert covariance matrix to correlation matrix
COR.annual <- cov2cor(VCOV.annual)
corrplot(COR.annual, method = "circle")




```
Target Portfolio Returns Vector

```{r}
increments=100
tgt.ret <- seq(min.ret,max.ret,length=increments)
head(tgt.ret)


tgt.sd <- rep(0,length=increments)
tgt.sd


wgt <- matrix(0,nrow=increments,ncol=length(avg.ret))
# head(wgt)

# Dmat_cov = round(VCOV*2,5)
# Run the quadrpog Optimizer
library(quadprog)
for (i in 1:increments){
  Dmat <- 2*VCOV  ## 2*VCOV
  dvec <- c(rep(0,length(avg.ret)))
  Amat <- cbind(rep(1,length(avg.ret)),avg.ret,
                diag(1,nrow=ncol(Ret.monthly)))
  bvec <- c(1,tgt.ret[i],rep(0,ncol(Ret.monthly)))
  
  soln <- solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=2)
  
  tgt.sd[i] <- sqrt(soln$value)
  wgt[i,] <- soln$solution
}


head(tgt.sd)
head(wgt)
```




```{r}


colnames(wgt) <- paste(c("wgt.NVDA", "wgt.MSFT", "wgt.AAPL", "wgt.NFLX",
                         "wgt.BRK_B",  "wgt.JPM", "wgt.C",  "wgt.BLK",
                         "wgt.MCD",  "wgt.SKX", "wgt.SBUX",  "wgt.NKE"))
head(wgt)
CHECK <- rowSums(wgt)
CHECK


tgt.port <- data.frame(cbind(tgt.ret,tgt.sd,wgt))
head(tgt.port)

```
## Minimum Variance Portfolio

```{r min variance portfolio}

minvar.port <- subset(tgt.port,tgt.port$tgt.sd==min(tgt.port$tgt.sd))
minvar.port


# The Sharpe Ratio requires a risk-free rate and we use the 3-Month Constant Maturity Treasury as a proxy for that rate. Since the yield as of December 31, 2013 of 0.07% is an annual yield, we convert this to a monthly yield by dividing the rate by 12.
# 
# December 31, 2023 of 5.4%   - reference: https://fred.stlouisfed.org/series/DGS3MO

riskfree = .054/12
riskfree

tgt.port$Sharpe <- (tgt.port$tgt.ret-riskfree)/tgt.port$tgt.sd
head(tgt.port)
```
Identify the portfolio with the highest Sharpe Ratio and that is the tangency portfolio
```{r tangency portfolio}


tangency.port <- subset(tgt.port,tgt.port$Sharpe==max(tgt.port$Sharpe))
print(tangency.port)


```
Identify Efficient Portfolios
Portfolios that have returns higher than the return of the minimum variance portfolio.
```{r efficient frontiers}
eff.frontier <- subset(tgt.port,tgt.port$tgt.ret>=minvar.port$tgt.ret)
eff.frontier[c(1:3,nrow(eff.frontier)),]
```

Plot the MV Efficient Frontier

```{r}
plot(x=tgt.sd,
     y=tgt.ret,
     col="gray40",
     xlab="Portfolio Risk",
     ylab="Portfolio Return",
     main="Mean-Variance Efficient Frontier of 12 Assets \n Based on the Quadratic Programming Approach")
abline(h=0,lty=1)
points(x=minvar.port$tgt.sd,y=minvar.port$tgt.ret,pch=17,cex=3,col="red")
points(x=tangency.port$tgt.sd,y=tangency.port$tgt.ret,pch=19,cex=3,col="blue")
points(x=eff.frontier$tgt.sd,y=eff.frontier$tgt.ret,pch=20,cex=1,col="darkgreen")


# Create legend
legend("bottomright", legend = c("Min Variance Portfolio", "Tangency Portfolio", "Efficient Frontier"),
       col = c("red", "blue", "darkgreen"), pch = c(17, 19, 20), cex = 1, bty = "n")

```











































FOR DAILY RETRUNS


convert to xts
a) Calculate Variance-Covariance (VCOV) Matrix of Returns

```{r}

Port.rets.xts = Port.rets.df 
date <-as.Date(Port.rets.all$date,format="%Y-%m-%d")
Port.rets.xts <- cbind(date, Port.rets.xts[,-1])
Port.rets.xts <- Port.rets.xts[order(Port.rets.xts$date),]
Port.rets.xts <- xts(Port.rets.xts[,2:ncol(Port.rets.xts)],order.by=Port.rets.xts[,1])


# # SPY.ret <- Delt(Port.monthly$data.SPY.Adjusted)
# 
# names(Port.monthly) <- paste(c(
#                       "NVDA", "MSFT", "AAPL", "NFLX",
#                       "BRK_B",  "JPM", "C",  "BLK",
#                       "MCD",  "SKX", "SBUX",  "NKE"
#                       ))
# Port.monthly[c(1:3,nrow(Port.monthly)),]

Port.rets.xts <- Port.rets.xts[-1,]
Port.rets.xts[c(1:3,nrow(Port.rets.xts)),]

VCOV.xts <- cov(Port.rets.xts)
VCOV.annual.xts <- nrow(Port.rets.xts)*VCOV.xts   ## s nrow of Port.rets.xts 
VCOV.annual.xts

```

```{r}
# # Convert xts object to zoo object
# Port.rets.zoo <- as.zoo(Port.rets.xts)
# # Convert daily returns to monthly returns
# Port.monthly <- to.period(Port.rets.zoo, period = "months", OHLC = FALSE)
# 
# # Convert zoo object back to xts object
# Port.monthly.xts <- as.xts(Port.monthly)
# Port.monthly.xts[c(1:3,nrow(Port.monthly.xts)),]
# 
# 
# 
# 
# VCOV.monthly.xts <- cov(Port.monthly.xts)
# VCOV.annual.xts1 <- nrow(Port.monthly.xts)*VCOV.monthly.xts   ## s nrow of Port.rets.xts 
# VCOV.annual.xts1

```
COnsrtuct target portfolio return vector

```{r}
mat.ret <- matrix(Port.rets.xts,nrow(Port.rets.xts))
# mat.ret[1:3,]
colnames(mat.ret) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
head(mat.ret)

avg.ret <- matrix(apply(mat.ret,2,mean))
rownames(avg.ret) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
colnames(avg.ret) <- c("Avg.Ret")
avg.ret


min.ret <- min(avg.ret)
min.ret
max.ret <- max(avg.ret)
max.ret
```
Use 100 increments between the minimum and maximum returns to generate the target returns. For each run of the optimizer, the optimizer finds the combination of weights of the four securities that generates the target return with the lowest risk.
```{r}
increments=50
tgt.ret <- seq(min.ret,max.ret,length=increments)
head(tgt.ret,3)

tgt.sd <- rep(0,length=increments)
tgt.sd

wgt <- matrix(0,nrow=increments,ncol=length(avg.ret))
head(wgt,3)



library(quadprog)

for (i in 1:increments){
  Dmat <- VCOV.xts*20
  dvec <- c(rep(0,length(avg.ret)))
  Amat <- cbind(rep(1,length(avg.ret)),avg.ret,
                diag(1,nrow=ncol(Port.rets.xts)))
  bvec <- c(1,tgt.ret[i],rep(0,ncol(Port.rets.xts)))
  soln <- solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=2)
  tgt.sd[i] <- sqrt(soln$value)
  wgt[i,] <- soln$solution
}
head(tgt.sd)
tail(tgt.sd)
```
```{r}
options(scipen=100)
head(wgt)
```
```{r}
colnames(wgt) <- paste(c("wgt.NVDA", "wgt.MSFT", "wgt.AAPL", "wgt.NFLX",
                         "wgt.BRK_B",  "wgt.JPM", "wgt.C",  "wgt.BLK",
                         "wgt.MCD",  "wgt.SKX", "wgt.SBUX",  "wgt.NKE"))
# wgt[1,1] <- 0 
# wgt[nrow(wgt),2] <- 0 
head(wgt)


tgt.port <- data.frame(cbind(tgt.ret,tgt.sd,wgt))
head(tgt.port)
```
Minimum Variance Portfolio 

```{r}

minvar.port <- subset(tgt.port,tgt.port$tgt.sd==min(tgt.port$tgt.sd))
minvar.port

```
The Sharpe Ratio requires a risk-free rate and we use the 3-Month Constant Maturity Treasury as a proxy for that rate. Since the yield as of December 31, 2013 of 0.07% is an annual yield, we convert this to a monthly yield by dividing the rate by 12.

December 31, 2023 of 5.4%   - reference: https://fred.stlouisfed.org/series/DGS3MO
```{r}
riskfree = .054/12

tgt.port$Sharpe <- (tgt.port$tgt.ret-riskfree)/tgt.port$tgt.sd
head(tgt.port)



# Indentify the portfolio with the highest Sharpe Ratio using a combination of subset and max commands.

tangency.port <- subset(tgt.port,tgt.port$Sharpe==max(tgt.port$Sharpe))
tangency.port


# Identify Efficient Portfolios

eff.frontier <- subset(tgt.port,tgt.port$tgt.ret>=minvar.port$tgt.ret)
eff.frontier[c(1:3,nrow(eff.frontier)),]
```

Plot the Efficient Frontier
```{r}
CHECK <- rowSums(wgt)
CHECK

```


```{r}
plot(x=tgt.sd,
     y=tgt.ret,
     col="gray40",
     xlab="Portfolio Risk",
     ylab="Portfolio Return",
     main="Mean-Variance Efficient Frontier of 12 Assets \n Based on the Quadratic Programming Approach")
abline(h=0,lty=1)
points(x=minvar.port$tgt.sd,y=minvar.port$tgt.ret,pch=17,cex=3,col="red")
points(x=tangency.port$tgt.sd,y=tangency.port$tgt.ret,pch=19,cex=3,col="blue")
points(x=eff.frontier$tgt.sd,y=eff.frontier$tgt.ret,pch=20,cex=1,col="darkgreen")


# Create legend
legend("bottomright", legend = c("Min Variance Portfolio", "Tangency Portfolio", "Efficient Frontier"),
       col = c("red", "blue", "darkgreen"), pch = c(17, 19, 20), cex = 1, bty = "n")
```


