---
title: "ANLY515_GroupProject_Saurabh v5 Historical Risks"
author: "Saurabh Shirish Prabhu"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE)
dir.create(tempdir())
```

Importing data from Yahoo finance:

```{r}
getwd()
setwd('F:/a_Harrisburg_University_Academics/ANLY 515-51- A-2024Spring - Risk Modeling and Assessment/Final Project/Code')
getwd()
```
This section contains
Part A – Markowitz Mean-Variance Optimization
Part B – Suitable distributions for returns

Select two market sectors from the 11 sectors identified on this
reference o <https://www.bloomberg.com/markets/sectors>

Answer:

[1]Information Technology<br>

1.1 Semiconductors & Semiconductor Equipment: NVIDIA Corporation (NVDA)<br>
1.2 Software & Services: Microsoft Corporation (MSFT)<br>
1.3 Software & Services: Apple Inc. (AAPL)<br>
1.4 Software & Services: Netflix Inc. (NFLX)<br>


[2]Financials<br>

2.1 Insurance: Berkshire Hathaway Inc. (BRK.B)<br>
2.2 Banks: JPMorgan Chase & Co. (JPM)<br>
2.3 Banks: CitiGroup Inc. (C)<br>
2.4 Insurance: BlackRock Inc. (BLK)<br>



[3]Consumer Discretionary:<br>

3.1 Retailing: McDonald's Corporation (MCD)<br>
3.2 Consumer Durables & Apparel: Skechers U.S.A., Inc. (SKX)<br>
3.3 Retailing: Starbucks Corp. (SBUX) <br>
3.4 Consumer Durables & Apparel: Nike Inc. (NKE)



[4]Industrials: <br>

4.1 Capital Goods: Cummins Inc. (CMI)<br>
4.2 Capital Goods:Deere & Company (DE)<br>


References: <br>
[1]<https://stockanalysis.com/stocks/industry/><br>
[2]<https://medium.com/\@sil.soham/importing-and-visualising-stock-market-data-in-r-ac5a22e23cd><br>


Import all necessary libraries

```{r}
library(quantmod)
library(xts)
library(dplyr)
library(corrplot)
```

Load all stocks



• Confirm that there is no missing data<br> 
• Check the dimensions to
verify that the data covers 5 years<br>
```{r}

start <- as.Date("2014-12-31",format="%Y-%m-%d")
end <- as.Date("2023-12-31",format="%Y-%m-%d")

# Use getSymbols to retrieve the data

# [1]Information Technology
data.NVDA <- getSymbols("NVDA", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.MSFT <- getSymbols("MSFT", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.AAPL <- getSymbols("AAPL", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NFLX <- getSymbols("NFLX", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [2]Financials
data.BRK_B <- getSymbols("BRK-B", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.JPM <- getSymbols("JPM", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.C <- getSymbols("C", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.BLK <- getSymbols("BLK", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [3]Consumer Discretionary:
data.MCD <- getSymbols("MCD", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SKX <- getSymbols("SKX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SBUX <- getSymbols("SBUX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NKE <- getSymbols("NKE", src = "yahoo", from = start, to = end, auto.assign = FALSE)
# Assign the class "xts" and "zoo" explicitly
# class(data.NVDA) <- c("xts", "zoo")
# Print the class of the assigned variable
class(data.NVDA)



names(data.BRK_B)
names(data.BRK_B) <- paste(c("BRK_B.Open","BRK_B.High","BRK_B.Low","BRK_B.Close","BRK_B.Volume","BRK_B.Adjusted"))
names(data.BRK_B)

```
```{r}
### Sector 1: Information Technology: MSFT and NVDA
Infotech.Adjusted.Prices <- data.NVDA$NVDA.Adjusted
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.MSFT$MSFT.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.AAPL$AAPL.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.NFLX$NFLX.Adjusted)
# Infotech.Adjusted.Prices[c(1:3,nrow(Infotech.Adjusted.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Adjusted.Prices <- data.BRK_B$BRK_B.Adjusted
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.JPM$JPM.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.C$C.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.BLK$BLK.Adjusted)
# Financials.Adjusted.Prices[c(1:3,nrow(Financials.Adjusted.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Adjusted.Prices <- data.MCD$MCD.Adjusted
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SKX$SKX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SBUX$SBUX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.NKE$NKE.Adjusted)
# Consumer.Adjusted.Prices[c(1:3,nrow(Consumer.Adjusted.Prices)),]


########
### Entire portfolio
Portfolio.Adj.all <- cbind(Infotech.Adjusted.Prices,Financials.Adjusted.Prices,Consumer.Adjusted.Prices)
Portfolio.Adj.all[c(1:3,nrow(Portfolio.Adj.all)),]

str(Portfolio.Adj.all)
summary(Portfolio.Adj.all)
```
Variance covariance matrix: 

Part A – Risks

```{r}

multi <- Portfolio.Adj.all

mat.price <- matrix(multi,nrow(multi))
prc2ret <- function(x) Delt(x)


mat.ret1 <- apply(mat.price,2,function(x) {prc2ret(c(x))})



mat.ret <- mat.ret1[-1,]
colnames(mat.ret1) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )
# mat.ret[1:4,]


mat.ret[c(1:2,nrow(mat.ret)),]

# # Create a vector of weights AMZN: 25% IBM: 75%
# 
# WGT.12asset <- rep(1/12, 12)   ###EQUALLY WEIGHTED
# WGT.12asset <- matrix(WGT.12asset,1)
# # WGT.12asset
# # Create a transposed vector of weights (command: t)
# 
# tWGT.12asset <- t(WGT.12asset)
# tWGT.12asset


## Calculate annualize and annualize variance-covariance matrix
VCOV <- cov(mat.ret)
VCOV.annual <- nrow(mat.ret)*VCOV   ## 252 is nrow of mat.ret 
VCOV.annual

# Check the range of values in the covariance matrix
min_value <- min(VCOV.annual)
max_value <- max(VCOV.annual)


# Convert covariance matrix to correlation matrix
COR.annual <- cov2cor(VCOV.annual)
corrplot(COR.annual, method = "circle")
```
```{r}
port.df <- data.frame(date = index(Portfolio.Adj.all), coredata(Portfolio.Adj.all))
port.df[c(1:3,nrow(port.df)),]


Port.rets <-port.df
date<-Port.rets$date
# str(date)

PortRet.price <- Port.rets[,-1]


attr(PortRet.price, 'time')<-date   ##add time attribute to dataset
# str(PortRet.price)

prc2ret <- function(x) Delt(x)


Port.rets.all <- apply(PortRet.price,2,function(x) {prc2ret(c(x))})



colnames(Port.rets.all) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )

## Add date column
Port.rets.all = data.frame(Port.rets.all)
Port.rets.all$date <- port.df$date

attr(Port.rets.all, 'time')<-date
head(Port.rets.all)


### reorder to get date in first column
# Get the index of the 'date' column
date_column_index <- which(names(Port.rets.all) == "date")

# Move 'date' column to the first position
new_order <- c(date_column_index, 1:(ncol(Port.rets.all)-1)[-date_column_index+1])

# Rearrange the columns of the data frame
Port.rets.df <- Port.rets.all[, new_order]
Port.rets.df <- Port.rets.df[-1,]
head(Port.rets.df)
```


Create a vector of weights min variance portfolio



```{r}

# Create a vector of weights min variance portfolio

WGT.12asset <- c(0,0.116,5.95e-19,0.0351,0.363,0,3.8e-17,0,0.425,0.00862,0.0261,0.0263)
WGT.12asset <- matrix(WGT.12asset,1)
WGT.12asset



# Create a transposed vector of weights (command: t)

tWGT.12asset <- t(WGT.12asset)
tWGT.12asset
```
MATRIX METHOD:
Calculate the portfolio risk (remmeber %*% is used to multiply a matrix)
```{r}
# Create a vector of weights min variance portfolio

WGT.12asset.mat <- c(0,0.116,5.95e-19,0.0351,0.363,0,3.8e-17,0,0.425,0.00862,0.0261,0.02627)
WGT.12asset.mat <- matrix(WGT.12asset.mat,1)
WGT.12asset.mat



# Create a transposed vector of weights (command: t)

tWGT.12asset.mat <- t(WGT.12asset)
tWGT.12asset.mat

# Calculate the portfolio risk (remmeber %*% is used to multiply a matrix)
mat.var2asset.mat <- WGT.12asset.mat %*% VCOV.annual %*% tWGT.12asset.mat
mat.var2asset.mat

# To calculate the portfolio stndard deviation, use the sqrt command.

mat.sd2asset.mat <- sqrt(mat.var2asset.mat)
mat.sd2asset.mat

```
Value-at-risk

```{r}
port.ret <- read.csv("Hypothetical Portfolio (Daily).csv")
port.ret[c(1:3,nrow(port.ret)),]

port.ret <- port.ret$VW.ret[-1]
port.ret[1:5]
```
Calculate the mean and standard deviation
```{r}
port.mean <- mean(port.ret)
port.mean

port.risk <- sd(port.ret)
port.risk
```
Calculate 1 and 5% VaR
```{r}
VaR01.Gaussian <- -(port.mean+port.risk*qnorm(0.01))*1050746	
VaR01.Gaussian <- format(VaR01.Gaussian,big.mark=',') #to include a comma
VaR01.Gaussian
# This means that there is a %1 chance that the portfolio loses more than $68,326.39

VaR05.Gaussian <- -(port.mean+port.risk*qnorm(0.05))*1050746	
VaR05.Gaussian <- format(VaR05.Gaussian,big.mark=',') #to include a comma
VaR05.Gaussian

# This means that there is a %5 chance that the portfolio loses more than $48,136.66
```
Historical Value-at-risk


```{r}
ret.data <- Port.rets.df
ret.data[c(1:3,nrow(ret.data)),]

last.idx <- c(0.06502349,	0.3241750, 0.3743718,	0.02372905,	0.07272399,	0.07176202,	0.01602416,	0.01937829,	0.03509835,	0.0010180735,	0.02070722, 0.02673449)*1000000

last.idx

port.val <- sum(last.idx)
port.val
```
Calculate simulated portfolio returns applying current portfolio weights to historical security returns
# ```{r}
# sim.portPnL <- last.idx[1]%*%ret.data$NVDA+
#                last.idx[2]%*%ret.data$MSFT+
#                last.idx[3]%*%ret.data$AAPL+
#                last.idx[4]%*%ret.data$NFLX+
#                last.idx[5]%*%ret.data$BRK_B+
#                last.idx[6]%*%ret.data$JPM+
#                last.idx[7]%*%ret.data$C+
#                last.idx[8]%*%ret.data$BLK+
#                last.idx[9]%*%ret.data$MCD+
#                last.idx[10]%*%ret.data$SKX+
#                last.idx[11]%*%ret.data$SBUX+
#                last.idx[12]%*%ret.data$NKE
# 
# 
# 
# 
# names(sim.portPnL) <- paste("Port.Pnl")
# sim.portPnL[c(1:3,nrow(sim.portPnL)),]
# 
# ```


```{r}
# Convert ret.data[, -1] to numeric matrix
ret_data_numeric <- as.matrix(as.data.frame(ret.data[, -1]))

# Convert last.idx to a numeric vector
last_idx_numeric <- as.numeric(last.idx)

# Convert last.idx to a column matrix
last_idx_mat <- matrix(last_idx_numeric, ncol = 1)

# Compute the portfolio PnL for each date
sim.portPnL <- ret_data_numeric %*% last_idx_mat

# Add column names
colnames(sim.portPnL) <- "Port.Pnl"

# Print the first few rows
sim.portPnL[c(1:3,nrow(sim.portPnL)),]

```

```{r}

VaR01.Historical = quantile(-sim.portPnL,0.99)
VaR01.Historical <- format(VaR01.Historical,big.mark = ",")
VaR01.Historical

```
```{r}

VaR05.Historical = quantile(-sim.portPnL,0.95)
VaR05.Historical <- format(VaR05.Historical,big.mark = ",")
VaR05.Historical

```
lot the VaR in relation to the P&L density

i - density of the simulated portfolio P&L ii - normal distribution of P&L’s based on the mean and sd of the simulated portfolio P&L iii - calculated estimates of the 1 and 5% 1-Day Historical Var

To obtain the density of the simulated portfolio P&L, use the density command Typing in ret.d generates the output shown below
```{r}
ret.d=density(sim.portPnL)
ret.d

```
```{r}
plot(ret.d,
     xlab = "Profit & Loss",
     ylab = "",
     yaxt="n",
     main = "Density of Simulated Portfolio P&L Over 8 years
     1% and 5% 1-Day Historical Value-at-Risk (VaR)")
abline(v=-quantile(-sim.portPnL,0.99),col="gray",lty=1)
abline(v=-quantile(-sim.portPnL,0.95),col="black",lty=2)

```

Add ii. Create a sequence of 1000 numbers between the smallest and the largest simulated P&L. This creates bounds for the normal density plot.
```{r}
x <- seq(min(sim.portPnL),max(sim.portPnL),length=1000)
head(x)
tail(x)

# Use the dnorm command to provide the values of the probability density function for the normal distribution. (dnorm: x vector created above, mean of the simulated portfolio P&L, sd of the simulated portfolio P&L)

y <- dnorm(x,mean=mean(sim.portPnL),sd=sd(sim.portPnL))
head(y)
tail(y)
```
Use the lines command to add the normal density plot as a dashed bell curve onto the plot.
```{r}
plot(ret.d,
     xlab = "Profit & Loss",
     ylab = "",
     yaxt="n",
     main = "Density of Simulated Portfolio P&L Over Three Years
     1% and 5% 1-Day Historical Value-at-Risk (VaR)")
abline(v=-quantile(-sim.portPnL,0.99),col="gray",lty=1)
abline(v=-quantile(-sim.portPnL,0.95),col="black",lty=2)

lines(x,y,type = "l",col="black",lwd=1,lty=3)

legend("topright",
       c("Simulated P&L Distribution",
       "Normal Distribution",
       "1% 1-Day VaR","5% 1-Day VaR"),
       col=c("black","black","gray","black"),
       lty=c(1,3,1,2))

```
Expected Shortfall
VaR is limited since it fails to answer the question “If losses exceed VaR, how bad are the losses expected to be?”

The Expected Shortfall (ES) answers this question

ES is also known as tail VaR and tail loss

As with VaR, this section will cover Gaussian ES and Historical ES

Gaussian ES


dnorm function will determine the height of the normal probability density function
qnorm is the inverse normal cumulative density function
mu is the portfolio return
sigma is the sd of the portfolio returns
alpha is the significance level
```{r}
ES01.Gaussian <- 1050746*(port.mean+port.risk*(dnorm(qnorm(.01))/.01))
ES01.Gaussian <- format(ES01.Gaussian,big.mark = ',')
ES01.Gaussian

ES05.Gaussian <- 1050746*(port.mean+port.risk*(dnorm(qnorm(.05))/.05))
ES05.Gaussian <- format(ES05.Gaussian,big.mark = ',')
ES05.Gaussian

# Historical ES
# 
# Historical ES is calculated by taking the average portfolio loss tht fails short of the Historical VaR estimate
# 
# Identify the Historical VaR limit for portfolio

VaR01.hist= -quantile(-sim.portPnL,0.99)
VaR01.hist

VaR05.hist= -quantile(-sim.portPnL,0.95)
VaR05.hist
```

```{r}
ES.PnL <- data.frame(sim.portPnL)

ES.PnL$VaR01.hist <- VaR01.hist
ES.PnL$dummy01 <- ifelse(ES.PnL$Port.Pnl<ES.PnL$VaR01.hist,1,0)

ES.PnL$VaR05.hist <- VaR05.hist
ES.PnL$dummy05 <- ifelse(ES.PnL$Port.Pnl<ES.PnL$VaR05.hist,1,0)
ES.PnL[c(1:3,nrow(ES.PnL)),]

```
Historical ES

Extract portfolio losses in excess of VaR
```{r}
ES.PnL <- data.frame(sim.portPnL)

ES.PnL$VaR01.hist <- VaR01.hist
ES.PnL$dummy01 <- ifelse(ES.PnL$Port.Pnl<ES.PnL$VaR01.hist,1,0)

ES.PnL$VaR05.hist <- VaR05.hist
ES.PnL$dummy05 <- ifelse(ES.PnL$Port.Pnl<ES.PnL$VaR05.hist,1,0)

shortfall01 <- subset(ES.PnL,ES.PnL$dummy01==1)
shortfall05 <- subset(ES.PnL,ES.PnL$dummy05==1)
head(shortfall01)

head(shortfall05)


```

Historical ES

Compute average losses in excess of VaR

Take the average of the returns in each the these data objects.
```{r}
avg.ES01 <- -mean(shortfall01$Port.Pnl)
ES01.Historical <- format(avg.ES01,big.mark = ',')
ES01.Historical

avg.ES05 <- -mean(shortfall05$Port.Pnl)
ES05.Historical <- format(avg.ES05,big.mark = ',')
ES05.Historical

```
Comparing VaR and ES
ES is expected to be larger than VaR

Using a combination of rbind and cbind to bring together all the resulting calculations of Historical and Gaussian VaR and ES.
```{r}
VaR.ES.Combined <- data.frame(rbind(
  cbind(VaR01.Historical,ES01.Historical[1], 
        VaR01.Gaussian,ES01.Gaussian[1]),
  cbind(VaR05.Historical,ES05.Historical[1],
        VaR05.Gaussian,ES05.Gaussian[1])))
names(VaR.ES.Combined) <- paste(
  c("VaR Historical","ES Historical","VaR Gaussian","ES Gaussian"))
rownames(VaR.ES.Combined) <- paste(c("1% 1-Day","5% 1-Day"))
VaR.ES.Combined
```


```{r}
plot(ret.d,
     xlab = "Profit & Loss",
     ylab = "",
     yaxt="n",
     main = "Density of Simulated Portfolio P&L Over 8 Years
     1% and 5% 1-Day Historical Expected Shortfall (ES) 
     1% and 5% 1-Day Historical Value-at-Risk (VaR)")
abline(v=-avg.ES01,col="maroon",lty=1)
abline(v=-avg.ES05,col="red",lty=2)
abline(v=-quantile(-sim.portPnL,0.99),col="darkgray",lty=3)
abline(v=-quantile(-sim.portPnL,0.95),col="black",lty=4)

lines(x,y,type = "l",col="black",lwd=1,lty=3)

legend("topright",
       c("Sim P&L Distribution",
       "Normal Distribution",
       "1% 1-Day ES","5% 1-Day ES",
       "1% 1-Day VaR","5% 1-Day VaR"),
       col=c("black","black","maroon","red","darkgray","black"),
       lty=c(1,3,1,2,3,4))

```