---
title: 'ANLY 515: Risk Modeling Project'
author: "Saurabh Shirish Prabhu"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE)
dir.create(tempdir())
```

Importing data from Yahoo finance:

```{r}
getwd()
setwd('F:/a_Harrisburg_University_Academics/ANLY 515-51- A-2024Spring - Risk Modeling and Assessment/Final Project/Code')
getwd()
```

Select two market sectors from the 11 sectors identified on this
reference o <https://www.bloomberg.com/markets/sectors>

Answer:

[1]Information Technology<br>

1.1 Semiconductors & Semiconductor Equipment: NVIDIA Corporation (NVDA)<br>
1.2 Software & Services: Microsoft Corporation (MSFT)<br>
1.3 Software & Services: Apple Inc. (AAPL)<br>
1.4 Software & Services: Netflix Inc. (NFLX)<br>


[2]Financials<br>

2.1 Insurance: Berkshire Hathaway Inc. (BRK.B)<br>
2.2 Banks: JPMorgan Chase & Co. (JPM)<br>
2.3 Banks: CitiGroup Inc. (C)<br>
2.4 Insurance: BlackRock Inc. (BLK)<br>



[3]Consumer Discretionary:<br>

3.1 Retailing: McDonald's Corporation (MCD)<br>
3.2 Consumer Durables & Apparel: Skechers U.S.A., Inc. (SKX)<br>
3.3 Retailing: Starbucks Corp. (SBUX) <br>
3.4 Consumer Durables & Apparel: Nike Inc. (NKE)



[4]Industrials: <br>

4.1 Capital Goods: Cummins Inc. (CMI)<br>
4.2 Capital Goods:Deere & Company (DE)<br>


References: <br>
[1]<https://stockanalysis.com/stocks/industry/><br>
[2]<https://medium.com/\@sil.soham/importing-and-visualising-stock-market-data-in-r-ac5a22e23cd><br>


Import all necessary libraries

```{r}
library(quantmod)
library(xts)
library(dplyr)
```

Students should have a five-year portfolio. The calculations for this homework will be based on the data from the third year of your portfolio.

• Identify the five-year period of your portfolio

a) Identify the period for this homework

• Use only 4 stocks from your portfolio



Part A – Individual Security Returns
1. Calculate Returns

a) Calculate portfolio price returns for the homework period


2. Dividend reinvestment strategy

a) Calculate portfolio total gross returns for the homework period

b) Calculate portfolio logarithmic gross returns for the homework period

c) Are the results the same?


3. Plot a comparison of Total Price returns and Total Gross returns



Part B – Portfolio Returns

Use the same investment period and the same stocks

1. Create an equally-weighted portfolio (rebalance each quarter)

2. Create a value-weighted portfolio (rebalance each quarter)

a. Create weight pie charts for each quarter

3. Plot a comparison between the EW and the VW portfolio



```{r}

start <- as.Date("2014-12-31",format="%Y-%m-%d")
end <- as.Date("2023-12-31",format="%Y-%m-%d")

# Use getSymbols to retrieve the data

# [1]Information Technology
data.NVDA <- getSymbols("NVDA", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.MSFT <- getSymbols("MSFT", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.AAPL <- getSymbols("AAPL", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NFLX <- getSymbols("NFLX", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [2]Financials
data.BRK_B <- getSymbols("BRK-B", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.JPM <- getSymbols("JPM", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.C <- getSymbols("C", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.BLK <- getSymbols("BLK", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [3]Consumer Discretionary:
data.MCD <- getSymbols("MCD", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SKX <- getSymbols("SKX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SBUX <- getSymbols("SBUX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NKE <- getSymbols("NKE", src = "yahoo", from = start, to = end, auto.assign = FALSE)
# Assign the class "xts" and "zoo" explicitly
# class(data.NVDA) <- c("xts", "zoo")
# Print the class of the assigned variable
class(data.NVDA)


```

Plot the data for each security to check for missing data<br>

• Confirm that there is no missing data<br> 
• Check the dimensions to
verify that the data covers 5 years<br>

```{r}
names(data.BRK_B)
names(data.BRK_B) <- paste(c("BRK_B.Open","BRK_B.High","BRK_B.Low","BRK_B.Close","BRK_B.Volume","BRK_B.Adjusted"))
names(data.BRK_B)
```

```{r}

## Information Technology
par(mfrow = c(2, 2))  # Set up a 2x2 grid layout
plot(data.NVDA$NVDA.Adjusted, main="NVDA")
plot(data.MSFT$MSFT.Adjusted, main="MSFT")
plot(data.AAPL$AAPL.Adjusted, main="AAPL")
plot(data.NFLX$NFLX.Adjusted, main="NFLX")


## Financials
par(mfrow = c(2, 2))  # Set up a 2x2 grid layout
plot(data.BRK_B$BRK_B.Adjusted, main="BRK_B")
plot(data.JPM$JPM.Adjusted, main="JPM")
plot(data.C$C.Adjusted, main="C")
plot(data.BLK$BLK.Adjusted, main="BLK")


## Consumer Discretionary
par(mfrow = c(2, 2))  # Set up a 2x2 grid layout
plot(data.MCD$MCD.Adjusted, main="MCD")
plot(data.SKX$SKX.Adjusted, main="SKX")
plot(data.SBUX$SBUX.Adjusted, main="SBUX")
plot(data.NKE$NKE.Adjusted, main="NKE")

```

Notes: <br>

-   No missing values<br>
-   Each stock covers 5 years from 2010/01/01 - 2014/12/31<br>


```{r}
# List of data frames
stocks_df <- list(data.NVDA, data.MSFT, data.AAPL, data.NFLX, data.BRK_B, data.JPM, data.C, data.BLK, data.MCD, data.SKX, data.SBUX, data.NKE)

# Loop over data frames
for (df in stocks_df) {
  print(dim(df))
  print(summary(df))
}

```


combining each sectors<br>



<<<<<<<<<<<<<<<<<<<< Total Returns >>>>>>>>>>>>>>>>>>>>>>>>



```{r}
stocks_df <- list(data.NVDA, data.MSFT, data.AAPL, data.NFLX, data.BRK_B, data.JPM, data.C, data.BLK, data.MCD, data.SKX, data.SBUX, data.NKE)
Infotech_df   <-list(data.NVDA, data.MSFT, data.AAPL, data.NFLX)
Financials_df <-list(data.BRK_B, data.JPM, data.C, data.C)
Consumer_df   <-list(data.MCD, data.SKX, data.SBUX, data.NKE)

### TOTAl RETURNS
# Combine Data Into individual sectors

```


```{r}
### Sector 1: Information Technology: MSFT and NVDA
Infotech.Adjusted.Prices <- data.NVDA$NVDA.Adjusted
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.MSFT$MSFT.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.AAPL$AAPL.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.NFLX$NFLX.Adjusted)
Infotech.Adjusted.Prices[c(1:3,nrow(Infotech.Adjusted.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Adjusted.Prices <- data.BRK_B$BRK_B.Adjusted
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.JPM$JPM.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.C$C.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.BLK$BLK.Adjusted)
Financials.Adjusted.Prices[c(1:3,nrow(Financials.Adjusted.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Adjusted.Prices <- data.MCD$MCD.Adjusted
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SKX$SKX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SBUX$SBUX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.NKE$NKE.Adjusted)
Consumer.Adjusted.Prices[c(1:3,nrow(Consumer.Adjusted.Prices)),]


########
### Entire portfolio
Portfolio.totret.all <- cbind(Infotech.Adjusted.Prices,Financials.Adjusted.Prices,Consumer.Adjusted.Prices)
Portfolio.totret.all[c(1:3,nrow(Portfolio.totret.all)),]


```




<<<<<<<<<<<<<<<<<<<<<<PRICE RETURNS>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

```{r}

### PRICE RETURNS
# Combine Data Into individual sectors

### Sector 1: Information Technology: MSFT and NVDA
Infotech.Close.Prices <- data.NVDA$NVDA.Close
Infotech.Close.Prices <-cbind(Infotech.Close.Prices,data.MSFT$MSFT.Close)
Infotech.Close.Prices <-cbind(Infotech.Close.Prices,data.AAPL$AAPL.Close)
Infotech.Close.Prices <-cbind(Infotech.Close.Prices,data.NFLX$NFLX.Close)
Infotech.Close.Prices[c(1:3,nrow(Infotech.Close.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Close.Prices <- data.BRK_B$BRK_B.Close
Financials.Close.Prices <-cbind(Financials.Close.Prices,data.JPM$JPM.Close)
Financials.Close.Prices <-cbind(Financials.Close.Prices,data.C$C.Close)
Financials.Close.Prices <-cbind(Financials.Close.Prices,data.BLK$BLK.Close)
Financials.Close.Prices[c(1:3,nrow(Financials.Close.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Close.Prices <- data.MCD$MCD.Close
Consumer.Close.Prices <-cbind(Consumer.Close.Prices,data.SKX$SKX.Close)
Consumer.Close.Prices <-cbind(Consumer.Close.Prices,data.SBUX$SBUX.Close)
Consumer.Close.Prices <-cbind(Consumer.Close.Prices,data.NKE$NKE.Close)
Consumer.Close.Prices[c(1:3,nrow(Consumer.Close.Prices)),]


########
### Entire portfolio
Portfolio.prcret.all <- cbind(Infotech.Close.Prices,Financials.Close.Prices, Consumer.Close.Prices)
Portfolio.prcret.all[c(1:3,nrow(Portfolio.prcret.all)),]


```



third year 

```{r}
### Portfolio Price Return for Homework period 2015-01-01 to 2023-12-31 



Portfolio.prcret.15_23 <- subset(Portfolio.prcret.all,
                    + index(Portfolio.prcret.all) >= "2014-12-31" &
                    + index(Portfolio.prcret.all) <= "2023-12-31")
Portfolio.prcret.15_23[c(1:3,nrow(Portfolio.prcret.15_23))]

Portfolio.prcret.15_23.df<- data.frame(date = index(Portfolio.prcret.15_23), coredata(Portfolio.prcret.15_23))
```
December 31, 2011 was Saturday and January 02, 2012 was observed as New Years Holiday 


```{r}
## Daily Price Returns - Arithmetic


#Calculate Price Return (using Delt command)
Portfolio.prc.ret = Portfolio.prcret.15_23 
Portfolio.prc.ret$NVDA.prc.ret <- Delt(Portfolio.prc.ret$NVDA.Close)
Portfolio.prc.ret$MSFT.prc.ret <- Delt(Portfolio.prc.ret$MSFT.Close)
Portfolio.prc.ret$AAPL.prc.ret <- Delt(Portfolio.prc.ret$AAPL.Close)
Portfolio.prc.ret$NFLX.prc.ret <- Delt(Portfolio.prc.ret$NFLX.Close)

Portfolio.prc.ret$BRK_B.prc.ret <- Delt(Portfolio.prc.ret$BRK_B.Close)
Portfolio.prc.ret$JPM.prc.ret <- Delt(Portfolio.prc.ret$JPM.Close)
Portfolio.prc.ret$C.prc.ret <- Delt(Portfolio.prc.ret$C.Close)
Portfolio.prc.ret$BLK.prc.ret <- Delt(Portfolio.prc.ret$BLK.Close)

Portfolio.prc.ret$MCD.prc.ret <- Delt(Portfolio.prc.ret$MCD.Close)
Portfolio.prc.ret$SKX.prc.ret <- Delt(Portfolio.prc.ret$SKX.Close)
Portfolio.prc.ret$SBUX.prc.ret <- Delt(Portfolio.prc.ret$SBUX.Close)
Portfolio.prc.ret$NKE.prc.ret <- Delt(Portfolio.prc.ret$NKE.Close)


Portfolio.prc.ret <- Portfolio.prc.ret[,-c(1:ncol(Portfolio.prcret.15_23))]
Portfolio.prc.ret[c(1:3,nrow(Portfolio.prc.ret)),]


```

```{r}
## Daily Price Returns - logarithmic 

#Calculate Log Price Return (using Delt command)
Portfolio.log.ret = Portfolio.prcret.15_23 
Portfolio.log.ret$NVDA.prclog.ret <- diff(log(Portfolio.log.ret$NVDA.Close))
Portfolio.log.ret$MSFT.prclog.ret <- diff(log(Portfolio.log.ret$MSFT.Close))
Portfolio.log.ret$AAPL.prclog.ret <- diff(log(Portfolio.log.ret$AAPL.Close))
Portfolio.log.ret$NFLX.prclog.ret <- diff(log(Portfolio.log.ret$NFLX.Close))



Portfolio.log.ret$BRK_B.prclog.ret <- diff(log(Portfolio.log.ret$BRK_B.Close))
Portfolio.log.ret$JPM.prclog.ret <- diff(log(Portfolio.log.ret$JPM.Close))
Portfolio.log.ret$C.prclog.ret <- diff(log(Portfolio.log.ret$C.Close))
Portfolio.log.ret$BLK.prclog.ret <- diff(log(Portfolio.log.ret$BLK.Close))

Portfolio.log.ret$MCD.prclog.ret <- diff(log(Portfolio.log.ret$MCD.Close))
Portfolio.log.ret$SKX.prclog.ret <- diff(log(Portfolio.log.ret$SKX.Close))
Portfolio.log.ret$SBUX.prclog.ret <- diff(log(Portfolio.log.ret$SBUX.Close))
Portfolio.log.ret$NKE.prclog.ret <- diff(log(Portfolio.log.ret$NKE.Close))

Portfolio.log.ret <- Portfolio.log.ret[,-c(1:ncol(Portfolio.prcret.15_23))]
Portfolio.log.ret[c(1:3,nrow(Portfolio.log.ret)),]


```


```{r}
## PORTFOLIO RETURNS 

########################### sum of all close values
Portfolio.prcret.15_23.rsum<- data.frame(date = index(Portfolio.prcret.15_23), coredata(Portfolio.prcret.15_23))

Portfolio.prcret.15_23.rsum <-data.frame(rowSums(Portfolio.prcret.15_23.rsum[,2:(ncol(Portfolio.prcret.15_23)+1)]))

# Portfolio.prcret.15_23.rsum[c(1:3,nrow(Portfolio.prcret.15_23.rsum)),]


names(Portfolio.prcret.15_23.rsum) <- paste("port15_23.close")

Portfolio.prcret.15_23.rsum$date <- Portfolio.prcret.15_23.df$date
Portfolio.prcret.15_23.rsum <- Portfolio.prcret.15_23.rsum[,c("date", "port15_23.close")]
Portfolio.prcret.15_23.rsum[c(1:3,nrow(Portfolio.prcret.15_23.rsum)),]


# Portfolio.prcret.15_23[c(1:3,nrow(Portfolio.prcret.15_23)),]
```



```{r}
## Daily Price Returns - Arithmetic


#Calculate Price Return (using Delt command)
Portfolio.prc.ret.rsum <- xts(Portfolio.prcret.15_23.rsum$port15_23.close,order.by=Portfolio.prcret.15_23.rsum$date)
names(Portfolio.prc.ret.rsum) <- paste(c("port15_23.close"))
# Portfolio.prc.ret.rsum = Portfolio.prcret.15_23.rsum
Portfolio.prc.ret.rsum$port15_23.prc.ret <- Delt(Portfolio.prc.ret.rsum$port15_23.close)
Portfolio.prc.ret.rsum[c(1:3,nrow(Portfolio.prc.ret.rsum)),]



## Daily Price Returns - logarithmic 

#Calculate Log Price Return (using Delt command)
Portfolio.log.ret.rsum = xts(Portfolio.prcret.15_23.rsum$port15_23.close,order.by=Portfolio.prcret.15_23.rsum$date)
names(Portfolio.log.ret.rsum) <- paste(c("port15_23.close"))

Portfolio.log.ret.rsum$port15_23.log.ret <- diff(log(Portfolio.log.ret.rsum$port15_23.close))
# Portfolio.log.ret <- Portfolio.log.ret[,-c(1:4)]
Portfolio.log.ret.rsum[c(1:3,nrow(Portfolio.log.ret.rsum)),]


```





Part A -- Individual Security Returns 
1. Calculate Returns 
a) Calculate portfolio price returns for the homework period

2.  Dividend reinvestment strategy
a)  Calculate portfolio total gross returns for the homework period
b)  Calculate portfolio logarithmic gross returns for the homework period

c)  Are the results the same?


3.  Plot a comparison of Total Price returns and Total Gross returns

Answers: Part A -- Individual Security Returns 
1. Calculate Returns 
a)Calculate portfolio price returns for the homework period


```{r}
### Portfolio Total Return for Homework period 2012-01-01 to 2012-12-31 


Portfolio.totret.15_23 <- subset(Portfolio.totret.all,
                    + index(Portfolio.totret.all) >= "2014-12-31" &
                    + index(Portfolio.totret.all) <= "2023-12-31")
Portfolio.totret.15_23[c(1:3,nrow(Portfolio.totret.15_23))]

Portfolio.totret.15_23.df<- data.frame(date = index(Portfolio.totret.15_23), coredata(Portfolio.totret.15_23))

```

```{r}
## Daily Total Returns - Arithmetic

options(digits=3)
#Calculate Total Return (using Delt command)
Portfolio.tot.ret = Portfolio.totret.15_23 
Portfolio.tot.ret$NVDA.tot.ret <- Delt(Portfolio.tot.ret$NVDA.Adjusted)
Portfolio.tot.ret$MSFT.tot.ret <- Delt(Portfolio.tot.ret$MSFT.Adjusted)
Portfolio.tot.ret$AAPL.tot.ret <- Delt(Portfolio.tot.ret$AAPL.Adjusted)
Portfolio.tot.ret$NFLX.tot.ret <- Delt(Portfolio.tot.ret$NFLX.Adjusted)



Portfolio.tot.ret$BRK_B.tot.ret <- Delt(Portfolio.tot.ret$BRK_B.Adjusted)
Portfolio.tot.ret$JPM.tot.ret <- Delt(Portfolio.tot.ret$JPM.Adjusted)
Portfolio.tot.ret$C.tot.ret <- Delt(Portfolio.tot.ret$C.Adjusted)
Portfolio.tot.ret$BLK.tot.ret <- Delt(Portfolio.tot.ret$BLK.Adjusted)


Portfolio.tot.ret$MCD.tot.ret <- Delt(Portfolio.tot.ret$MCD.Adjusted)
Portfolio.tot.ret$SKX.tot.ret <- Delt(Portfolio.tot.ret$SKX.Adjusted)
Portfolio.tot.ret$SBUX.tot.ret <- Delt(Portfolio.tot.ret$SBUX.Adjusted)
Portfolio.tot.ret$NKE.tot.ret <- Delt(Portfolio.tot.ret$NKE.Adjusted)


Portfolio.tot.ret <- Portfolio.tot.ret[,-c(1:ncol(Portfolio.totret.15_23))]
Portfolio.tot.ret[c(1:3,nrow(Portfolio.tot.ret)),]


```

```{r}
## Daily Total Returns - logarithmic 
options(digits=3)
#Calculate Log Total Return (using Delt command)
Portfolio.totlog.ret = Portfolio.totret.15_23 
Portfolio.totlog.ret$NVDA.totlog.ret <- diff(log(Portfolio.totlog.ret$NVDA.Adjusted))
Portfolio.totlog.ret$MSFT.totlog.ret <- diff(log(Portfolio.totlog.ret$MSFT.Adjusted))
Portfolio.totlog.ret$AAPL.totlog.ret <- diff(log(Portfolio.totlog.ret$AAPL.Adjusted))
Portfolio.totlog.ret$NKLX.totlog.ret <- diff(log(Portfolio.totlog.ret$NFLX.Adjusted))


Portfolio.totlog.ret$BRK_B.totlog.ret <- diff(log(Portfolio.totlog.ret$BRK_B.Adjusted))
Portfolio.totlog.ret$JPM.totlog.ret <- diff(log(Portfolio.totlog.ret$JPM.Adjusted))
Portfolio.totlog.ret$C.totlog.ret <- diff(log(Portfolio.totlog.ret$C.Adjusted))
Portfolio.totlog.ret$BLK.totlog.ret <- diff(log(Portfolio.totlog.ret$BLK.Adjusted))


Portfolio.totlog.ret$MCD.totlog.ret <- diff(log(Portfolio.totlog.ret$MCD.Adjusted))
Portfolio.totlog.ret$SKX.totlog.ret <- diff(log(Portfolio.totlog.ret$SKX.Adjusted))
Portfolio.totlog.ret$SBUX.totlog.ret <- diff(log(Portfolio.totlog.ret$SBUX.Adjusted))
Portfolio.totlog.ret$NKE.totlog.ret <- diff(log(Portfolio.totlog.ret$NKE.Adjusted))

Portfolio.totlog.ret <- Portfolio.totlog.ret[,-c(1:ncol(Portfolio.totret.15_23))]
Portfolio.totlog.ret[c(1:3,nrow(Portfolio.totlog.ret)),]


```






difference between log return and arithmetic return for Total retursn

```{r}
## This is Q2.a Answer

options(digits=3,scipen=1000)
tot.rets <- cbind(Portfolio.tot.ret,Portfolio.totlog.ret)
tot.rets[c(1:3,nrow(tot.rets)),]

max(abs(tot.rets$NVDA.tot.ret-tot.rets$NVDA.totlog.ret),na.rm=TRUE)
min(abs(tot.rets$NVDA.tot.ret-tot.rets$NVDA.totlog.ret),na.rm=TRUE)

max(abs(tot.rets$JPM.tot.ret-tot.rets$JPM.totlog.ret),na.rm=TRUE)
min(abs(tot.rets$JPM.tot.ret-tot.rets$JPM.totlog.ret),na.rm=TRUE)
# options(digits=7,scipen=0) #back to default
```

######################################## PORTFOLIO RSUM ########################################

```{r}
## PORTFOLIO RETURNS 


options(digits=7,scipen=10)

########################### sum of all close values
Portfolio.totret.15_23.rsum<- data.frame(date = index(Portfolio.totret.15_23), coredata(Portfolio.totret.15_23))
Portfolio.totret.15_23.rsum <-data.frame(rowSums(Portfolio.totret.15_23.rsum[,2:(1+ncol(Portfolio.totret.15_23))]))

# Portfolio.totret.15_23.rsum[c(1:3,nrow(Portfolio.totret.15_23.rsum)),]


names(Portfolio.totret.15_23.rsum) <- paste("port15_23.adjusted")

Portfolio.totret.15_23.rsum$date <- Portfolio.totret.15_23.df$date
Portfolio.totret.15_23.rsum <- Portfolio.totret.15_23.rsum[,c("date", "port15_23.adjusted")]
Portfolio.totret.15_23.rsum[c(1:3,nrow(Portfolio.totret.15_23.rsum)),]

```
```{r}
#Calculate Total Return (using Delt command)
Portfolio.tot.ret.rsum = xts(Portfolio.totret.15_23.rsum$port15_23.adjusted,order.by=Portfolio.totret.15_23.rsum$date)
names(Portfolio.tot.ret.rsum) <- paste(c("port15_23.adjusted"))


Portfolio.tot.ret.rsum$port15_23.tot.ret <- Delt(Portfolio.tot.ret.rsum$port15_23.adjusted)
# Portfolio.tot.ret.rsum <- Portfolio.tot.ret.rsum[,-c(1:4)]
Portfolio.tot.ret.rsum[c(1:3,nrow(Portfolio.tot.ret.rsum)),]




## Daily Total Returns - logarithmic 

#Calculate Log Price Return (using Delt command)
Portfolio.totlog.ret.rsum = xts(Portfolio.totret.15_23.rsum$port15_23.adjusted,order.by=Portfolio.totret.15_23.rsum$date)
names(Portfolio.totlog.ret.rsum) <- paste(c("port15_23.adjusted"))

Portfolio.totlog.ret.rsum$port15_23.totlog.ret <- diff(log(Portfolio.totlog.ret.rsum$port15_23.adjusted))
# Portfolio.log.ret <- Portfolio.log.ret[,-c(1:4)]
Portfolio.totlog.ret.rsum[c(1:3,nrow(Portfolio.totlog.ret.rsum)),]



# options(digits=3,scipen=1000)
tot.rets.rsum <- cbind(Portfolio.tot.ret.rsum,Portfolio.totlog.ret.rsum[,-c(1)])
tot.rets.rsum[c(1:3,nrow(tot.rets.rsum)),]


```

############################### PORTFOLIO RSUM END ############################





<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<gross returns>>>>>>>>>>>>>>>>>>>>>>>>>>>>

2. Dividend reinvestment strategy
a) Calculate portfolio total gross returns for the homework period
b) Calculate portfolio logarithmic gross returns for the homework period
c) Are the results the same?

Cumulating Arithmetic Returns


```{r}
options(digits=7,scipen=100)
Portfolio.acum <- tot.rets

Portfolio.acum[1,] <-0   ### Set first day total return to zero (investment day)




# <<<<< Cumulating Arithmetic Returns>>>

#### Gross return (1 + net total return) 
Portfolio.acum$NVDA.GrossRet <- 1+Portfolio.acum$NVDA.tot.ret
Portfolio.acum$MSFT.GrossRet <- 1+Portfolio.acum$MSFT.tot.ret
Portfolio.acum$AAPL.GrossRet <- 1+Portfolio.acum$AAPL.tot.ret
Portfolio.acum$NFLX.GrossRet <- 1+Portfolio.acum$NFLX.tot.ret

Portfolio.acum$BRK_B.GrossRet <- 1+Portfolio.acum$BRK_B.tot.ret
Portfolio.acum$JPM.GrossRet <- 1+Portfolio.acum$JPM.tot.ret
Portfolio.acum$C.GrossRet <- 1+Portfolio.acum$C.tot.ret
Portfolio.acum$BLK.GrossRet <- 1+Portfolio.acum$BLK.tot.ret

Portfolio.acum$MCD.GrossRet <- 1+Portfolio.acum$MCD.tot.ret
Portfolio.acum$SKX.GrossRet <- 1+Portfolio.acum$SKX.tot.ret
Portfolio.acum$SBUX.GrossRet <- 1+Portfolio.acum$SBUX.tot.ret
Portfolio.acum$NKE.GrossRet <- 1+Portfolio.acum$NKE.tot.ret


#### Cummulative Gross return ( product of all the gross returns for the preiod)
Portfolio.acum$NVDA.GrossCum <- cumprod(Portfolio.acum$NVDA.GrossRet)
Portfolio.acum$MSFT.GrossCum <- cumprod(Portfolio.acum$MSFT.GrossRet)
Portfolio.acum$AAPL.GrossCum <- cumprod(Portfolio.acum$AAPL.GrossRet)
Portfolio.acum$NFLX.GrossCum <- cumprod(Portfolio.acum$NFLX.GrossRet)

Portfolio.acum$BRK_B.GrossCum <- cumprod(Portfolio.acum$BRK_B.GrossRet)
Portfolio.acum$JPM.GrossCum <- cumprod(Portfolio.acum$JPM.GrossRet)
Portfolio.acum$C.GrossCum <- cumprod(Portfolio.acum$C.GrossRet)
Portfolio.acum$BLK.GrossCum <- cumprod(Portfolio.acum$BLK.GrossRet)

Portfolio.acum$MCD.GrossCum <- cumprod(Portfolio.acum$MCD.GrossRet)
Portfolio.acum$SKX.GrossCum <- cumprod(Portfolio.acum$SKX.GrossRet)
Portfolio.acum$SBUX.GrossCum <- cumprod(Portfolio.acum$SBUX.GrossRet)
Portfolio.acum$NKE.GrossCum <- cumprod(Portfolio.acum$NKE.GrossRet)



#### Convert Cumulative Gross Returns to Cumulative Net Returns (-1)
Portfolio.acum$NVDA.NetCum <- Portfolio.acum$NVDA.GrossCum - 1
Portfolio.acum$MSFT.NetCum <- Portfolio.acum$MSFT.GrossCum - 1
Portfolio.acum$AAPL.NetCum <- Portfolio.acum$AAPL.GrossCum - 1
Portfolio.acum$NFLX.NetCum <- Portfolio.acum$NFLX.GrossCum - 1

Portfolio.acum$BRK_B.NetCum <- Portfolio.acum$BRK_B.GrossCum - 1
Portfolio.acum$JPM.NetCum <- Portfolio.acum$JPM.GrossCum - 1
Portfolio.acum$C.NetCum <- Portfolio.acum$C.GrossCum - 1
Portfolio.acum$BLK.NetCum <- Portfolio.acum$BLK.GrossCum - 1

Portfolio.acum$MCD.NetCum <- Portfolio.acum$MCD.GrossCum - 1
Portfolio.acum$SKX.NetCum <- Portfolio.acum$SKX.GrossCum - 1
Portfolio.acum$SBUX.NetCum <- Portfolio.acum$SBUX.GrossCum - 1
Portfolio.acum$NKE.NetCum <- Portfolio.acum$NKE.GrossCum - 1


# for (stock in stocks) {print(Portfolio.acum[,paste0(stock, ".GrossCum")])}



# <<<<< Cumulating Logarithmic Returns>>>

exp(sum(Portfolio.acum$NVDA.totlog.ret))-1
# exp(sum(Portfolio.acum$MSFT.totlog.ret))-1
# exp(sum(Portfolio.acum$AAPL.totlog.ret))-1
# exp(sum(Portfolio.acum$NFLX.totlog.ret))-1
# 
# exp(sum(Portfolio.acum$BRK_B.totlog.ret))-1
# exp(sum(Portfolio.acum$JPM.totlog.ret))-1
# exp(sum(Portfolio.acum$C.totlog.ret))-1
# exp(sum(Portfolio.acum$BLK.totlog.ret))-1
# 
# exp(sum(Portfolio.acum$MCD.totlog.ret))-1
# exp(sum(Portfolio.acum$SKX.totlog.ret))-1
# exp(sum(Portfolio.acum$SBUX.totlog.ret))-1
exp(sum(Portfolio.acum$NKE.totlog.ret))-1


Portfolio.acum[c(1:3,nrow(Portfolio.acum)),]


```
Yes. total gross returns and logarithmic gross returns results are same. 


######################################## PORTFOLIO RSUM  ########################################
```{r}
Portfolio.acum.rsum <- tot.rets.rsum

Portfolio.acum.rsum[1,] <-0   ### Set first day total return to zero (investment day)




# <<<<< Cumulating Arithmetic Returns>>>

#### Gross return (1 + net total return) 
Portfolio.acum.rsum$port15_23.GrossRet <- 1+Portfolio.acum.rsum$port15_23.tot.ret


#### Cummulative Gross return ( product of all the gross returns for the preiod)
Portfolio.acum.rsum$port15_23.GrossCum <- cumprod(Portfolio.acum.rsum$port15_23.GrossRet)


#### Convert Cumulative Gross Returns to Cumulative Net Returns (-1)
Portfolio.acum.rsum$port15_23.NetCum <- Portfolio.acum.rsum$port15_23.GrossCum - 1

# for (stock in stocks) {print(Portfolio.acum[,paste0(stock, ".GrossCum")])}



# <<<<< Cumulating Logarithmic Returns>>>

exp(sum(Portfolio.acum.rsum$port15_23.totlog.ret))-1

Portfolio.acum.rsum[c(1:3,nrow(Portfolio.acum.rsum)),]
```
Port Cumulative Net Returns and Cumulating Logarithmic Returns are the same

######################################## PORTFOLIO RSUM END ########################################





3. Plot a comparison of Total Price returns and Total Gross returns


```{r}

Daily.rets <- cbind(Portfolio.prc.ret,Portfolio.tot.ret)
Daily.rets[1,]<-0

# Calculate gross returns
Daily.gross.rets <-1+Daily.rets
# Define new column names
new_column_names <- c(
                      "NVDA.gross.prc", "MSFT.gross.prc", "AAPL.gross.prc", "NFLX.gross.prc",
                      "BRK_B.gross.prc",  "JPM.gross.prc", "C.gross.prc",  "BLK.gross.prc",
                      "MCD.gross.prc",  "SKX.gross.prc", "SBUX.gross.prc",  "NKE.gross.prc",
                      "NVDA.gross.tot", "MSFT.gross.tot","AAPL.gross.tot", "NFLX.gross.tot", 
                      "BRK_B.gross.tot", "JPM.gross.tot", "C.gross.tot",  "BLK.gross.tot",
                      "MCD.gross.tot",  "SKX.gross.tot", "SBUX.gross.tot",  "NKE.gross.tot"
                      )

# Set the new column names
colnames(Daily.gross.rets) <- new_column_names


# Calculate gross returns cumprod
Daily.cum.rets <-cumprod(Daily.gross.rets)
# new_column_names <- c("NVDA.cum.prc", "MSFT.cum.prc", "BRK_B.cum.prc",  "JPM.cum.prc", "NVDA.cum.tot", "MSFT.cum.tot", "BRK_B.cum.tot", "JPM.cum.tot")

new_column_names <- c(
                      "NVDA.cum.prc", "MSFT.cum.prc", "AAPL.cum.prc", "NFLX.cum.prc",
                      "BRK_B.cum.prc",  "JPM.cum.prc", "C.cum.prc",  "BLK.cum.prc",
                      "MCD.cum.prc",  "SKX.cum.prc", "SBUX.cum.prc",  "NKE.cum.prc",
                      "NVDA.cum.tot", "MSFT.cum.tot","AAPL.cum.tot", "NFLX.cum.tot", 
                      "BRK_B.cum.tot", "JPM.cum.tot", "C.cum.tot",  "BLK.cum.tot",
                      "MCD.cum.tot",  "SKX.cum.tot", "SBUX.cum.tot",  "NKE.cum.tot"
                      )


colnames(Daily.cum.rets) <- new_column_names




Daily.rets[c(1:3,nrow(Daily.rets)),]

Daily.gross.rets[c(1:3,nrow(Daily.gross.rets)),]

Daily.cum.rets[c(1:3,nrow(Daily.cum.rets)),]


```
Plot a comparison of Total Price returns and Total Gross returns
```{r}
# y.range <- range(Daily.cum.rets)
# y.range

# Convert xts to data frame
df1 <- data.frame(Date = index(Daily.cum.rets), coredata(Daily.cum.rets))

# df1 <-Daily.cum.rets
### NVDA
plot(df1$Date,df1$NVDA.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$NVDA.cum.tot),
        # minor.ticks=FALSE,
        main = "NVDA Stock Performance Based on \n Total Returns and Price Returns")
        
lines(df1$Date,df1$NVDA.cum.tot, col = 2, lty = 2)

# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("NVDA.cum.prc", "NVDA.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)
# Customize x-axis labels to show months
# axis(1, at = seq(min(df1$Date), max(df1$Date), by = "3 months"), labels = format(seq(min(df1$Date), max(df1$Date), by = "3 months"), "%Y-%m"), las = 2)

### MSFT

plot(df1$Date,df1$MSFT.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$MSFT.cum.tot),
        # minor.ticks=FALSE,
        main = "MSFT Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$MSFT.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("MSFT.cum.prc", "MSFT.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


### AAPL

plot(df1$Date,df1$AAPL.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$AAPL.cum.tot),
        # minor.ticks=FALSE,
        main = "AAPL Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$AAPL.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("AAPL.cum.prc", "AAPL.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


### NFLX

plot(df1$Date,df1$NFLX.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$NFLX.cum.tot),
        # minor.ticks=FALSE,
        main = "NFLX Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$NFLX.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("NFLX.cum.prc", "NFLX.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)






```



```{r}


## BRK_B

plot(df1$Date,df1$BRK_B.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$BRK_B.cum.tot),
        # minor.ticks=FALSE,
        main = "BRK_B Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$BRK_B.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("BRK_B.cum.prc", "BRK_B.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


##JPM

plot(df1$Date,df1$JPM.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$JPM.cum.tot),
        # minor.ticks=FALSE,
        main = "JPM Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$JPM.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("JPM.cum.prc", "JPM.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


### C

plot(df1$Date,df1$C.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$C.cum.tot),
        # minor.ticks=FALSE,
        main = "C Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$C.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("C.cum.prc", "C.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


### BLK

plot(df1$Date,df1$BLK.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$BLK.cum.tot),
        # minor.ticks=FALSE,
        main = "BLK Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$BLK.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("BLK.cum.prc", "BLK.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)

```

```{r}




### MCD

plot(df1$Date,df1$MCD.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$MCD.cum.tot),
        # minor.ticks=FALSE,
        main = "MCD Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$MCD.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("MCD.cum.prc", "MCD.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


### SKX

plot(df1$Date,df1$SKX.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$SKX.cum.tot),
        # minor.ticks=FALSE,
        main = "SKX Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$SKX.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("SKX.cum.prc", "SKX.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)



### SBUX

plot(df1$Date,df1$SBUX.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$SBUX.cum.tot),
        # minor.ticks=FALSE,
        main = "SBUX Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$SBUX.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("SBUX.cum.prc", "SBUX.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)



### NKE

plot(df1$Date,df1$NKE.cum.prc,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(Daily.cum.rets$NKE.cum.tot),
        # minor.ticks=FALSE,
        main = "NKE Stock Performance Based on \n Total Returns and Price Returns")
lines(df1$Date,df1$NKE.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("NKE.cum.prc", "NKE.cum.tot", "abline(h = 1)"), col = 1:3, lty = 1:3)


```




########################################## PORTFOLIO COMBINED RSUM##########################


```{r}

Daily.rets.rsum <- cbind(Portfolio.prc.ret.rsum[,-c(1)],Portfolio.tot.ret.rsum[,-c(1)])
Daily.rets.rsum[1,]<-0

# Calculate gross returns
Daily.gross.rets.rsum <-1+Daily.rets.rsum
# Define new column names
new_column_names <- c("port15_23gross.prc", "port15_23.gross.tot")

# Set the new column names
colnames(Daily.gross.rets.rsum) <- new_column_names


# Calculate gross returns cumprod
Daily.cum.rets.rsum <-cumprod(Daily.gross.rets.rsum)
new_column_names <- c("port15_23.cum.prc", "port15_23.cum.tot")
colnames(Daily.cum.rets.rsum) <- new_column_names




Daily.rets.rsum[c(1:3,nrow(Daily.rets.rsum)),]

Daily.gross.rets.rsum[c(1:3,nrow(Daily.gross.rets.rsum)),]

Daily.cum.rets.rsum[c(1:3,nrow(Daily.cum.rets.rsum)),]



# Convert xts to data frame
df1.rsum <- data.frame(Date = index(Daily.cum.rets.rsum), coredata(Daily.cum.rets.rsum))



plot(df1.rsum$Date,df1.rsum$port15_23.cum.tot,
        col = 1, lty = 1, lwd=2, 
        type="l",
        # auto.grid=FALSE,
        xlab="Date",
        ylab="Value of Investment ($)",
        ylim=range(df1.rsum$port15_23.cum.tot),
        # minor.ticks=FALSE,
        main = "Portfolio Performance Based on \n Total Returns and Price Returns \n 01-01-2015 to 12-31-2023")


lines(df1.rsum$Date,df1.rsum$port15_23.cum.tot, col = 2, lty = 2)
# Add abline at y = 1
abline(h = 1, col = 3)

# Optionally, add a legend
legend("topleft", legend = c("Port Cum Price", "Port Cum Total", "abline(h = 1)"), col = 1:3, lty = 1:3)


```




*** Note to Self Before Submitting: 
- Check Total Price Returns and Total Gross Returns formula - checked
- Check plot - checked
- Check period - checked

Total 
```{r}
Portfolio.totret.all[c(1:3,nrow(Portfolio.totret.all)),]

multi.2022 <- subset(Portfolio.totret.all,
                    + index(Portfolio.totret.all) >= "2020-12-31" &
                    + index(Portfolio.totret.all) <= "2022-12-31")
multi.2022[c(1:3,nrow(multi.2022))]

period.ret.2022 <- multi.2022[c(1,nrow(multi.2022)),]
period.ret.2022

## Calculate returns for each security over the investment period and convert to df 
rets.2022 <- lapply(period.ret.2022,Delt)
rets.2022

rets.2022.df <- data.frame(rets.2022)
rets.2022.df

rets.2022.df <- rets.2022.df[2,]*100
names(rets.2022.df) <- paste(c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE"))
rets.2022.df

```
####################### Constructing portfolio returns ######################### 



calculate weights for each security

```{r}

# i.NVDA <- 5000
# i.MSFT <- 5000
# i.AAPL <- 5000
# i.NFLX <- 5000
# 
# i.BRK_B<-5000
# i.JPM <- 5000
# i.C   <- 5000
# i.BLK <- 5000
# 
# i.MCD <- 5000
# i.SKX <- 5000
# i.SBUX<- 5000
# i.NKE <- 5000
# 
# w.NVDA <- i.NVDA/(i.NVDA+i.MSFT+i.AAPL+i.NFLX+i.BRK_B+i.JPM+i.C+i.BLK+i.MCD+i.SKX+i.SBUX+i.NKE)
# w.MSFT <- i.MSFT/(i.NVDA+i.MSFT+i.BRK_B+i.JPM)



# Define initial investments
investments <- c(NVDA = 5000, MSFT = 5000, AAPL = 5000, NFLX = 5000,
                 BRK_B = 5000, JPM = 5000, C = 5000, BLK = 5000,
                 MCD = 5000, SKX = 5000, SBUX = 5000, NKE = 5000)

# Calculate w.NVDA
w.NVDA <- investments["NVDA"] / sum(investments)
w.MSFT <- investments["MSFT"] / sum(investments)
w.AAPL <- investments["AAPL"] / sum(investments)
w.NFLX <- investments["NFLX"] / sum(investments)

w.BRK_B <- investments["BRK_B"] / sum(investments)
w.JPM   <- investments["JPM"]   / sum(investments)
w.C     <- investments["C"]     / sum(investments)
w.BLK   <- investments["BLK"]   / sum(investments)

w.MCD   <- investments["MCD"] / sum(investments)
w.SKX   <- investments["SKX"]   / sum(investments)
w.SBUX  <- investments["SBUX"]     / sum(investments)
w.NKE   <- investments["NKE"]   / sum(investments)

# Calculate portfolio returns (weights x return)
port.ret.4asset <- 0
port.ret.4asset <- (w.NVDA*rets.2022.df$NVDA   + w.MSFT*rets.2022.df$MSFT + w.AAPL*rets.2022.df$AAPL + w.NFLX*rets.2022.df$NFLX +
                   w.BRK_B*rets.2022.df$BRK_B + w.JPM*rets.2022.df$JPM   + w.C*rets.2022.df$C + w.BLK*rets.2022.df$BLK +
                   w.MCD*rets.2022.df$MCD + w.SKX*rets.2022.df$SKX   + w.SBUX*rets.2022.df$SBUX + w.NKE*rets.2022.df$NKE)
port.ret.4asset

```
MATRIX METHOD

```{r}
# wgt <- c(0.08333333 ,0.08333333 ,0.08333333 ,0.08333333 )
wgt <- rep(1/12, 12)


mat.wgt <- matrix(wgt,1) 
mat.wgt

ret <- unlist(rets.2022.df)
# ret <- c(rets.2022.df$NVDA,rets.2022.df$MSFT,rets.2022.df$BRK_B,rets.2022.df$JPM)

mat.ret <- matrix(ret,12)
mat.ret


port.ret <- mat.wgt %*% mat.ret
port.ret

```


#####################################################################
Constructing Benchmark Portfolio Returns
#####################################################################



The objective is to create a hypothetical EW and VW portfolio consisting of NVDA, MSFT, BRK_B and JPM using returns in 2022.

```{r}

port <- cbind(Portfolio.totret.all, Portfolio.prcret.all)

port[c(1:3,nrow(port)),]
port$NVDA.ret <- Delt(port$NVDA.Adjusted)
port$MSFT.ret <- Delt(port$MSFT.Adjusted)
port$AAPL.ret <- Delt(port$AAPL.Adjusted)
port$NFLX.ret <- Delt(port$NFLX.Adjusted)


port$BRK_B.ret <- Delt(port$BRK_B.Adjusted)
port$JPM.ret <- Delt(port$JPM.Adjusted)
port$C.ret <- Delt(port$C.Adjusted)
port$BLK.ret <- Delt(port$BLK.Adjusted)


port$MCD.ret <- Delt(port$MCD.Adjusted)
port$SKX.ret <- Delt(port$SKX.Adjusted)
port$SBUX.ret <- Delt(port$SBUX.Adjusted)
port$NKE.ret <- Delt(port$NKE.Adjusted)


port[c(1:3,nrow(port)),]


port.df <- data.frame(Date = index(port), coredata(port))
port.df[c(1:3,nrow(port.df)),]
```

## Portfolio investment period - 2nd last year i.e 2022

```{r}
port.df.2022 <- subset(port.df,
                    port.df$Date >= "2021-12-31" &
                    port.df$Date <= "2022-12-31")
port.df.2022[c(1:3,nrow(port.df.2022)),]

### This is the benchmark portfolio for 2022
```

#########################
Equal-Weighted Portfolio
#########################

Equal-weight to small firms and large firms

Example: S&P 500 Equal Weight Index

The indexes are balanced quarterly which means that in between quarters the constituent weights are allowed to fluctuate based on their performance.

On each rebalancing date, the weights of each firm is set to reset to 1/N (number of securities in the portfolio)


```{r}

ewport <- port.df.2022[c(1,(ncol(port.df.2022)-11):ncol(port.df.2022))] 
ewport[c(1:3,nrow(ewport)),]

names(ewport) <-paste(c("date","NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE"))
rownames(ewport) <-seq(1:nrow(ewport))
ewport[c(1:3,nrow(ewport)),]


## gross returns ( 1 + returns)

ewport.xts <-xts(ewport[, -1], order.by = as.Date(ewport$date))
ewport.xts <- 1+ewport.xts
ewport <- data.frame(date = index(ewport.xts), coredata(ewport.xts))

ewport[c(1:3,nrow(ewport)),]


```
Equally weighted portfolio for Q1 2022

```{r}
## gross returns ( 1 + returns)

ew.q1 <- subset(ewport,
                ewport$date >= as.Date("2021-12-31") &
                ewport$date <= as.Date("2022-03-31"))
ew.q1[c(1:3,nrow(ew.q1)),]

# Set the first row, columns 2:4 to 1
ew.q1[1, 2:ncol(ew.q1)] <- 1

# Apply cumprod to selected columns

# ew.q1$NVDA <- cumprod(ew.q1$NVDA)
# ew.q1$MSFT <- cumprod(ew.q1$MSFT)
# ew.q1$BRK_B <- cumprod(ew.q1$BRK_B)
# ew.q1$JPM <- cumprod(ew.q1$JPM)


columns_to_cumprod <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
ew.q1[columns_to_cumprod] <- cumprod(ew.q1[columns_to_cumprod])   ## Simplified previous code

# Select specific rows and columns
ew.q1[c(1:3, nrow(ew.q1)), ]


```

```{r}
num.sec <- 12 ## Number of securities

ew.q1$NVDA.idx <- (1/num.sec)*(ew.q1$NVDA)  ##(q1.inv/num.sec)
ew.q1$MSFT.idx <- (1/num.sec)*(ew.q1$MSFT)
ew.q1$AAPL.idx <- (1/num.sec)*(ew.q1$AAPL)  
ew.q1$NFLX.idx <- (1/num.sec)*(ew.q1$NFLX)

ew.q1$BRK_B.idx <- (1/num.sec)*(ew.q1$BRK_B)
ew.q1$JPM.idx <- (1/num.sec)*(ew.q1$JPM)
ew.q1$C.idx <- (1/num.sec)*(ew.q1$C)
ew.q1$BLK.idx <- (1/num.sec)*(ew.q1$BLK)

ew.q1$MCD.idx <- (1/num.sec)*(ew.q1$MCD)
ew.q1$SKX.idx <- (1/num.sec)*(ew.q1$SKX)
ew.q1$SBUX.idx <- (1/num.sec)*(ew.q1$SBUX)
ew.q1$NKE.idx <- (1/num.sec)*(ew.q1$NKE)



ew.q1[c(1:3, nrow(ew.q1)), ]

```

```{r}
# q1.val <- data.frame(rowSums(ew.q1[,6:9]))
q1.val <- data.frame(rowSums(ew.q1[,(ncol(ew.q1)-num.sec+1):ncol(ew.q1)]))
q1.val[c(1:3,nrow(q1.val)),]


names(q1.val) <- paste("port.val")
q1.val$date <- ew.q1$date
q1.val[c(1:3,nrow(q1.val)),]

q2.inv <- q1.val[nrow(q1.val),1]
q2.inv

```
The value of 0.8906874 is used at the beginning of the second quarter instead of 1.00



Calculate the index value for each security during the quarter

q1.val holds the portfolio values for the first quarter

q2.inv holds the aggregate portfolio value at the end of Q1

q2.inv will be redistributed equally among three stocks at the beginning of the second quarter
```{r}

ew.q2 <- subset(ewport,
                ewport$date >= as.Date("2022-04-01") &
                ewport$date <= as.Date("2022-06-30"))
ew.q2[c(1:3,nrow(ew.q2)),]

columns_to_cumprod2 <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
ew.q2[columns_to_cumprod2] <- cumprod(ew.q2[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns
ew.q2[c(1:3, nrow(ew.q2)), ]


# ew.q2$NVDA.idx <- (q2.inv/num.sec)*(ew.q2$NVDA)
# ew.q2$MSFT.idx <- (q2.inv/num.sec)*(ew.q2$MSFT)
# ew.q2$BRK_B.idx <- (q2.inv/num.sec)*(ew.q2$BRK_B)
# ew.q2$JPM.idx <- (q2.inv/num.sec)*(ew.q2$JPM)



ew.q2$NVDA.idx <- (q2.inv/num.sec)*(ew.q2$NVDA)  ##(q1.inv/num.sec)
ew.q2$MSFT.idx <- (q2.inv/num.sec)*(ew.q2$MSFT)
ew.q2$AAPL.idx <- (q2.inv/num.sec)*(ew.q2$AAPL)  
ew.q2$NFLX.idx <- (q2.inv/num.sec)*(ew.q2$NFLX)

ew.q2$BRK_B.idx <- (q2.inv/num.sec)*(ew.q2$BRK_B)
ew.q2$JPM.idx <- (q2.inv/num.sec)*(ew.q2$JPM)
ew.q2$C.idx <- (q2.inv/num.sec)*(ew.q2$C)
ew.q2$BLK.idx <- (q2.inv/num.sec)*(ew.q2$BLK)

ew.q2$MCD.idx <- (q2.inv/num.sec)*(ew.q2$MCD)
ew.q2$SKX.idx <- (q2.inv/num.sec)*(ew.q2$SKX)
ew.q2$SBUX.idx <- (q2.inv/num.sec)*(ew.q2$SBUX)
ew.q2$NKE.idx <- (q2.inv/num.sec)*(ew.q2$NKE)



ew.q2[c(1:3, nrow(ew.q2)), ]

q2.val <- data.frame(rowSums(ew.q2[,(ncol(ew.q2)-num.sec+1):ncol(ew.q2)]))
q2.val[c(1:3,nrow(q2.val)),]


names(q2.val) <- paste("port.val")
q2.val$date <- ew.q2$date
q2.val[c(1:3,nrow(q2.val)),]

q3.inv <- q2.val[nrow(q2.val),1]
q3.inv
```


The portfolio is NOT performing well


Quarter 3

```{r}

ew.q3 <- subset(ewport,
                ewport$date >= as.Date("2022-07-01") &
                ewport$date <= as.Date("2022-09-30"))
ew.q3[c(1:3,nrow(ew.q3)),]

columns_to_cumprod2 <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
ew.q3[columns_to_cumprod2] <- cumprod(ew.q3[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns
ew.q3[c(1:3, nrow(ew.q3)), ]


# ew.q3$NVDA.idx <- (q3.inv/num.sec)*(ew.q3$NVDA)
# ew.q3$MSFT.idx <- (q3.inv/num.sec)*(ew.q3$MSFT)
# ew.q3$BRK_B.idx <- (q3.inv/num.sec)*(ew.q3$BRK_B)
# ew.q3$JPM.idx <- (q3.inv/num.sec)*(ew.q3$JPM)


ew.q3$NVDA.idx <- (q3.inv/num.sec)*(ew.q3$NVDA)  
ew.q3$MSFT.idx <- (q3.inv/num.sec)*(ew.q3$MSFT)
ew.q3$AAPL.idx <- (q3.inv/num.sec)*(ew.q3$AAPL)  
ew.q3$NFLX.idx <- (q3.inv/num.sec)*(ew.q3$NFLX)

ew.q3$BRK_B.idx <- (q3.inv/num.sec)*(ew.q3$BRK_B)
ew.q3$JPM.idx <- (q3.inv/num.sec)*(ew.q3$JPM)
ew.q3$C.idx <- (q3.inv/num.sec)*(ew.q3$C)
ew.q3$BLK.idx <- (q3.inv/num.sec)*(ew.q3$BLK)

ew.q3$MCD.idx <- (q3.inv/num.sec)*(ew.q3$MCD)
ew.q3$SKX.idx <- (q3.inv/num.sec)*(ew.q3$SKX)
ew.q3$SBUX.idx <- (q3.inv/num.sec)*(ew.q3$SBUX)
ew.q3$NKE.idx <- (q3.inv/num.sec)*(ew.q3$NKE)



ew.q3[c(1:3, nrow(ew.q3)), ]

q3.val <- data.frame(rowSums(ew.q3[,(ncol(ew.q3)-num.sec+1):ncol(ew.q3)]))
q3.val[c(1:3,nrow(q3.val)),]


names(q3.val) <- paste("port.val")
q3.val$date <- ew.q3$date
q3.val[c(1:3,nrow(q3.val)),]

q4.inv <- q3.val[nrow(q3.val),1]
q4.inv
```


Quarter 4

```{r}

ew.q4 <- subset(ewport,
                ewport$date >= as.Date("2022-10-01") &
                ewport$date <= as.Date("2022-12-31"))
ew.q4[c(1:3,nrow(ew.q4)),]

columns_to_cumprod2 <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
ew.q4[columns_to_cumprod2] <- cumprod(ew.q4[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns
ew.q4[c(1:3, nrow(ew.q4)), ]


# ew.q4$NVDA.idx <- (q4.inv/num.sec)*(ew.q4$NVDA)
# ew.q4$MSFT.idx <- (q4.inv/num.sec)*(ew.q4$MSFT)
# ew.q4$BRK_B.idx <- (q4.inv/num.sec)*(ew.q4$BRK_B)
# ew.q4$JPM.idx <- (q4.inv/num.sec)*(ew.q4$JPM)
# 
# 

ew.q4$NVDA.idx <- (q4.inv/num.sec)*(ew.q4$NVDA)  
ew.q4$MSFT.idx <- (q4.inv/num.sec)*(ew.q4$MSFT)
ew.q4$AAPL.idx <- (q4.inv/num.sec)*(ew.q4$AAPL)  
ew.q4$NFLX.idx <- (q4.inv/num.sec)*(ew.q4$NFLX)

ew.q4$BRK_B.idx <- (q4.inv/num.sec)*(ew.q4$BRK_B)
ew.q4$JPM.idx <- (q4.inv/num.sec)*(ew.q4$JPM)
ew.q4$C.idx <- (q4.inv/num.sec)*(ew.q4$C)
ew.q4$BLK.idx <- (q4.inv/num.sec)*(ew.q4$BLK)

ew.q4$MCD.idx <- (q4.inv/num.sec)*(ew.q4$MCD)
ew.q4$SKX.idx <- (q4.inv/num.sec)*(ew.q4$SKX)
ew.q4$SBUX.idx <- (q4.inv/num.sec)*(ew.q4$SBUX)
ew.q4$NKE.idx <- (q4.inv/num.sec)*(ew.q4$NKE)


ew.q4[c(1:3, nrow(ew.q4)), ]

q4.val <- data.frame(rowSums(ew.q4[,(ncol(ew.q4)-num.sec+1):ncol(ew.q4)]))
q4.val[c(1:3,nrow(q4.val)),]


names(q4.val) <- paste("port.val")
q4.val$date <- ew.q4$date
q4.val[c(1:3,nrow(q4.val)),]

# q5.inv <- q4.val[nrow(q4.val),1]
# q5.inv
```
Combine quarterly EW portfolio values into one data object (ew.portval)
```{r}
ew.portval <- rbind(q1.val,q2.val,q3.val,q4.val)
ew.portval[c(1:3,nrow(ew.portval)),]

```
Please note that this calculations do not include transactions costs incurred during each Q rebalancing.



########################
Value-Weighted Portfolio
########################


```{r}
nsecurities = 12


vwport <-port.df.2022[,-c(2:(nsecurities+1))]
vwport[c(1:3,nrow(vwport)),]


rownames(vwport) <- seq(1:nrow(vwport))
vwport[c(1:3,nrow(vwport)),] 
```
Converting Net Returns to Gross Returns

```{r}
vwport$NVDA.ret <- 1+vwport$NVDA.ret
vwport$MSFT.ret <- 1+vwport$MSFT.ret
vwport$AAPL.ret <- 1+vwport$AAPL.ret
vwport$NFLX.ret <- 1+vwport$NFLX.ret

vwport$BRK_B.ret <- 1+vwport$BRK_B.ret
vwport$JPM.ret <- 1+vwport$JPM.ret
vwport$C.ret <- 1+vwport$C.ret
vwport$BLK.ret <- 1+vwport$BLK.ret

vwport$MCD.ret <- 1+vwport$MCD.ret
vwport$SKX.ret <- 1+vwport$SKX.ret
vwport$SBUX.ret <- 1+vwport$SBUX.ret
vwport$NKE.ret <- 1+vwport$NKE.ret



vwport[c(1:3,nrow(vwport)),]
```

Calculate the market capitalization of each security in the portfolio - Market cap is equal to the price multiplied by the outstanding shares

Construct a series of calendar days

```{r}

date <- seq(as.Date("2021-12-31"),as.Date("2022-12-31"),by=1)
date <- data.frame(date)
date[c(1:3,nrow(date)),]

```
Calculate the market capitalization of each security in the portfolio

-Market cap is equal to the price multiplied by the outstanding shares

Create data object with daily prices, filling in last avialable price on non-trading days
```{r}
PRICE.qtr <- vwport[,c(1:(nsecurities+1))]
PRICE.qtr[c(1:3,nrow(PRICE.qtr)),]
colnames(PRICE.qtr)[colnames(PRICE.qtr) == "Date"] <- "date"
PRICE.qtr[c(1:3,nrow(PRICE.qtr)),]
```
Calculate the market capitalization of each security in the portfolio - Market cap is equal to the price multiplied by the outstanding shares

Create data object with daily prices, filling in last avialable price on non-trading days

Merge date and PRICE.qtr using a combination of the na.locf and merge commands.

The merge command combines two data objects. Using the all.x=TRUE option tells R that when merging we should keep all the data in the “by” variable that is available in the x=date data object.


```{r}
PRICE.qtr <- na.locf(merge(x=date,y=PRICE.qtr,by="date",all.x=TRUE))
PRICE.qtr[c(1:3,nrow(PRICE.qtr)),]

```

Calculate the market capitalization of each security in the portfolio

Market cap is equal to the price multiplied by the outstanding shares
Keep only prices at the end of each calendar quarter


```{r}
PRICE.qtr <- subset(PRICE.qtr,
                    PRICE.qtr$date==as.Date("2021-12-31") |
                    PRICE.qtr$date==as.Date("2022-03-31") |
                    PRICE.qtr$date==as.Date("2022-06-30") |
                    PRICE.qtr$date==as.Date("2022-09-30"))
PRICE.qtr
```

Calculate the market capitalization of each security in the portfolio

Market cap is equal to the price multiplied by the outstanding shares
Obtain shares outstanding data from SEC filings

Available from the SEC EDGAR database (Form 10k - Form 10-Q)
https://www.sec.gov/edgar/browse/?CIK=1018724&owner=exclude

Enter the data manually


<!-- ```{r} -->
<!-- library(edgarWebR) -->

<!-- # Replace "AAPL" with the stock symbol of the company you're interested in -->
<!-- company_cik <- c(1018724) -->

<!-- # Fetch 10-Q filings for the specified company within the date range -->
<!-- filings <- getFilings(company_cik,c('10-K','10-Q'),2013,quarter=c(1,2,3),downl.permit = "n") -->

<!-- # View the obtained filings -->
<!-- print(filings) -->

<!-- ``` -->


NVDA: https://www.sec.gov/edgar/browse/?CIK=1045810&owner=exclude
March 11, 2022: The number of shares of common stock outstanding as of March 11, 2022 was 2.51 billion
May 20, 2022: The number of shares of common stock, $0.001 par value, outstanding as of May 20, 2022, was 2.50 billion.
August 19, 2022: The number of shares of common stock, $0.001 par value, outstanding as of August 19, 2022, was 2.49 billion.
November 11, 2022: TThe number of shares of common stock, $0.001 par value, outstanding as of November 11, 2022, was 2.46 billion .


MSFT: https://www.sec.gov/edgar/browse/?CIK=789019&owner=exclude
Jan 20, 2022: Common Stock, $0.00000625 par value per share 7,496,866,428 shares
Apr 21, 2022: Common Stock, $0.00000625 par value per share  7,479,033,135 shares
July 25, 2022: As of July 25, 2022, there were 7,457,891,872 shares of common stock outstanding.
October 20, 2022 Common Stock, $0.00000625 par value per share 7,454,473,144 shares


AAPL: https://www.sec.gov/edgar/browse/?CIK=320193&owner=exclude
Jan 14, 2022: 16,319,441,000 shares of common stock were issued and outstanding as of January 14, 2022.
Apr 15, 2022: 16,185,181,000 shares of common stock were issued and outstanding as of April 15, 2022.
July 15, 2022: 16,070,752,000 shares of common stock were issued and outstanding as of July 15, 2022.
October 14, 2022: 15,908,118,000 shares of common stock were issued and outstanding as of October 14, 2022.


NFLX: https://www.sec.gov/edgar/browse/?CIK=1065280&owner=exclude
Dec 31, 2021: As of December 31, 2021, there were 443,963,107 shares of the registrant’s common stock, par value $0.001, outstanding.
Mar 21, 2022: As of March 31, 2022, there were 444,273,850 shares of the registrant’s common stock, par value $0.001, outstanding.
Jun 30, 2022: As of June 30, 2022, there were 444,705,591 shares of the registrant’s common stock, par value $0.001, outstanding.
Sep 30, 2022: As of September 30, 2022, there were 445,020,494 shares of the registrant’s common stock, par value $0.001, outstanding.



PRICE.qtr$NVDA.shout <- c(2.51e9,2.50e9,2.49e9,2.46e9)
PRICE.qtr$MSFT.shout <- c(7496866428 ,7479033135 ,7457891872 ,7454473144)
PRICE.qtr$AAPL.shout <- c(16319441000 ,16185181000 ,16070752000 ,15908118000)
PRICE.qtr$NFLX.shout <- c(443963107,444273850,444705591,445020494)





BRK_B: https://www.sec.gov/edgar/browse/?CIK=1067983&owner=exclude
February 14, 2022—Class B common stock, $0.0033 par value 1,291,212,661 shares
April 20, 2022: Number of shares of common stock outstanding as of April 20, 2022:    Class B —  1,285,751,332  
July 26, 2022: Number of shares of common stock outstanding as of July 26, 2022: Class B —  1,301,126,370  
October 2, 2022: Number of shares of common stock outstanding as of October 26, 2022: 	Class B — 1,301,981,370  	  

JPM: https://www.sec.gov/edgar/browse/?CIK=19617&owner=exclude
January 31, 2022: Number of shares of common stock outstanding as of January 31, 2022: 2,952,808,970
March 31, 2022: Number of shares of common stock outstanding as of March 31, 2022: 2,937,050,466
June 30, 2022: Number of shares of common stock outstanding as of June 30, 2022: 2,932,572,390
September 30, 2022: Number of shares of common stock outstanding as of September 30, 2022: 2,933,204,888

C: https://www.sec.gov/edgar/browse/?CIK=831001&owner=exclude
January 31, 2022: Number of shares of Citigroup Inc. common stock outstanding on January 31, 2022: 1,980,894,613
March 31, 2022: Number of shares of Citigroup Inc. common stock outstanding on March 31, 2022: 1,941,920,542
June 30, 2022:Number of shares of Citigroup Inc. common stock outstanding on June 30, 2022: 1,936,709,623
September 30, 2022: Number of shares of Citigroup Inc. common stock outstanding on September 30, 2022: 1,936,852,864

BLK: https://www.sec.gov/edgar/browse/?CIK=1364742&owner=exclude
As of January 31, 2022, there were 152,042,401 shares of the registrant’s common stock outstanding.
As of April 30, 2022, there were 151,503,255 shares of the registrant’s common stock outstanding.
As of July 31, 2022, there were 150,768,739 shares of the registrant’s common stock outstanding.
As of October 31, 2022, there were 150,195,577 shares of the registrant’s common stock outstanding. 


PRICE.qtr$BRK_B.shout <- c(1291212661,1285751332 ,1301126370 ,1301981370)
PRICE.qtr$JPM.shout <- c(2952808970 ,2937050466 ,2932572390 ,2933204888)
PRICE.qtr$C.shout <- c(1980894613 ,1941920542 ,1936709623 ,1936852864)
PRICE.qtr$BLK.shout <- c(152042401 ,151503255 ,150768739 ,150195577)


MCD: https://www.sec.gov/edgar/browse/?CIK=63908&owner=exclude
January 31, 2022: The number of shares outstanding of the registrant’s common stock as of January 31, 2022: 743,584,718.
March 31, 2022: Number of shares of common stock outstanding as of March 31, 2022: 739,546,930
June 30, 2022: Number of shares of common stock outstanding as of June 30, 2022: 735,717,271	
Sept 30, 2022 Number of shares of common stock outstanding as of 9/30/2022: 732,423,892


SKX: https://www.sec.gov/edgar/browse/?CIK=1065837&owner=exclude
February 15, 2022: The number of shares of Class A Common Stock outstanding as of February 15, 2022: 135,107,264.
February 15, 2022: The number of shares of Class B Common Stock outstanding as of February 15, 2022: 20,938,571.
April 28, 2022: As of April 28, 2022, 134,881,830 shares of the registrant’s Class A Common Stock, $0.001 par value per share, were outstanding.
April 28, 2022: As of April 28, 2022, 20,888,571 shares of the registrant’s Class B Common Stock, $0.001 par value per share, were outstanding.
July 29, 2022: As of July 29, 2022, 134,844,529 shares of the registrant’s Class A Common Stock, $0.001 par value per share, were outstanding.
July 29, 2022: As of July 29, 2022, 20,888,571 shares of the registrant’s Class B Common Stock, $0.001 par value per share, were outstanding.
October 28, 2022: As of October 28, 2022, 134,212,238 shares of the registrant’s Class A Common Stock, $0.001 par value per share, were outstanding.
October 28, 2022: As of October 28, 2022, 20,888,571 shares of the registrant’s Class B Common Stock, $0.001 par value per share, were outstanding.

SBUX: https://www.sec.gov/edgar/browse/?CIK=829224&owner=exclude
January 26, 2022: Shares Outstanding as of January 26, 2022: 1,150.3 million
April 27, 2022: Shares Outstanding as of April 27, 2022: 1,146.9 million
July 27, 2022: Shares Outstanding as of July 27, 2022: 1,147.4 million
November 11, 2022: As of November 11, 2022, there were 1,147.8 million shares of the registrant’s Common Stock outstanding.


NKE: 
As of December 27, 2021, the number of shares of the Registrant's Common Stock outstanding were: Class A 305,007,252 	Class B 1,276,288,021 = 1,581,295,273 	
As of March 28, 2022, the number of shares of the Registrant's Common Stock outstanding were: Class A 305,007,252 Class B 1,268,760,217= 1,573,767,469 	
As of July 8, 2022, the number of shares of the Registrant's Common Stock outstanding were: Class A 304,903,252 Class B 1,263,652,653 = 1,568,555,905 	
As of September 29, 2022, the number of shares of the Registrant's Common Stock outstanding were: Class A 304,903,252 Class B 1,259,687,689 = 1,564,590,941 	
  
 
 

PRICE.qtr$MCD.shout <- c(743584718,739546930 ,735717271 ,732423892)
PRICE.qtr$SKX.shout <- c(135107264 ,134881830 ,134844529 ,134212238)
PRICE.qtr$SBUX.shout <- c(1150300000 ,1146900000 ,1147400000 ,1147800000)
PRICE.qtr$NKE.shout <- c(1276288021 ,1268760217 ,1263,652653 ,1259687689)


```{r}
PRICE.qtr$NVDA.shout <- c(2.51e9,2.50e9,2.49e9,2.46e9)
PRICE.qtr$MSFT.shout <- c(7496866428 ,7479033135 ,7457891872 ,7454473144)
PRICE.qtr$AAPL.shout <- c(16319441000 ,16185181000 ,16070752000 ,15908118000)
PRICE.qtr$NFLX.shout <- c(443963107,444273850,444705591,445020494)

PRICE.qtr$BRK_B.shout <- c(1291212661,1285751332 ,1301126370 ,1301981370)
PRICE.qtr$JPM.shout <- c(2952808970 ,2937050466 ,2932572390 ,2933204888)
PRICE.qtr$C.shout <- c(1980894613 ,1941920542 ,1936709623 ,1936852864)
PRICE.qtr$BLK.shout <- c(152042401 ,151503255 ,150768739 ,150195577)

PRICE.qtr$MCD.shout <- c(743584718,739546930 ,735717271 ,732423892)
PRICE.qtr$SKX.shout <- c(135107264 ,134881830 ,134844529 ,134212238)
PRICE.qtr$SBUX.shout <- c(1150300000 ,1146900000 ,1147400000 ,1147800000)
PRICE.qtr$NKE.shout <- c(1276288021 ,1268760217 ,1263652653 ,1259687689)

PRICE.qtr

```
Market cap is equal to the price multiplied by the outstanding shares
Calculate market capitalization for each security

-check that date and closing price are read-in as character variables

```{r}
str(PRICE.qtr)
```
Market cap is equal to the price multiplied by the outstanding shares
To make the data object name more sensible to hold the weights of the securities, copy the data in PRICE.qtr into weights. Calculate the market cap for each security by multiplying that security’s closing price with its shares outstanding.

```{r}
weights <- PRICE.qtr
weights$NVDA.mcap <- weights$NVDA.Close*weights$NVDA.shout
weights$MSFT.mcap <- weights$MSFT.Close*weights$MSFT.shout
weights$AAPL.mcap <- weights$AAPL.Close*weights$AAPL.shout
weights$NFLX.mcap <- weights$NFLX.Close*weights$NFLX.shout

weights$BRK_B.mcap <- weights$BRK_B.Close*weights$BRK_B.shout
weights$JPM.mcap <- weights$JPM.Close*weights$JPM.shout
weights$C.mcap <- weights$C.Close*weights$C.shout
weights$BLK.mcap <- weights$BLK.Close*weights$BLK.shout

weights$MCD.mcap <- weights$MCD.Close*weights$MCD.shout
weights$SKX.mcap <- weights$SKX.Close*weights$SKX.shout
weights$SBUX.mcap <- weights$SBUX.Close*weights$SBUX.shout
weights$NKE.mcap <- weights$NKE.Close*weights$NKE.shout



weights
```
Market cap is equal to the price multiplied by the outstanding shares
Calculate quarter-end aggregate market capitalization

-Apply the rowSums command to the three market capitalization variables (8-10)
```{r}
weights$tot.mcap <- rowSums(weights[(ncol(weights)-(nsecurities-1)):ncol(weights)])
weights

```
Calculate the quarter-end weights of each security in the portfolio

Divide each security’s market cap by the combined market cap of the three securities
```{r}
weights$NVDA.wgt <- weights$NVDA.mcap/weights$tot.mcap
weights$MSFT.wgt <- weights$MSFT.mcap/weights$tot.mcap
weights$AAPL.wgt <- weights$AAPL.mcap/weights$tot.mcap
weights$NFLX.wgt <- weights$NFLX.mcap/weights$tot.mcap

weights$BRK_B.wgt <- weights$BRK_B.mcap/weights$tot.mcap
weights$JPM.wgt <- weights$JPM.mcap/weights$tot.mcap
weights$C.wgt <- weights$C.mcap/weights$tot.mcap
weights$BLK.wgt <- weights$BLK.mcap/weights$tot.mcap

weights$MCD.wgt <- weights$MCD.mcap/weights$tot.mcap
weights$SKX.wgt <- weights$SKX.mcap/weights$tot.mcap
weights$SBUX.wgt <- weights$SBUX.mcap/weights$tot.mcap
weights$NKE.wgt <- weights$NKE.mcap/weights$tot.mcap


weights


WEIGHT <- weights[,c(1,(ncol(weights)-11):ncol(weights))]
WEIGHT

```
Calculate the quarter-end weights of each security in the portfolio

To apply the weights to the start of the following quarter, add one to all dates

```{r}
WEIGHT$date <- WEIGHT$date+1
WEIGHT
```
Calculating the quarterly VW portfolio values (similar to EW portfolio)

Create series of dates to find the applicable weights at the beginning of each quarter

```{r}

date <- seq(as.Date("2021-12-31"),as.Date("2022-12-31"),by=1)
date <- data.frame(date)
date[c(1:3,nrow(date)),]

```


```{r}
vwret <- na.locf(merge(date,WEIGHT,by="date",all.x=TRUE))
vwret[c(1:3,nrow(vwret)),] 
```


Check date as.date and wgt as.num
```{r}
str(vwret)

```



```{r}
q1.vw.wgt <- subset(vwret,vwret$date==as.Date("2022-01-01"))  ## 2012-01-02 was new years day holiday. 01/01 was Sunday
q1.vw.wgt
q2.vw.wgt <- subset(vwret,vwret$date==as.Date("2022-04-01"))
q2.vw.wgt
q3.vw.wgt <- subset(vwret,vwret$date==as.Date("2022-07-01"))
q3.vw.wgt
q4.vw.wgt <- subset(vwret,vwret$date==as.Date("2022-10-01"))
q4.vw.wgt

```


```{r}

Q1.pie.values <- as.numeric(q1.vw.wgt[,-1])
Q1.pie.labels <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
pct <- round(Q1.pie.values*100)
Q1.pie.labels <- paste(Q1.pie.labels,pct) #Add pct
Q1.pie.labels <- paste(Q1.pie.labels,"%",sep="") #Add % sign
pie(Q1.pie.values,
    labels=Q1.pie.labels,
    col=1:12,
    main="Q1 Value Weigthing")


Q2.pie.values <- as.numeric(q2.vw.wgt[,-1])
Q2.pie.labels <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
pct <- round(Q2.pie.values*100)
Q2.pie.labels <- paste(Q2.pie.labels,pct) #Add pct
Q2.pie.labels <- paste(Q2.pie.labels,"%",sep="") #Add % sign
pie(Q2.pie.values,
    labels=Q2.pie.labels,
    col=1:12,
    main="Q2 Value Weigthing")


Q3.pie.values <- as.numeric(q3.vw.wgt[,-1])
Q3.pie.labels <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
pct <- round(Q3.pie.values*100)
Q3.pie.labels <- paste(Q3.pie.labels,pct) #Add pct
Q3.pie.labels <- paste(Q3.pie.labels,"%",sep="") #Add % sign
pie(Q3.pie.values,
    labels=Q3.pie.labels,
    col=1:12,
    main="Q3 Value Weigthing")


Q4.pie.values <- as.numeric(q4.vw.wgt[,-1])
Q4.pie.labels <- c("NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")
pct <- round(Q4.pie.values*100)
Q4.pie.labels <- paste(Q4.pie.labels,pct) #Add pct
Q4.pie.labels <- paste(Q4.pie.labels,"%",sep="") #Add % sign
pie(Q4.pie.values,
    labels=Q4.pie.labels,
    col=1:12,
    main="Q4 Value Weigthing")


```
Calculating VW portfolio values for 1Q 2012 (similar to the EW portfolio)

Subset vwport to the data from Dec 31, 2011 to March 31, 2012

```{r}

vw.q1 <- subset(vwport[,c(1,(ncol(vwport)-(nsecurities-1)):ncol(vwport))], 
                vwport$Date >= as.Date("2021-12-31") &
                vwport$Date <= as.Date("2022-03-31"))
names(vw.q1) <- paste(c("date","NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")) # shorten the names
vw.q1[c(1:3,nrow(vw.q1)),]


vw.q1[1,2:ncol(vw.q1)] <-1  ### delete fisrt row because it lies in q4 of last year 
vw.q1$NVDA <- cumprod(vw.q1$NVDA)
vw.q1$MSFT <- cumprod(vw.q1$MSFT)
vw.q1$AAPL <- cumprod(vw.q1$AAPL)
vw.q1$NFLX <- cumprod(vw.q1$NFLX)

vw.q1$BRK_B <- cumprod(vw.q1$BRK_B)
vw.q1$JPM <- cumprod(vw.q1$JPM)
vw.q1$C <- cumprod(vw.q1$C)
vw.q1$BLK <- cumprod(vw.q1$BLK)

vw.q1$MCD <- cumprod(vw.q1$MCD)
vw.q1$SKX <- cumprod(vw.q1$SKX)
vw.q1$SBUX <- cumprod(vw.q1$SBUX)
vw.q1$NKE <- cumprod(vw.q1$NKE)

vw.q1[c(1:3,nrow(vw.q1)),]


vw.q1$NVDA.idx <- (1*q1.vw.wgt$NVDA.wgt)*vw.q1$NVDA
vw.q1$MSFT.idx <- (1*q1.vw.wgt$MSFT.wgt)*vw.q1$MSFT
vw.q1$AAPL.idx <- (1*q1.vw.wgt$AAPL.wgt)*vw.q1$AAPL
vw.q1$NFLX.idx <- (1*q1.vw.wgt$NFLX.wgt)*vw.q1$NFLX

vw.q1$BRK_B.idx <- (1*q1.vw.wgt$BRK_B.wgt)*vw.q1$BRK_B
vw.q1$JPM.idx <- (1*q1.vw.wgt$JPM.wgt)*vw.q1$JPM
vw.q1$C.idx <- (1*q1.vw.wgt$C.wgt)*vw.q1$C
vw.q1$BLK.idx <- (1*q1.vw.wgt$BLK.wgt)*vw.q1$BLK

vw.q1$MCD.idx <- (1*q1.vw.wgt$MCD.wgt)*vw.q1$MCD
vw.q1$SKX.idx <- (1*q1.vw.wgt$SKX.wgt)*vw.q1$SKX
vw.q1$SBUX.idx <- (1*q1.vw.wgt$SBUX.wgt)*vw.q1$SBUX
vw.q1$NKE.idx <- (1*q1.vw.wgt$NKE.wgt)*vw.q1$NKE

vw.q1[c(1:3,nrow(vw.q1)),]



q1.vw.val <- data.frame(rowSums(vw.q1[,(ncol(vw.q1)-(nsecurities-1)):ncol(vw.q1)]))
q1.vw.val[c(1:3,nrow(q1.vw.val)),]

names(q1.vw.val) <- paste("port.val")
q1.vw.val$date <- vw.q1$date
q1.vw.val[c(1:3,nrow(q1.vw.val)),]



q1.vw.inv <- q1.vw.val[nrow(q1.vw.val),1]
q1.vw.inv
```


Subset vwport to the data from Mar 2022 to Jun 2022
```{r}

vw.q2 <- subset(vwport[,c(1,(ncol(vwport)-(nsecurities-1)):ncol(vwport))], 
                vwport$Date >= as.Date("2022-04-01") &
                vwport$Date <= as.Date("2022-06-30"))
names(vw.q2) <- paste(c("date","NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")) # shorten the names
vw.q2[c(1:3,nrow(vw.q2)),]


# vw.q2[1,2:ncol(vw.q2)] <-1  ### delete fisrt row because it lies in q4 of last year 
vw.q2$NVDA <- cumprod(vw.q2$NVDA)
vw.q2$MSFT <- cumprod(vw.q2$MSFT)
vw.q2$AAPL <- cumprod(vw.q2$AAPL)
vw.q2$NFLX <- cumprod(vw.q2$NFLX)

vw.q2$BRK_B <- cumprod(vw.q2$BRK_B)
vw.q2$JPM <- cumprod(vw.q2$JPM)
vw.q2$C <- cumprod(vw.q2$C)
vw.q2$BLK <- cumprod(vw.q2$BLK)

vw.q2$MCD <- cumprod(vw.q2$MCD)
vw.q2$SKX <- cumprod(vw.q2$SKX)
vw.q2$SBUX <- cumprod(vw.q2$SBUX)
vw.q2$NKE <- cumprod(vw.q2$NKE)

vw.q2[c(1:3,nrow(vw.q2)),]


vw.q2$NVDA.idx <- (1*q2.vw.wgt$NVDA.wgt)*vw.q2$NVDA
vw.q2$MSFT.idx <- (1*q2.vw.wgt$MSFT.wgt)*vw.q2$MSFT
vw.q2$AAPL.idx <- (1*q2.vw.wgt$AAPL.wgt)*vw.q2$AAPL
vw.q2$NFLX.idx <- (1*q2.vw.wgt$NFLX.wgt)*vw.q2$NFLX

vw.q2$BRK_B.idx <- (1*q2.vw.wgt$BRK_B.wgt)*vw.q2$BRK_B
vw.q2$JPM.idx <- (1*q2.vw.wgt$JPM.wgt)*vw.q2$JPM
vw.q2$C.idx <- (1*q2.vw.wgt$C.wgt)*vw.q2$C
vw.q2$BLK.idx <- (1*q2.vw.wgt$BLK.wgt)*vw.q2$BLK

vw.q2$MCD.idx <- (1*q2.vw.wgt$MCD.wgt)*vw.q2$MCD
vw.q2$SKX.idx <- (1*q2.vw.wgt$SKX.wgt)*vw.q2$SKX
vw.q2$SBUX.idx <- (1*q2.vw.wgt$SBUX.wgt)*vw.q2$SBUX
vw.q2$NKE.idx <- (1*q2.vw.wgt$NKE.wgt)*vw.q2$NKE

vw.q2[c(1:3,nrow(vw.q2)),]



q2.vw.val <- data.frame(rowSums(vw.q2[,(ncol(vw.q2)-(nsecurities-1)):ncol(vw.q2)]))
q2.vw.val[c(1:3,nrow(q2.vw.val)),]

names(q2.vw.val) <- paste("port.val")
q2.vw.val$date <- vw.q2$date
q2.vw.val[c(1:3,nrow(q2.vw.val)),]



q2.vw.inv <- q2.vw.val[nrow(q2.vw.val),1]
q2.vw.inv
```

Subset vwport to the data from Jul 2022 to Sep 2022
```{r}

vw.q3 <- subset(vwport[,c(1,(ncol(vwport)-(nsecurities-1)):ncol(vwport))], 
                vwport$Date >= as.Date("2022-07-01") &
                vwport$Date <= as.Date("2022-09-30"))
names(vw.q3) <- paste(c("date","NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")) # shorten the names
vw.q3[c(1:3,nrow(vw.q3)),]


# vw.q3[1,2:ncol(vw.q3)] <-1  ### delete fisrt row because it lies in q4 of last year 
vw.q3$NVDA <- cumprod(vw.q3$NVDA)
vw.q3$MSFT <- cumprod(vw.q3$MSFT)
vw.q3$AAPL <- cumprod(vw.q3$AAPL)
vw.q3$NFLX <- cumprod(vw.q3$NFLX)

vw.q3$BRK_B <- cumprod(vw.q3$BRK_B)
vw.q3$JPM <- cumprod(vw.q3$JPM)
vw.q3$C <- cumprod(vw.q3$C)
vw.q3$BLK <- cumprod(vw.q3$BLK)

vw.q3$MCD <- cumprod(vw.q3$MCD)
vw.q3$SKX <- cumprod(vw.q3$SKX)
vw.q3$SBUX <- cumprod(vw.q3$SBUX)
vw.q3$NKE <- cumprod(vw.q3$NKE)

vw.q3[c(1:3,nrow(vw.q3)),]


vw.q3$NVDA.idx <- (1*q3.vw.wgt$NVDA.wgt)*vw.q3$NVDA
vw.q3$MSFT.idx <- (1*q3.vw.wgt$MSFT.wgt)*vw.q3$MSFT
vw.q3$AAPL.idx <- (1*q3.vw.wgt$AAPL.wgt)*vw.q3$AAPL
vw.q3$NFLX.idx <- (1*q3.vw.wgt$NFLX.wgt)*vw.q3$NFLX

vw.q3$BRK_B.idx <- (1*q3.vw.wgt$BRK_B.wgt)*vw.q3$BRK_B
vw.q3$JPM.idx <-   (1*q3.vw.wgt$JPM.wgt)*vw.q3$JPM
vw.q3$C.idx <-     (1*q3.vw.wgt$C.wgt)*vw.q3$C
vw.q3$BLK.idx <-   (1*q3.vw.wgt$BLK.wgt)*vw.q3$BLK

vw.q3$MCD.idx <- (1*q3.vw.wgt$MCD.wgt)*vw.q3$MCD
vw.q3$SKX.idx <- (1*q3.vw.wgt$SKX.wgt)*vw.q3$SKX
vw.q3$SBUX.idx <- (1*q3.vw.wgt$SBUX.wgt)*vw.q3$SBUX
vw.q3$NKE.idx <- (1*q3.vw.wgt$NKE.wgt)*vw.q3$NKE

vw.q3[c(1:3,nrow(vw.q3)),]



q3.vw.val <- data.frame(rowSums(vw.q3[,(ncol(vw.q3)-(nsecurities-1)):ncol(vw.q3)]))
q3.vw.val[c(1:3,nrow(q3.vw.val)),]

names(q3.vw.val) <- paste("port.val")
q3.vw.val$date <- vw.q3$date
q3.vw.val[c(1:3,nrow(q3.vw.val)),]



q3.vw.inv <- q3.vw.val[nrow(q3.vw.val),1]
q3.vw.inv
```


Subset vwport to the data from Oct 2012 to Dec 2012


```{r}

vw.q4 <- subset(vwport[,c(1,(ncol(vwport)-(nsecurities-1)):ncol(vwport))], 
                vwport$Date >= as.Date("2022-10-01") &
                vwport$Date <= as.Date("2022-12-31"))
names(vw.q4) <- paste(c("date","NVDA","MSFT","AAPL","NFLX","BRK_B","JPM","C","BLK","MCD","SKX","SBUX","NKE")) # shorten the names
vw.q4[c(1:3,nrow(vw.q4)),]


# vw.q3[1,2:ncol(vw.q3)] <-1  ### delete fisrt row because it lies in q4 of last year 
vw.q4$NVDA <- cumprod(vw.q4$NVDA)
vw.q4$MSFT <- cumprod(vw.q4$MSFT)
vw.q4$AAPL <- cumprod(vw.q4$AAPL)
vw.q4$NFLX <- cumprod(vw.q4$NFLX)

vw.q4$BRK_B <- cumprod(vw.q4$BRK_B)
vw.q4$JPM <- cumprod(vw.q4$JPM)
vw.q4$C <- cumprod(vw.q4$C)
vw.q4$BLK <- cumprod(vw.q4$BLK)

vw.q4$MCD <- cumprod(vw.q4$MCD)
vw.q4$SKX <- cumprod(vw.q4$SKX)
vw.q4$SBUX <- cumprod(vw.q4$SBUX)
vw.q4$NKE <- cumprod(vw.q4$NKE)

vw.q4[c(1:3,nrow(vw.q4)),]


vw.q4$NVDA.idx <- (1*q4.vw.wgt$NVDA.wgt)*vw.q4$NVDA
vw.q4$MSFT.idx <- (1*q4.vw.wgt$MSFT.wgt)*vw.q4$MSFT
vw.q4$AAPL.idx <- (1*q4.vw.wgt$AAPL.wgt)*vw.q4$AAPL
vw.q4$NFLX.idx <- (1*q4.vw.wgt$NFLX.wgt)*vw.q4$NFLX

vw.q4$BRK_B.idx <- (1*q4.vw.wgt$BRK_B.wgt)*vw.q4$BRK_B
vw.q4$JPM.idx <- (1*q4.vw.wgt$JPM.wgt)*vw.q4$JPM
vw.q4$C.idx <- (1*q4.vw.wgt$C.wgt)*vw.q4$C
vw.q4$BLK.idx <- (1*q4.vw.wgt$BLK.wgt)*vw.q4$BLK

vw.q4$MCD.idx <- (1*q4.vw.wgt$MCD.wgt)*vw.q4$MCD
vw.q4$SKX.idx <- (1*q4.vw.wgt$SKX.wgt)*vw.q4$SKX
vw.q4$SBUX.idx <- (1*q4.vw.wgt$SBUX.wgt)*vw.q4$SBUX
vw.q4$NKE.idx <- (1*q4.vw.wgt$NKE.wgt)*vw.q4$NKE

vw.q4[c(1:3,nrow(vw.q4)),]



q4.vw.val <- data.frame(rowSums(vw.q4[,(ncol(vw.q4)-(nsecurities-1)):ncol(vw.q4)]))
q4.vw.val[c(1:3,nrow(q4.vw.val)),]

names(q4.vw.val) <- paste("port.val")
q4.vw.val$date <- vw.q4$date
q4.vw.val[c(1:3,nrow(q4.vw.val)),]



q4.vw.inv <- q4.vw.val[nrow(q4.vw.val),1]
q4.vw.inv
```


Combining: 

```{r}
vw.portval <- rbind(q1.vw.val,q2.vw.val,q3.vw.val,q4.vw.val)
vw.portval[c(1:3,nrow(vw.portval)),]

```


```{r}
port.val <- merge(vw.portval,ew.portval,by="date")
names(port.val) <- paste(c("date","VW.cum","EW.cum"))
port.val[c(1:3,nrow(port.val)),]

```

```{r}
y.range <-range(port.val[,2:3])
plot(port.val$EW.cum,
     type="l",
     xlab="Date",
     ylab="Value of Investment",
     ylim=y.range,
     lty=1,
     main="Value of $1 Investment in Equal-Weighted and Value-Weighted Portfolios \n of 12 stocks \n December 31, 2021 - December 31, 2022")
lines(port.val$VW.cum,lty=2)
abline(h=1,lty=1)
legend("topleft",
       c("Equal-Weighted Portfolio","Value-Weighted Portfolio"),
       lty=c(1,2))


```
Saving benchmark portfolio returns into a CSV file
```{r}
port.xts <-xts(port.val[,2:3],order.by=port.val[,1])

port.xts$Lag.VW <- Lag(port.xts$VW.cum,k=1)
port.xts$Lag.EW <- Lag(port.xts$EW.cum,k=1)

port.xts$VW.ret <- port.xts$VW.cum/port.xts$Lag.VW-1
port.xts$EW.ret <- port.xts$EW.cum/port.xts$Lag.EW-1

Port.Ret <- port.xts[,c(1,2,5,6)]
Port.Ret[c(1:3,nrow(Port.Ret)),]


```


```{r}
csv.port <- cbind(data.frame(index(Port.Ret)),data.frame(Port.Ret))
names(csv.port)[1]<- paste("date")
csv.port[c(1:3,nrow(csv.port)),]

```


```{r}
rownames(csv.port) <- seq(1:nrow(csv.port))
csv.port[c(1:3,nrow(csv.port)),]

```


```{r}
write.csv(csv.port,"Hypothetical Portfolio (Daily).csv")
```


References: <br>

[1] Module 1 importing data <br>

[2] Module 2 individual returns <br>

[3] Module 3 portfolio returns<br>

[4] Stackoverflow - for errors associated with Rstudio<br>

[5] ChatGPT - for code troubleshooting<br>
