---
title: "ANLY515 Group Project Saurabh v7 Diversification Reconsideration"
author: "Saurabh Shirish Prabhu"
date: "`r Sys.Date()`"
output: word_document
---
```{r setup, include=FALSE}
rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE)
dir.create(tempdir())
```

Importing data from Yahoo finance:

```{r}
getwd()
setwd('F:/a_Harrisburg_University_Academics/ANLY 515-51- A-2024Spring - Risk Modeling and Assessment/Final Project/Code')
getwd()
```
This section contains
Lecture-11---Diversification-Reconsidered

Portfolios
Examples :

The global-minimum variance portfolio.

The most diversified Portfolio,

The equal-risk contributed Portfolio

Minimum tail-dependent portfolio

All optimization approaches have a common goal, namely to minimize the investor’s risk through diversification

Select two market sectors from the 11 sectors identified on this
reference o <https://www.bloomberg.com/markets/sectors>

Answer:

[1]Information Technology<br>

1.1 Semiconductors & Semiconductor Equipment: NVIDIA Corporation (NVDA)<br>
1.2 Software & Services: Microsoft Corporation (MSFT)<br>
1.3 Software & Services: Apple Inc. (AAPL)<br>
1.4 Software & Services: Netflix Inc. (NFLX)<br>


[2]Financials<br>

2.1 Insurance: Berkshire Hathaway Inc. (BRK.B)<br>
2.2 Banks: JPMorgan Chase & Co. (JPM)<br>
2.3 Banks: CitiGroup Inc. (C)<br>
2.4 Insurance: BlackRock Inc. (BLK)<br>



[3]Consumer Discretionary:<br>

3.1 Retailing: McDonald's Corporation (MCD)<br>
3.2 Consumer Durables & Apparel: Skechers U.S.A., Inc. (SKX)<br>
3.3 Retailing: Starbucks Corp. (SBUX) <br>
3.4 Consumer Durables & Apparel: Nike Inc. (NKE)



[4]Industrials: <br>

4.1 Capital Goods: Cummins Inc. (CMI)<br>
4.2 Capital Goods:Deere & Company (DE)<br>


References: <br>
[1]<https://stockanalysis.com/stocks/industry/><br>
[2]<https://medium.com/\@sil.soham/importing-and-visualising-stock-market-data-in-r-ac5a22e23cd><br>


Import all necessary libraries

```{r}
library(quantmod)
library(xts)
library(dplyr)
library(corrplot)
```

Load all stocks



• Confirm that there is no missing data<br> 
• Check the dimensions to
verify that the data covers 5 years<br>
```{r}

start <- as.Date("2014-12-31",format="%Y-%m-%d")
end <- as.Date("2023-12-31",format="%Y-%m-%d")

# Use getSymbols to retrieve the data

# [1]Information Technology
data.NVDA <- getSymbols("NVDA", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.MSFT <- getSymbols("MSFT", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.AAPL <- getSymbols("AAPL", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NFLX <- getSymbols("NFLX", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [2]Financials
data.BRK_B <- getSymbols("BRK-B", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.JPM <- getSymbols("JPM", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.C <- getSymbols("C", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.BLK <- getSymbols("BLK", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [3]Consumer Discretionary:
data.MCD <- getSymbols("MCD", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SKX <- getSymbols("SKX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SBUX <- getSymbols("SBUX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NKE <- getSymbols("NKE", src = "yahoo", from = start, to = end, auto.assign = FALSE)
# Assign the class "xts" and "zoo" explicitly
# class(data.NVDA) <- c("xts", "zoo")
# Print the class of the assigned variable
class(data.NVDA)



names(data.BRK_B)
names(data.BRK_B) <- paste(c("BRK_B.Open","BRK_B.High","BRK_B.Low","BRK_B.Close","BRK_B.Volume","BRK_B.Adjusted"))
names(data.BRK_B)

```
```{r}
### Sector 1: Information Technology: MSFT and NVDA
Infotech.Adjusted.Prices <- data.NVDA$NVDA.Adjusted
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.MSFT$MSFT.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.AAPL$AAPL.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.NFLX$NFLX.Adjusted)
# Infotech.Adjusted.Prices[c(1:3,nrow(Infotech.Adjusted.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Adjusted.Prices <- data.BRK_B$BRK_B.Adjusted
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.JPM$JPM.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.C$C.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.BLK$BLK.Adjusted)
# Financials.Adjusted.Prices[c(1:3,nrow(Financials.Adjusted.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Adjusted.Prices <- data.MCD$MCD.Adjusted
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SKX$SKX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SBUX$SBUX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.NKE$NKE.Adjusted)
# Consumer.Adjusted.Prices[c(1:3,nrow(Consumer.Adjusted.Prices)),]


########
### Entire portfolio
Portfolio.Adj.all <- cbind(Infotech.Adjusted.Prices,Financials.Adjusted.Prices,Consumer.Adjusted.Prices)
Portfolio.Adj.all[c(1:3,nrow(Portfolio.Adj.all)),]

str(Portfolio.Adj.all)
summary(Portfolio.Adj.all)
```
Portfolios
Examples :

The global-minimum variance portfolio.

The most diversified Portfolio,

The equal-risk contributed Portfolio

Minimum tail-dependent portfolio

All optimization approaches have a common goal, namely to minimize the investor’s risk through diversification


```{r}

library(fPortfolio)
library(lattice)

```

All optimizations will be carried out with the functions provided in FRAPO. The utilized data set is contained in the package fPortfolio and the base package lattice will be employed in the graphical analysis of the results.

Loading data and calculating returns

interNA: NA values are interpolated

Discrete daily returns are computed as well as the variance-covariance matrix

Calculate return time series 

```{r}
port.df <- data.frame(date = index(Portfolio.Adj.all), coredata(Portfolio.Adj.all))
port.df[c(1:3,nrow(port.df)),]


Port.rets <-port.df
date<-Port.rets$date
# str(date)

PortRet.price <- Port.rets[,-1]


attr(PortRet.price, 'time')<-date   ##add time attribute to dataset
# str(PortRet.price)

prc2ret <- function(x) Delt(x)


Port.rets.all <- apply(PortRet.price,2,function(x) {prc2ret(c(x))})



colnames(Port.rets.all) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )

## Add date column


Port.rets.all = data.frame(Port.rets.all)
Port.rets.all$date <- port.df$date

# summary(PortRet_2013)
# str(PortRet_2013)
# head(PortRet_2013)
attr(Port.rets.all, 'time')<-date
# str(Port.rets.all)
head(Port.rets.all)


### reorder to get date in first column
# Get the index of the 'date' column
date_column_index <- which(names(Port.rets.all) == "date")

# Move 'date' column to the first position
new_order <- c(date_column_index, 1:(ncol(Port.rets.all)-1)[-date_column_index+1])

# Rearrange the columns of the data frame
Port.rets.df <- Port.rets.all[, new_order]


# Replace NA in the first row with 1

Port.rets.df <- Port.rets.df[, -1]
Port.rets.df[1,] <- 0
Port.rets.df <- Port.rets.df+1
# Add the "date" column back to the dataframe
Port.rets.df$date <- as.Date(Port.rets$date)  # Assuming "date" is already a column in Port.rets

# Reorder columns to have "date" as the first column
Port.rets.df <- Port.rets.df[, c("date", setdiff(names(Port.rets.df), "date"))]

# Print the first few rows of the dataframe
head(Port.rets.df)
tail(Port.rets.df)
```



Calculate return time series 


```{r}


library(FRAPO)

Idx <- interpNA(Port.rets.df[, -1], method = "before")
R <- returnseries(Idx, method = "discrete", trim = TRUE)
V <- cov(R)
head(Idx)
head(R)
V
```
The allocations according to the four portfolio optimizations are then extracted by means of the Weights() method and assigned to the objects GMVw, MDPw, MTDw, and ERCw for the global-minimum variance, most-diversified, minimum tail-dependent, and equal-risk contributed solutions, respectively.
```{r}
GMVw <- Weights(PGMV(R))

```
```{r}
MDPw <- Weights(PMD(R))
```
```{r}
MTDw <- Weights(PMTD(R))
```
```{r}
ERCw <- Weights(PERC(V))

```
The weights are then collected in the matrix object W.

This object is then used in the call to the apply() function to determine the marginal risk contributions for each of the four optimal weight vectors.

```{r}
W <- cbind(GMVw, MDPw, MTDw, ERCw)
MRC <- apply(W, 2, mrc, Sigma = V)
rownames(MRC) <- colnames(Idx)
colnames(MRC) <- c("GMV", "MDP", "MTD", "ERC")
```

```{r}
# oldpar <- par(no.readonly = TRUE)
# par(mfrow = c(2, 2))
dotchart(GMVw, xlim = c(0, 40), main = "GMV Allocation", pch = 19)
dotchart(MDPw - GMVw, xlim = c(-20, 20), main = "MDP vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
dotchart(MTDw - GMVw, xlim = c(-20, 20), main = "MTD vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
dotchart(ERCw - GMVw, xlim = c(-20, 20), main = "ERC vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
```
The weights are displayed in the form of dot charts. Usually, asset allocations are portrayed as pie charts. However, this kind of visualization is problematic, because the relation of surfaces and their sizes cannot be well digested by visual inspection.

GMV: Global Minimum Variance

MDP: Most Diversified Portfolio

MTD: Minimum Tail Dependence

ERC: Equal Risk Contribution

```{r}
# par(oldpar)

```


The marginal risk contributions (MRCs) for each of the portfolios are shown as dot plots. Here, the MRCs are ordered by sector and per portfolio optimization and by portfolio and per sector. In order to do so, the sectors and the kind of portfolio have to be coerced to factors and then this kind of lattice plot can be produced by the formula arguments in the calls to the dotplot() function which is part of the package lattice.
```{r}
Sector <- factor(rep(rownames(MRC), 4),
                 levels = sort(rownames(MRC)))
Port <- factor(rep(colnames(MRC), each = 12),
               levels = colnames(MRC))
MRCdf <- data.frame(MRC = c(MRC), Port, Sector)
dotplot(Sector ~ MRC | Port, groups = Port, data = MRCdf,
        xlab = "Percentages",
        main = "Marginal Risk Contributions by Security per Portfolio",
        col = "black", pch = 19)
```








Per Sector


### Portfolio - 2023 total returns ### END


#### Equally weighted portfolio ###
 
```{r}
port<- Portfolio.Adj.all
port$NVDA.ret <- Delt(port$NVDA.Adjusted)
port$MSFT.ret <- Delt(port$MSFT.Adjusted)
port$AAPL.ret <- Delt(port$AAPL.Adjusted)
port$NFLX.ret <- Delt(port$NFLX.Adjusted)

port$BRK_B.ret <- Delt(port$BRK_B.Adjusted)
port$JPM.ret <- Delt(port$JPM.Adjusted)
port$C.ret <- Delt(port$C.Adjusted)
port$BLK.ret <- Delt(port$BLK.Adjusted)

port$MCD.ret <- Delt(port$MCD.Adjusted)
port$SKX.ret <- Delt(port$SKX.Adjusted)
port$SBUX.ret <- Delt(port$SBUX.Adjusted)
port$NKE.ret <- Delt(port$NKE.Adjusted)

# port[c(1:3,nrow(port)),]


port.df <- data.frame(Date = index(port), coredata(port))
port.df[c(1:3,nrow(port.df)),]


nsecurities = 12

ewport <- port.df[c(1,(ncol(port.df)-(nsecurities-1)):ncol(port.df))] 
# ewport[c(1:3,nrow(ewport)),]
names(ewport) <-paste(c("date",
                        "NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE"))

rownames(ewport) <-seq(1:nrow(ewport))
# ewport[c(1:3,nrow(ewport)),]

## gross returns ( 1 + returns)

ewport.xts <-xts(ewport[, -1], order.by = as.Date(ewport$date))
ewport.xts <- 1+ewport.xts
ewport <- data.frame(date = index(ewport.xts), coredata(ewport.xts))

ewport[c(1:3,nrow(ewport)),]
```



```{r}
# Infotech.Adjusted.Prices



# year 1 inv / returns


### Year 1 

ew.y1<- subset(ewport,
                ewport$date >= as.Date("2014-12-31") &
                ewport$date <= as.Date("2015-12-31"))

ew.y1[1, 2:ncol(ew.y1)] <- 1

# Apply cumprod to selected columns
columns_to_cumprod <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")

ew.y1[columns_to_cumprod] <- cumprod(ew.y1[columns_to_cumprod])   ## Simplified previous code
head(ew.y1)


# Select specific rows and columns
ew.y1[c(1:3, nrow(ew.y1)), ]

num.sec = 4

ew.y1$NVDA.idx <- (1/num.sec)*(ew.y1$NVDA)  ##(q1.inv/num.sec)
ew.y1$MSFT.idx <- (1/num.sec)*(ew.y1$MSFT)
ew.y1$AAPL.idx <- (1/num.sec)*(ew.y1$AAPL)
ew.y1$NFLX.idx <- (1/num.sec)*(ew.y1$NFLX)

ew.y1$BRK_B.idx <- (1/num.sec)*(ew.y1$BRK_B)
ew.y1$JPM.idx <- (1/num.sec)*(ew.y1$JPM)
ew.y1$C.idx <- (1/num.sec)*(ew.y1$C)
ew.y1$BLK.idx <- (1/num.sec)*(ew.y1$BLK)

ew.y1$MCD.idx <- (1/num.sec)*(ew.y1$MCD)
ew.y1$SKX.idx <- (1/num.sec)*(ew.y1$SKX)
ew.y1$SBUX.idx <- (1/num.sec)*(ew.y1$SBUX)
ew.y1$NKE.idx <- (1/num.sec)*(ew.y1$NKE)


ew.y1[c(1:3, nrow(ew.y1)), ]



#### INFOTECH
y1.val.infotech <- data.frame(rowSums(ew.y1[,(ncol(ew.y1)-num.sec+1-8):(ncol(ew.y1)-8)]))
y1.val.infotech[c(1:3,nrow(y1.val.infotech)),]


names(y1.val.infotech) <- paste("InfoTech.val")


y1.val.infotech$date <- ew.y1$date
y1.val.infotech[c(1:3,nrow(y1.val.infotech)),]
y2.inv.infotech <- y1.val.infotech[nrow(y1.val.infotech),1]
y2.inv.infotech

#### FINANCIAL
y1.val.Fin <- data.frame(rowSums(ew.y1[,(ncol(ew.y1)-num.sec+1-4):(ncol(ew.y1)-4)]))
y1.val.Fin[c(1:3,nrow(y1.val.Fin)),]


names(y1.val.Fin) <- paste("Financial.val")


y1.val.Fin$date <- ew.y1$date
y1.val.Fin[c(1:3,nrow(y1.val.Fin)),]
y2.inv.Fin <- y1.val.Fin[nrow(y1.val.Fin),1]
y2.inv.Fin


#### CONSUMER
y1.val.Cons <- data.frame(rowSums(ew.y1[,(ncol(ew.y1)-num.sec+1):(ncol(ew.y1))]))
y1.val.Cons[c(1:3,nrow(y1.val.Cons)),]


names(y1.val.Cons) <- paste("Consumer.val")


y1.val.Cons$date <- ew.y1$date
y1.val.Cons[c(1:3,nrow(y1.val.Cons)),]
y2.inv.Cons <- y1.val.Cons[nrow(y1.val.Cons),1]
y2.inv.Cons





```

```{r}
##year 2 - 2016

ew.y2 <- subset(ewport,
                ewport$date >= as.Date("2016-01-01") &
                ewport$date <= as.Date("2016-12-31"))
# ew.y2[c(1:3,nrow(ew.y2)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y2[columns_to_cumprod2] <- cumprod(ew.y2[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y2$NVDA.idx <- (y2.inv.infotech/num.sec)*(ew.y2$NVDA)  ##(q1.inv/num.sec)
ew.y2$MSFT.idx <- (y2.inv.infotech/num.sec)*(ew.y2$MSFT)
ew.y2$AAPL.idx <- (y2.inv.infotech/num.sec)*(ew.y2$AAPL)
ew.y2$NFLX.idx <- (y2.inv.infotech/num.sec)*(ew.y2$NFLX)

ew.y2$BRK_B.idx <- (y2.inv.Fin/num.sec)*(ew.y2$BRK_B)
ew.y2$JPM.idx <- (y2.inv.Fin/num.sec)*(ew.y2$JPM)
ew.y2$C.idx <- (y2.inv.Fin/num.sec)*(ew.y2$C)
ew.y2$BLK.idx <- (y2.inv.Fin/num.sec)*(ew.y2$BLK)

ew.y2$MCD.idx <- (y2.inv.Cons/num.sec)*(ew.y2$MCD)
ew.y2$SKX.idx <- (y2.inv.Cons/num.sec)*(ew.y2$SKX)
ew.y2$SBUX.idx <- (y2.inv.Cons/num.sec)*(ew.y2$SBUX)
ew.y2$NKE.idx <- (y2.inv.Cons/num.sec)*(ew.y2$NKE)

# # ew.y2[c(1:3, nrow(ew.y2)), ]
# 
# y2.val <- data.frame(rowSums(ew.y2[,(ncol(ew.y2)-num.sec+1):ncol(ew.y2)]))
# # y2.val[c(1:3,nrow(y2.val)),]
# names(y2.val) <- paste("port.val")
# y2.val$date <- ew.y2$date
# y2.val[c(1:3,nrow(y2.val)),]
# 
# 
# y3.inv <- y2.val[nrow(y2.val),1]
# y3.inv






#### INFOTECH
y2.val.infotech <- data.frame(rowSums(ew.y2[,(ncol(ew.y2)-num.sec+1-8):(ncol(ew.y2)-8)]))
y2.val.infotech[c(1:3,nrow(y2.val.infotech)),]


names(y2.val.infotech) <- paste("InfoTech.val")


y2.val.infotech$date <- ew.y2$date
y2.val.infotech[c(1:3,nrow(y2.val.infotech)),]
y3.inv.infotech <- y2.val.infotech[nrow(y2.val.infotech),1]
y3.inv.infotech

#### FINANCIAL
y2.val.Fin <- data.frame(rowSums(ew.y2[,(ncol(ew.y2)-num.sec+1-4):(ncol(ew.y2)-4)]))
y2.val.Fin[c(1:3,nrow(y2.val.Fin)),]


names(y2.val.Fin) <- paste("Financial.val")


y2.val.Fin$date <- ew.y2$date
y2.val.Fin[c(1:3,nrow(y2.val.Fin)),]
y3.inv.Fin <- y2.val.Fin[nrow(y2.val.Fin),1]
y3.inv.Fin


#### CONSUMER
y2.val.Cons <- data.frame(rowSums(ew.y2[,(ncol(ew.y2)-num.sec+1):(ncol(ew.y2))]))
y2.val.Cons[c(1:3,nrow(y2.val.Cons)),]


names(y2.val.Cons) <- paste("Consumer.val")


y2.val.Cons$date <- ew.y2$date
y2.val.Cons[c(1:3,nrow(y2.val.Cons)),]
y3.inv.Cons <- y2.val.Cons[nrow(y2.val.Cons),1]
y3.inv.Cons


```


```{r}
##year 3 - 2017

ew.y3 <- subset(ewport,
                ewport$date >= as.Date("2017-01-01") &
                ewport$date <= as.Date("2017-12-31"))
# ew.y3[c(1:3,nrow(ew.y3)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y3[columns_to_cumprod2] <- cumprod(ew.y3[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y3$NVDA.idx <- (y3.inv.infotech/num.sec)*(ew.y3$NVDA)  ##(q1.inv/num.sec)
ew.y3$MSFT.idx <- (y3.inv.infotech/num.sec)*(ew.y3$MSFT)
ew.y3$AAPL.idx <- (y3.inv.infotech/num.sec)*(ew.y3$AAPL)
ew.y3$NFLX.idx <- (y3.inv.infotech/num.sec)*(ew.y3$NFLX)

ew.y3$BRK_B.idx <- (y3.inv.Fin/num.sec)*(ew.y3$BRK_B)
ew.y3$JPM.idx <- (y3.inv.Fin/num.sec)*(ew.y3$JPM)
ew.y3$C.idx <- (y3.inv.Fin/num.sec)*(ew.y3$C)
ew.y3$BLK.idx <- (y3.inv.Fin/num.sec)*(ew.y3$BLK)

ew.y3$MCD.idx <- (y3.inv.Cons/num.sec)*(ew.y3$MCD)
ew.y3$SKX.idx <- (y3.inv.Cons/num.sec)*(ew.y3$SKX)
ew.y3$SBUX.idx <- (y3.inv.Cons/num.sec)*(ew.y3$SBUX)
ew.y3$NKE.idx <- (y3.inv.Cons/num.sec)*(ew.y3$NKE)


##CUMPROD

#### INFOTECH
y3.val.infotech <- data.frame(rowSums(ew.y3[,(ncol(ew.y3)-num.sec+1-8):(ncol(ew.y3)-8)]))
y3.val.infotech[c(1:3,nrow(y3.val.infotech)),]


names(y3.val.infotech) <- paste("InfoTech.val")


y3.val.infotech$date <- ew.y3$date
y3.val.infotech[c(1:3,nrow(y3.val.infotech)),]
y4.inv.infotech <- y3.val.infotech[nrow(y3.val.infotech),1]
y4.inv.infotech

#### FINANCIAL
y3.val.Fin <- data.frame(rowSums(ew.y3[,(ncol(ew.y3)-num.sec+1-4):(ncol(ew.y3)-4)]))
y3.val.Fin[c(1:3,nrow(y3.val.Fin)),]


names(y3.val.Fin) <- paste("Financial.val")


y3.val.Fin$date <- ew.y3$date
y3.val.Fin[c(1:3,nrow(y3.val.Fin)),]
y4.inv.Fin <- y3.val.Fin[nrow(y3.val.Fin),1]
y4.inv.Fin


#### CONSUMER
y3.val.Cons <- data.frame(rowSums(ew.y3[,(ncol(ew.y3)-num.sec+1):(ncol(ew.y3))]))
y3.val.Cons[c(1:3,nrow(y3.val.Cons)),]


names(y3.val.Cons) <- paste("Consumer.val")


y3.val.Cons$date <- ew.y3$date
y3.val.Cons[c(1:3,nrow(y3.val.Cons)),]
y4.inv.Cons <- y3.val.Cons[nrow(y3.val.Cons),1]
y4.inv.Cons


```


```{r}
##year 4 - 2018

ew.y4 <- subset(ewport,
                ewport$date >= as.Date("2018-01-01") &
                ewport$date <= as.Date("2018-12-31"))
# ew.y4[c(1:3,nrow(ew.y4)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y4[columns_to_cumprod2] <- cumprod(ew.y4[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y4$NVDA.idx <- (y4.inv.infotech/num.sec)*(ew.y4$NVDA)  ##(q1.inv/num.sec)
ew.y4$MSFT.idx <- (y4.inv.infotech/num.sec)*(ew.y4$MSFT)
ew.y4$AAPL.idx <- (y4.inv.infotech/num.sec)*(ew.y4$AAPL)
ew.y4$NFLX.idx <- (y4.inv.infotech/num.sec)*(ew.y4$NFLX)

ew.y4$BRK_B.idx <- (y4.inv.Fin/num.sec)*(ew.y4$BRK_B)
ew.y4$JPM.idx <- (y4.inv.Fin/num.sec)*(ew.y4$JPM)
ew.y4$C.idx <- (y4.inv.Fin/num.sec)*(ew.y4$C)
ew.y4$BLK.idx <- (y4.inv.Fin/num.sec)*(ew.y4$BLK)

ew.y4$MCD.idx <- (y4.inv.Cons/num.sec)*(ew.y4$MCD)
ew.y4$SKX.idx <- (y4.inv.Cons/num.sec)*(ew.y4$SKX)
ew.y4$SBUX.idx <- (y4.inv.Cons/num.sec)*(ew.y4$SBUX)
ew.y4$NKE.idx <- (y4.inv.Cons/num.sec)*(ew.y4$NKE)


##CUMPROD

#### INFOTECH
y4.val.infotech <- data.frame(rowSums(ew.y4[,(ncol(ew.y4)-num.sec+1-8):(ncol(ew.y4)-8)]))
y4.val.infotech[c(1:3,nrow(y4.val.infotech)),]


names(y4.val.infotech) <- paste("InfoTech.val")


y4.val.infotech$date <- ew.y4$date
y4.val.infotech[c(1:3,nrow(y4.val.infotech)),]
y5.inv.infotech <- y4.val.infotech[nrow(y4.val.infotech),1]
y5.inv.infotech

#### FINANCIAL
y4.val.Fin <- data.frame(rowSums(ew.y4[,(ncol(ew.y4)-num.sec+1-4):(ncol(ew.y4)-4)]))
y4.val.Fin[c(1:3,nrow(y4.val.Fin)),]


names(y4.val.Fin) <- paste("Financial.val")


y4.val.Fin$date <- ew.y4$date
y4.val.Fin[c(1:3,nrow(y4.val.Fin)),]
y5.inv.Fin <- y4.val.Fin[nrow(y4.val.Fin),1]
y5.inv.Fin


#### CONSUMER
y4.val.Cons <- data.frame(rowSums(ew.y4[,(ncol(ew.y4)-num.sec+1):(ncol(ew.y4))]))
y4.val.Cons[c(1:3,nrow(y4.val.Cons)),]


names(y4.val.Cons) <- paste("Consumer.val")


y4.val.Cons$date <- ew.y4$date
y4.val.Cons[c(1:3,nrow(y4.val.Cons)),]
y5.inv.Cons <- y4.val.Cons[nrow(y4.val.Cons),1]
y5.inv.Cons


```

```{r}
##year 5 - 2019

ew.y5 <- subset(ewport,
                ewport$date >= as.Date("2019-01-01") &
                ewport$date <= as.Date("2019-12-31"))
# ew.y5[c(1:3,nrow(ew.y5)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y5[columns_to_cumprod2] <- cumprod(ew.y5[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y5$NVDA.idx <- (y5.inv.infotech/num.sec)*(ew.y5$NVDA)  ##(q1.inv/num.sec)
ew.y5$MSFT.idx <- (y5.inv.infotech/num.sec)*(ew.y5$MSFT)
ew.y5$AAPL.idx <- (y5.inv.infotech/num.sec)*(ew.y5$AAPL)
ew.y5$NFLX.idx <- (y5.inv.infotech/num.sec)*(ew.y5$NFLX)

ew.y5$BRK_B.idx <- (y5.inv.Fin/num.sec)*(ew.y5$BRK_B)
ew.y5$JPM.idx <- (y5.inv.Fin/num.sec)*(ew.y5$JPM)
ew.y5$C.idx <- (y5.inv.Fin/num.sec)*(ew.y5$C)
ew.y5$BLK.idx <- (y5.inv.Fin/num.sec)*(ew.y5$BLK)

ew.y5$MCD.idx <- (y5.inv.Cons/num.sec)*(ew.y5$MCD)
ew.y5$SKX.idx <- (y5.inv.Cons/num.sec)*(ew.y5$SKX)
ew.y5$SBUX.idx <- (y5.inv.Cons/num.sec)*(ew.y5$SBUX)
ew.y5$NKE.idx <- (y5.inv.Cons/num.sec)*(ew.y5$NKE)


##CUMPROD

#### INFOTECH
y5.val.infotech <- data.frame(rowSums(ew.y5[,(ncol(ew.y5)-num.sec+1-8):(ncol(ew.y5)-8)]))
y5.val.infotech[c(1:3,nrow(y5.val.infotech)),]


names(y5.val.infotech) <- paste("InfoTech.val")


y5.val.infotech$date <- ew.y5$date
y5.val.infotech[c(1:3,nrow(y5.val.infotech)),]
y6.inv.infotech <- y5.val.infotech[nrow(y5.val.infotech),1]
y6.inv.infotech

#### FINANCIAL
y5.val.Fin <- data.frame(rowSums(ew.y5[,(ncol(ew.y5)-num.sec+1-4):(ncol(ew.y5)-4)]))
y5.val.Fin[c(1:3,nrow(y5.val.Fin)),]


names(y5.val.Fin) <- paste("Financial.val")


y5.val.Fin$date <- ew.y5$date
y5.val.Fin[c(1:3,nrow(y5.val.Fin)),]
y6.inv.Fin <- y5.val.Fin[nrow(y5.val.Fin),1]
y6.inv.Fin


#### CONSUMER
y5.val.Cons <- data.frame(rowSums(ew.y5[,(ncol(ew.y5)-num.sec+1):(ncol(ew.y5))]))
y5.val.Cons[c(1:3,nrow(y5.val.Cons)),]


names(y5.val.Cons) <- paste("Consumer.val")


y5.val.Cons$date <- ew.y5$date
y5.val.Cons[c(1:3,nrow(y5.val.Cons)),]
y6.inv.Cons <- y5.val.Cons[nrow(y5.val.Cons),1]
y6.inv.Cons


```
```{r}
##year 6 - 2020

ew.y6 <- subset(ewport,
                ewport$date >= as.Date("2020-01-01") &
                ewport$date <= as.Date("2020-12-31"))
# ew.y6[c(1:3,nrow(ew.y6)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y6[columns_to_cumprod2] <- cumprod(ew.y6[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y6$NVDA.idx <- (y6.inv.infotech/num.sec)*(ew.y6$NVDA)  ##(q1.inv/num.sec)
ew.y6$MSFT.idx <- (y6.inv.infotech/num.sec)*(ew.y6$MSFT)
ew.y6$AAPL.idx <- (y6.inv.infotech/num.sec)*(ew.y6$AAPL)
ew.y6$NFLX.idx <- (y6.inv.infotech/num.sec)*(ew.y6$NFLX)

ew.y6$BRK_B.idx <- (y6.inv.Fin/num.sec)*(ew.y6$BRK_B)
ew.y6$JPM.idx <- (y6.inv.Fin/num.sec)*(ew.y6$JPM)
ew.y6$C.idx <- (y6.inv.Fin/num.sec)*(ew.y6$C)
ew.y6$BLK.idx <- (y6.inv.Fin/num.sec)*(ew.y6$BLK)

ew.y6$MCD.idx <- (y6.inv.Cons/num.sec)*(ew.y6$MCD)
ew.y6$SKX.idx <- (y6.inv.Cons/num.sec)*(ew.y6$SKX)
ew.y6$SBUX.idx <- (y6.inv.Cons/num.sec)*(ew.y6$SBUX)
ew.y6$NKE.idx <- (y6.inv.Cons/num.sec)*(ew.y6$NKE)


##CUMPROD

#### INFOTECH
y6.val.infotech <- data.frame(rowSums(ew.y6[,(ncol(ew.y6)-num.sec+1-8):(ncol(ew.y6)-8)]))
y6.val.infotech[c(1:3,nrow(y6.val.infotech)),]


names(y6.val.infotech) <- paste("InfoTech.val")


y6.val.infotech$date <- ew.y6$date
y6.val.infotech[c(1:3,nrow(y6.val.infotech)),]
y7.inv.infotech <- y6.val.infotech[nrow(y6.val.infotech),1]
y7.inv.infotech

#### FINANCIAL
y6.val.Fin <- data.frame(rowSums(ew.y6[,(ncol(ew.y6)-num.sec+1-4):(ncol(ew.y6)-4)]))
y6.val.Fin[c(1:3,nrow(y6.val.Fin)),]


names(y6.val.Fin) <- paste("Financial.val")


y6.val.Fin$date <- ew.y6$date
y6.val.Fin[c(1:3,nrow(y6.val.Fin)),]
y7.inv.Fin <- y6.val.Fin[nrow(y6.val.Fin),1]
y7.inv.Fin


#### CONSUMER
y6.val.Cons <- data.frame(rowSums(ew.y6[,(ncol(ew.y6)-num.sec+1):(ncol(ew.y6))]))
y6.val.Cons[c(1:3,nrow(y6.val.Cons)),]


names(y6.val.Cons) <- paste("Consumer.val")


y6.val.Cons$date <- ew.y6$date
y6.val.Cons[c(1:3,nrow(y6.val.Cons)),]
y7.inv.Cons <- y6.val.Cons[nrow(y6.val.Cons),1]
y7.inv.Cons


```
```{r}
##year 7 - 2021

ew.y7 <- subset(ewport,
                ewport$date >= as.Date("2021-01-01") &
                ewport$date <= as.Date("2021-12-31"))
# ew.y7[c(1:3,nrow(ew.y7)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y7[columns_to_cumprod2] <- cumprod(ew.y7[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y7$NVDA.idx <- (y7.inv.infotech/num.sec)*(ew.y7$NVDA)  ##(q1.inv/num.sec)
ew.y7$MSFT.idx <- (y7.inv.infotech/num.sec)*(ew.y7$MSFT)
ew.y7$AAPL.idx <- (y7.inv.infotech/num.sec)*(ew.y7$AAPL)
ew.y7$NFLX.idx <- (y7.inv.infotech/num.sec)*(ew.y7$NFLX)

ew.y7$BRK_B.idx <- (y7.inv.Fin/num.sec)*(ew.y7$BRK_B)
ew.y7$JPM.idx <- (y7.inv.Fin/num.sec)*(ew.y7$JPM)
ew.y7$C.idx <- (y7.inv.Fin/num.sec)*(ew.y7$C)
ew.y7$BLK.idx <- (y7.inv.Fin/num.sec)*(ew.y7$BLK)

ew.y7$MCD.idx <- (y7.inv.Cons/num.sec)*(ew.y7$MCD)
ew.y7$SKX.idx <- (y7.inv.Cons/num.sec)*(ew.y7$SKX)
ew.y7$SBUX.idx <- (y7.inv.Cons/num.sec)*(ew.y7$SBUX)
ew.y7$NKE.idx <- (y7.inv.Cons/num.sec)*(ew.y7$NKE)


##CUMPROD

#### INFOTECH
y7.val.infotech <- data.frame(rowSums(ew.y7[,(ncol(ew.y7)-num.sec+1-8):(ncol(ew.y7)-8)]))
y7.val.infotech[c(1:3,nrow(y7.val.infotech)),]


names(y7.val.infotech) <- paste("InfoTech.val")


y7.val.infotech$date <- ew.y7$date
y7.val.infotech[c(1:3,nrow(y7.val.infotech)),]
y8.inv.infotech <- y7.val.infotech[nrow(y7.val.infotech),1]
y8.inv.infotech

#### FINANCIAL
y7.val.Fin <- data.frame(rowSums(ew.y7[,(ncol(ew.y7)-num.sec+1-4):(ncol(ew.y7)-4)]))
y7.val.Fin[c(1:3,nrow(y7.val.Fin)),]


names(y7.val.Fin) <- paste("Financial.val")


y7.val.Fin$date <- ew.y7$date
y7.val.Fin[c(1:3,nrow(y7.val.Fin)),]
y8.inv.Fin <- y7.val.Fin[nrow(y7.val.Fin),1]
y8.inv.Fin


#### CONSUMER
y7.val.Cons <- data.frame(rowSums(ew.y7[,(ncol(ew.y7)-num.sec+1):(ncol(ew.y7))]))
y7.val.Cons[c(1:3,nrow(y7.val.Cons)),]


names(y7.val.Cons) <- paste("Consumer.val")


y7.val.Cons$date <- ew.y7$date
y7.val.Cons[c(1:3,nrow(y7.val.Cons)),]
y8.inv.Cons <- y7.val.Cons[nrow(y7.val.Cons),1]
y8.inv.Cons


```

```{r}
##year 8 - 2022

ew.y8 <- subset(ewport,
                ewport$date >= as.Date("2022-01-01") &
                ewport$date <= as.Date("2022-12-31"))
# ew.y8[c(1:3,nrow(ew.y8)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y8[columns_to_cumprod2] <- cumprod(ew.y8[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y8$NVDA.idx <- (y8.inv.infotech/num.sec)*(ew.y8$NVDA)  ##(q1.inv/num.sec)
ew.y8$MSFT.idx <- (y8.inv.infotech/num.sec)*(ew.y8$MSFT)
ew.y8$AAPL.idx <- (y8.inv.infotech/num.sec)*(ew.y8$AAPL)
ew.y8$NFLX.idx <- (y8.inv.infotech/num.sec)*(ew.y8$NFLX)

ew.y8$BRK_B.idx <- (y8.inv.Fin/num.sec)*(ew.y8$BRK_B)
ew.y8$JPM.idx <- (y8.inv.Fin/num.sec)*(ew.y8$JPM)
ew.y8$C.idx <- (y8.inv.Fin/num.sec)*(ew.y8$C)
ew.y8$BLK.idx <- (y8.inv.Fin/num.sec)*(ew.y8$BLK)

ew.y8$MCD.idx <- (y8.inv.Cons/num.sec)*(ew.y8$MCD)
ew.y8$SKX.idx <- (y8.inv.Cons/num.sec)*(ew.y8$SKX)
ew.y8$SBUX.idx <- (y8.inv.Cons/num.sec)*(ew.y8$SBUX)
ew.y8$NKE.idx <- (y8.inv.Cons/num.sec)*(ew.y8$NKE)


##CUMPROD

#### INFOTECH
y8.val.infotech <- data.frame(rowSums(ew.y8[,(ncol(ew.y8)-num.sec+1-8):(ncol(ew.y8)-8)]))
y8.val.infotech[c(1:3,nrow(y8.val.infotech)),]


names(y8.val.infotech) <- paste("InfoTech.val")


y8.val.infotech$date <- ew.y8$date
y8.val.infotech[c(1:3,nrow(y8.val.infotech)),]
y9.inv.infotech <- y8.val.infotech[nrow(y8.val.infotech),1]
y9.inv.infotech

#### FINANCIAL
y8.val.Fin <- data.frame(rowSums(ew.y8[,(ncol(ew.y8)-num.sec+1-4):(ncol(ew.y8)-4)]))
y8.val.Fin[c(1:3,nrow(y8.val.Fin)),]


names(y8.val.Fin) <- paste("Financial.val")


y8.val.Fin$date <- ew.y8$date
y8.val.Fin[c(1:3,nrow(y8.val.Fin)),]
y9.inv.Fin <- y8.val.Fin[nrow(y8.val.Fin),1]
y9.inv.Fin


#### CONSUMER
y8.val.Cons <- data.frame(rowSums(ew.y8[,(ncol(ew.y8)-num.sec+1):(ncol(ew.y8))]))
y8.val.Cons[c(1:3,nrow(y8.val.Cons)),]


names(y8.val.Cons) <- paste("Consumer.val")


y8.val.Cons$date <- ew.y8$date
y8.val.Cons[c(1:3,nrow(y8.val.Cons)),]
y9.inv.Cons <- y8.val.Cons[nrow(y8.val.Cons),1]
y9.inv.Cons


```
```{r}
##year 8 - 2023

ew.y9 <- subset(ewport,
                ewport$date >= as.Date("2023-01-01") &
                ewport$date <= as.Date("2023-12-31"))
# ew.y9[c(1:3,nrow(ew.y9)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y9[columns_to_cumprod2] <- cumprod(ew.y9[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y9$NVDA.idx <- (y9.inv.infotech/num.sec)*(ew.y9$NVDA)  ##(q1.inv/num.sec)
ew.y9$MSFT.idx <- (y9.inv.infotech/num.sec)*(ew.y9$MSFT)
ew.y9$AAPL.idx <- (y9.inv.infotech/num.sec)*(ew.y9$AAPL)
ew.y9$NFLX.idx <- (y9.inv.infotech/num.sec)*(ew.y9$NFLX)

ew.y9$BRK_B.idx <- (y9.inv.Fin/num.sec)*(ew.y9$BRK_B)
ew.y9$JPM.idx <- (y9.inv.Fin/num.sec)*(ew.y9$JPM)
ew.y9$C.idx <- (y9.inv.Fin/num.sec)*(ew.y9$C)
ew.y9$BLK.idx <- (y9.inv.Fin/num.sec)*(ew.y9$BLK)

ew.y9$MCD.idx <- (y9.inv.Cons/num.sec)*(ew.y9$MCD)
ew.y9$SKX.idx <- (y9.inv.Cons/num.sec)*(ew.y9$SKX)
ew.y9$SBUX.idx <- (y9.inv.Cons/num.sec)*(ew.y9$SBUX)
ew.y9$NKE.idx <- (y9.inv.Cons/num.sec)*(ew.y9$NKE)


##CUMPROD

#### INFOTECH
y9.val.infotech <- data.frame(rowSums(ew.y9[,(ncol(ew.y9)-num.sec+1-8):(ncol(ew.y9)-8)]))
y9.val.infotech[c(1:3,nrow(y9.val.infotech)),]


names(y9.val.infotech) <- paste("InfoTech.val")


y9.val.infotech$date <- ew.y9$date
y9.val.infotech[c(1:3,nrow(y9.val.infotech)),]
y10.inv.infotech <- y9.val.infotech[nrow(y9.val.infotech),1]
y10.inv.infotech

#### FINANCIAL
y9.val.Fin <- data.frame(rowSums(ew.y9[,(ncol(ew.y9)-num.sec+1-4):(ncol(ew.y9)-4)]))
y9.val.Fin[c(1:3,nrow(y9.val.Fin)),]


names(y9.val.Fin) <- paste("Financial.val")


y9.val.Fin$date <- ew.y9$date
y9.val.Fin[c(1:3,nrow(y9.val.Fin)),]
y10.inv.Fin <- y9.val.Fin[nrow(y9.val.Fin),1]
y10.inv.Fin


#### CONSUMER
y9.val.Cons <- data.frame(rowSums(ew.y9[,(ncol(ew.y9)-num.sec+1):(ncol(ew.y9))]))
y9.val.Cons[c(1:3,nrow(y9.val.Cons)),]


names(y9.val.Cons) <- paste("Consumer.val")


y9.val.Cons$date <- ew.y9$date
y9.val.Cons[c(1:3,nrow(y9.val.Cons)),]
y10.inv.Cons <- y9.val.Cons[nrow(y9.val.Cons),1]
y10.inv.Cons


```

```{r}
ew.portval.infotech <- rbind(y1.val.infotech,y2.val.infotech,y3.val.infotech,y4.val.infotech,y5.val.infotech,y6.val.infotech,y7.val.infotech,y8.val.infotech,y9.val.infotech)
ew.portval.infotech[c(1:3,nrow(ew.portval.infotech)),]

ew.portval.Fin <- rbind(y1.val.Fin,y2.val.Fin,y3.val.Fin,y4.val.Fin,y5.val.Fin,y6.val.Fin,y7.val.Fin,y8.val.Fin,y9.val.Fin)
ew.portval.Fin[c(1:3,nrow(ew.portval.Fin)),]

ew.portval.Cons <- rbind(y1.val.Cons,y2.val.Cons,y3.val.Cons,y4.val.Cons,y5.val.Cons,y6.val.Cons,y7.val.Cons,y8.val.Cons,y9.val.Cons)
ew.portval.Cons[c(1:3,nrow(ew.portval.Cons)),]



ew.portval<-cbind(ew.portval.infotech$InfoTech.val,ew.portval.Fin$Financial.val,ew.portval.Cons)
names(ew.portval) <- paste(c("InfoTech.val","Financial.val","Consumer.val","date"))

ew.portval[c(1:3,nrow(ew.portval)),]
```


```{r}
## Find the index of the "date" column
date_col_index <- which(colnames(ew.portval) == "date")

# Rearrange columns to bring "date" to the first position
ew.portval <- ew.portval[, c(date_col_index, setdiff(1:ncol(ew.portval), date_col_index))]

# Print the first few rows to verify the result
ew.portval[c(1:3,nrow(ew.portval)),]
```


Saving benchmark portfolio returns into a CSV file

# port2.xts <-xts(ew.portval[,2:4],order.by=ew.portval[,1])
# 
# port2.xts$Lag.InfoTech <- Lag(port2.xts$InfoTech.val,k=1)
# port2.xts$Lag.Financial <- Lag(port2.xts$Financial.val,k=1)
# port2.xts$Lag.Consumer <- Lag(port2.xts$Consumer.val,k=1)
# 
# # # port2.xts$Lag.EW <- Lag(port2.xts$EW.cum,k=1)
# # 
# # port.xts$VW.ret <- port.xts$VW.cum/port.xts$Lag.VW-1
# # port.xts$EW.ret <- port.xts$EW.cum/port.xts$Lag.EW-1
# # 
# Port.Ret <- port2.xts #[,c(1,2,5,6)]
# Port.Ret[c(1:3,nrow(Port.Ret)),]
# # 




```{r}
csv1.port <- cbind(data.frame(index(ew.portval)),data.frame(ew.portval))
names(csv1.port)[1]<- paste("date")
csv1.port[c(1:3,nrow(csv1.port)),]

```


```{r}
rownames(csv1.port) <- seq(1:nrow(csv1.port))
csv1.port[c(1:3,nrow(csv1.port)),]

```


```{r}
write.csv(csv1.port,"EW Portfolio Per Sector(Daily).csv")
```





















Calculate return time series 


```{r}



Idx <- interpNA(ew.portval[, -1], method = "before")
R <- returnseries(Idx, method = "discrete", trim = TRUE)
V <- cov(R)
head(Idx)
head(R)
V
```
```{r}
GMVw <- Weights(PGMV(R))
MDPw <- Weights(PMD(R))
MTDw <- Weights(PMTD(R))
ERCw <- Weights(PERC(V))
```
The weights are then collected in the matrix object W.

This object is then used in the call to the apply() function to determine the marginal risk contributions for each of the four optimal weight vectors.
```{r}
W <- cbind(GMVw, MDPw, MTDw, ERCw)
MRC <- apply(W, 2, mrc, Sigma = V)
rownames(MRC) <- colnames(Idx)
colnames(MRC) <- c("GMV", "MDP", "MTD", "ERC")


oldpar <- par(no.readonly = TRUE)
par(mfrow = c(2, 2))
dotchart(GMVw, xlim = c(0, 60), main = "GMV Allocation", pch = 19)
dotchart(MDPw - GMVw, xlim = c(-20, 20), main = "MDP vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
dotchart(MTDw - GMVw, xlim = c(-20, 20), main = "MTD vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
dotchart(ERCw - GMVw, xlim = c(-20, 20), main = "ERC vs. GMV",
         pch = 19)
abline(v = 0, col = "grey")
```
```{r}
Sector <- factor(rep(rownames(MRC), 4),
                 levels = sort(rownames(MRC)))
Port <- factor(rep(colnames(MRC), each = 3),
               levels = colnames(MRC))
MRCdf <- data.frame(MRC = c(MRC), Port, Sector)
dotplot(Sector ~ MRC | Port, groups = Port, data = MRCdf,
        xlab = "Percentages",
        main = "Marginal Risk Contributions by Sector per Portfolio",
        col = "black", pch = 19)

```













