---
title: "ANLY515_GroupProject_Saurabh v6 ARCH GARCH"
author: "Saurabh Shirish Prabhu"
date: '`r Sys.Date()`'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE)
dir.create(tempdir())
```

Importing data from Yahoo finance:

```{r}
getwd()
setwd('F:/a_Harrisburg_University_Academics/ANLY 515-51- A-2024Spring - Risk Modeling and Assessment/Final Project/Code')
getwd()
```
This section contains
Part A – Markowitz Mean-Variance Optimization
Part B – Suitable distributions for returns

Select two market sectors from the 11 sectors identified on this
reference o <https://www.bloomberg.com/markets/sectors>

Answer:

[1]Information Technology<br>

1.1 Semiconductors & Semiconductor Equipment: NVIDIA Corporation (NVDA)<br>
1.2 Software & Services: Microsoft Corporation (MSFT)<br>
1.3 Software & Services: Apple Inc. (AAPL)<br>
1.4 Software & Services: Netflix Inc. (NFLX)<br>


[2]Financials<br>

2.1 Insurance: Berkshire Hathaway Inc. (BRK.B)<br>
2.2 Banks: JPMorgan Chase & Co. (JPM)<br>
2.3 Banks: CitiGroup Inc. (C)<br>
2.4 Insurance: BlackRock Inc. (BLK)<br>



[3]Consumer Discretionary:<br>

3.1 Retailing: McDonald's Corporation (MCD)<br>
3.2 Consumer Durables & Apparel: Skechers U.S.A., Inc. (SKX)<br>
3.3 Retailing: Starbucks Corp. (SBUX) <br>
3.4 Consumer Durables & Apparel: Nike Inc. (NKE)



[4]Industrials: <br>

4.1 Capital Goods: Cummins Inc. (CMI)<br>
4.2 Capital Goods:Deere & Company (DE)<br>


References: <br>
[1]<https://stockanalysis.com/stocks/industry/><br>
[2]<https://medium.com/\@sil.soham/importing-and-visualising-stock-market-data-in-r-ac5a22e23cd><br>


Import all necessary libraries

```{r}
library(quantmod)
library(xts)
library(dplyr)
library(corrplot)


library(FRAPO)
library(readr)
library(timeSeries)
```

Load all stocks



• Confirm that there is no missing data<br> 
• Check the dimensions to
verify that the data covers 5 years<br>
```{r}

start <- as.Date("2014-12-31",format="%Y-%m-%d")
end <- as.Date("2023-12-31",format="%Y-%m-%d")

# Use getSymbols to retrieve the data

# [1]Information Technology
data.NVDA <- getSymbols("NVDA", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.MSFT <- getSymbols("MSFT", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.AAPL <- getSymbols("AAPL", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NFLX <- getSymbols("NFLX", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [2]Financials
data.BRK_B <- getSymbols("BRK-B", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.JPM <- getSymbols("JPM", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.C <- getSymbols("C", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.BLK <- getSymbols("BLK", src = "yahoo", from = start, to = end, auto.assign = FALSE)

# [3]Consumer Discretionary:
data.MCD <- getSymbols("MCD", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SKX <- getSymbols("SKX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.SBUX <- getSymbols("SBUX", src = "yahoo", from = start, to = end, auto.assign = FALSE)
data.NKE <- getSymbols("NKE", src = "yahoo", from = start, to = end, auto.assign = FALSE)
# Assign the class "xts" and "zoo" explicitly
# class(data.NVDA) <- c("xts", "zoo")
# Print the class of the assigned variable
class(data.NVDA)



names(data.BRK_B)
names(data.BRK_B) <- paste(c("BRK_B.Open","BRK_B.High","BRK_B.Low","BRK_B.Close","BRK_B.Volume","BRK_B.Adjusted"))
names(data.BRK_B)

```
```{r}
### Sector 1: Information Technology: MSFT and NVDA
Infotech.Adjusted.Prices <- data.NVDA$NVDA.Adjusted
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.MSFT$MSFT.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.AAPL$AAPL.Adjusted)
Infotech.Adjusted.Prices <-cbind(Infotech.Adjusted.Prices,data.NFLX$NFLX.Adjusted)
# Infotech.Adjusted.Prices[c(1:3,nrow(Infotech.Adjusted.Prices)),]




##########
### Sector 2: Financials: BRK_B and JPM
Financials.Adjusted.Prices <- data.BRK_B$BRK_B.Adjusted
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.JPM$JPM.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.C$C.Adjusted)
Financials.Adjusted.Prices <-cbind(Financials.Adjusted.Prices,data.BLK$BLK.Adjusted)
# Financials.Adjusted.Prices[c(1:3,nrow(Financials.Adjusted.Prices)),]



#########
### Sector 3: Consumer Discretionary: MCD and SKX
Consumer.Adjusted.Prices <- data.MCD$MCD.Adjusted
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SKX$SKX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.SBUX$SBUX.Adjusted)
Consumer.Adjusted.Prices <-cbind(Consumer.Adjusted.Prices,data.NKE$NKE.Adjusted)
# Consumer.Adjusted.Prices[c(1:3,nrow(Consumer.Adjusted.Prices)),]


########
### Entire portfolio
Portfolio.Adj.all <- cbind(Infotech.Adjusted.Prices,Financials.Adjusted.Prices,Consumer.Adjusted.Prices)
Portfolio.Adj.all[c(1:3,nrow(Portfolio.Adj.all)),]

str(Portfolio.Adj.all)
summary(Portfolio.Adj.all)
```
Individual Returns
```{r}
port.df <- data.frame(date = index(Portfolio.Adj.all), coredata(Portfolio.Adj.all))
port.df[c(1:3,nrow(port.df)),]


Port.rets <-port.df
date<-Port.rets$date
# str(date)

PortRet.price <- Port.rets[,-1]


attr(PortRet.price, 'time')<-date   ##add time attribute to dataset
# str(PortRet.price)

prc2ret <- function(x) Delt(x)


Port.rets.all <- apply(PortRet.price,2,function(x) {prc2ret(c(x))})



colnames(Port.rets.all) <- c(
                      "NVDA", "MSFT", "AAPL", "NFLX",
                      "BRK_B",  "JPM", "C",  "BLK",
                      "MCD",  "SKX", "SBUX",  "NKE"
                      )

## Add date column
Port.rets.all = data.frame(Port.rets.all)
Port.rets.all$date <- port.df$date

attr(Port.rets.all, 'time')<-date
head(Port.rets.all)


### reorder to get date in first column
# Get the index of the 'date' column
date_column_index <- which(names(Port.rets.all) == "date")

# Move 'date' column to the first position
new_order <- c(date_column_index, 1:(ncol(Port.rets.all)-1)[-date_column_index+1])

# Rearrange the columns of the data frame
Port.rets.df <- Port.rets.all[, new_order]
Port.rets.df <- Port.rets.df[-1,]
head(Port.rets.df)


ewport <-Port.rets.df[-1,]+1
head(ewport)

```

Create a vector of weights min variance portfolio


year 1 inv / returns
```{r}

### Year 1 

ew.y1<- subset(ewport,
                ewport$date >= as.Date("2014-12-31") &
                ewport$date <= as.Date("2015-12-31"))

ew.y1[1, 2:ncol(ew.y1)] <- 1

# Apply cumprod to selected columns
columns_to_cumprod <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")

ew.y1[columns_to_cumprod] <- cumprod(ew.y1[columns_to_cumprod])   ## Simplified previous code

# Select specific rows and columns
# ew.y1[c(1:3, nrow(ew.y1)), ]

num.sec = 12

ew.y1$NVDA.idx <- (1/num.sec)*(ew.y1$NVDA)  ##(q1.inv/num.sec)
ew.y1$MSFT.idx <- (1/num.sec)*(ew.y1$MSFT)
ew.y1$AAPL.idx <- (1/num.sec)*(ew.y1$AAPL)
ew.y1$NFLX.idx <- (1/num.sec)*(ew.y1$NFLX)

ew.y1$BRK_B.idx <- (1/num.sec)*(ew.y1$BRK_B)
ew.y1$JPM.idx <- (1/num.sec)*(ew.y1$JPM)
ew.y1$C.idx <- (1/num.sec)*(ew.y1$C)
ew.y1$BLK.idx <- (1/num.sec)*(ew.y1$BLK)

ew.y1$MCD.idx <- (1/num.sec)*(ew.y1$MCD)
ew.y1$SKX.idx <- (1/num.sec)*(ew.y1$SKX)
ew.y1$SBUX.idx <- (1/num.sec)*(ew.y1$SBUX)
ew.y1$NKE.idx <- (1/num.sec)*(ew.y1$NKE)


# ew.y1[c(1:3, nrow(ew.y1)), ]

y1.val <- data.frame(rowSums(ew.y1[,(ncol(ew.y1)-num.sec+1):ncol(ew.y1)]))
# y1.val[c(1:3,nrow(y1.val)),]


names(y1.val) <- paste("port.val")
y1.val$date <- ew.y1$date
# y1.val[c(1:3,nrow(y1.val)),]
y2.inv <- y1.val[nrow(y1.val),1]
# y2.inv

##year 2 - 2016

ew.y2 <- subset(ewport,
                ewport$date >= as.Date("2016-01-01") &
                ewport$date <= as.Date("2016-12-31"))
# ew.y2[c(1:3,nrow(ew.y2)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y2[columns_to_cumprod2] <- cumprod(ew.y2[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y2$NVDA.idx <- (y2.inv/num.sec)*(ew.y2$NVDA)  ##(q1.inv/num.sec)
ew.y2$MSFT.idx <- (y2.inv/num.sec)*(ew.y2$MSFT)
ew.y2$AAPL.idx <- (y2.inv/num.sec)*(ew.y2$AAPL)
ew.y2$NFLX.idx <- (y2.inv/num.sec)*(ew.y2$NFLX)

ew.y2$BRK_B.idx <- (y2.inv/num.sec)*(ew.y2$BRK_B)
ew.y2$JPM.idx <- (y2.inv/num.sec)*(ew.y2$JPM)
ew.y2$C.idx <- (y2.inv/num.sec)*(ew.y2$C)
ew.y2$BLK.idx <- (y2.inv/num.sec)*(ew.y2$BLK)

ew.y2$MCD.idx <- (y2.inv/num.sec)*(ew.y2$MCD)
ew.y2$SKX.idx <- (y2.inv/num.sec)*(ew.y2$SKX)
ew.y2$SBUX.idx <- (y2.inv/num.sec)*(ew.y2$SBUX)
ew.y2$NKE.idx <- (y2.inv/num.sec)*(ew.y2$NKE)

# ew.y2[c(1:3, nrow(ew.y2)), ]

y2.val <- data.frame(rowSums(ew.y2[,(ncol(ew.y2)-num.sec+1):ncol(ew.y2)]))
# y2.val[c(1:3,nrow(y2.val)),]
names(y2.val) <- paste("port.val")
y2.val$date <- ew.y2$date
# y2.val[c(1:3,nrow(y2.val)),]


y3.inv <- y2.val[nrow(y2.val),1]
# y3.inv


## Year 3 - 2017

ew.y3 <- subset(ewport,
                ewport$date >= as.Date("2017-01-01") &
                ewport$date <= as.Date("2017-12-31"))
# ew.y3[c(1:3,nrow(ew.y3)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y3[columns_to_cumprod2] <- cumprod(ew.y3[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y3$NVDA.idx <- (y3.inv/num.sec)*(ew.y3$NVDA)  ##(q1.inv/num.sec)
ew.y3$MSFT.idx <- (y3.inv/num.sec)*(ew.y3$MSFT)
ew.y3$AAPL.idx <- (y3.inv/num.sec)*(ew.y3$AAPL)
ew.y3$NFLX.idx <- (y3.inv/num.sec)*(ew.y3$NFLX)

ew.y3$BRK_B.idx <- (y3.inv/num.sec)*(ew.y3$BRK_B)
ew.y3$JPM.idx <- (y3.inv/num.sec)*(ew.y3$JPM)
ew.y3$C.idx <- (y3.inv/num.sec)*(ew.y3$C)
ew.y3$BLK.idx <- (y3.inv/num.sec)*(ew.y3$BLK)

ew.y3$MCD.idx <- (y3.inv/num.sec)*(ew.y3$MCD)
ew.y3$SKX.idx <- (y3.inv/num.sec)*(ew.y3$SKX)
ew.y3$SBUX.idx <- (y3.inv/num.sec)*(ew.y3$SBUX)
ew.y3$NKE.idx <- (y3.inv/num.sec)*(ew.y3$NKE)

# ew.y3[c(1:3, nrow(ew.y3)), ]

y3.val <- data.frame(rowSums(ew.y3[,(ncol(ew.y3)-num.sec+1):ncol(ew.y3)]))
# y3.val[c(1:3,nrow(y3.val)),]
names(y3.val) <- paste("port.val")
y3.val$date <- ew.y3$date
# y3.val[c(1:3,nrow(y3.val)),]

y4.inv <- y3.val[nrow(y3.val),1]
# y4.inv

## Year 4 -2018

ew.y4 <- subset(ewport,
                ewport$date >= as.Date("2018-01-01") &
                ewport$date <= as.Date("2018-12-31"))
# ew.y4[c(1:3,nrow(ew.y4)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y4[columns_to_cumprod2] <- cumprod(ew.y4[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y4$NVDA.idx <- (y4.inv/num.sec)*(ew.y4$NVDA)  ##(q1.inv/num.sec)
ew.y4$MSFT.idx <- (y4.inv/num.sec)*(ew.y4$MSFT)
ew.y4$AAPL.idx <- (y4.inv/num.sec)*(ew.y4$AAPL)
ew.y4$NFLX.idx <- (y4.inv/num.sec)*(ew.y4$NFLX)

ew.y4$BRK_B.idx <- (y4.inv/num.sec)*(ew.y4$BRK_B)
ew.y4$JPM.idx <- (y4.inv/num.sec)*(ew.y4$JPM)
ew.y4$C.idx <- (y4.inv/num.sec)*(ew.y4$C)
ew.y4$BLK.idx <- (y4.inv/num.sec)*(ew.y4$BLK)

ew.y4$MCD.idx <- (y4.inv/num.sec)*(ew.y4$MCD)
ew.y4$SKX.idx <- (y4.inv/num.sec)*(ew.y4$SKX)
ew.y4$SBUX.idx <- (y4.inv/num.sec)*(ew.y4$SBUX)
ew.y4$NKE.idx <- (y4.inv/num.sec)*(ew.y4$NKE)

# ew.y4[c(1:3, nrow(ew.y4)), ]

y4.val <- data.frame(rowSums(ew.y4[,(ncol(ew.y4)-num.sec+1):ncol(ew.y4)]))
# y4.val[c(1:3,nrow(y4.val)),]
names(y4.val) <- paste("port.val")
y4.val$date <- ew.y4$date
# y4.val[c(1:3,nrow(y4.val)),]

y5.inv <- y4.val[nrow(y4.val),1]
# y5.inv


## Year 5 -2019

ew.y5 <- subset(ewport,
                ewport$date >= as.Date("2019-01-01") &
                ewport$date <= as.Date("2019-12-31"))
# ew.y5[c(1:3,nrow(ew.y5)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y5[columns_to_cumprod2] <- cumprod(ew.y5[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y5$NVDA.idx <- (y5.inv/num.sec)*(ew.y5$NVDA)  ##(q1.inv/num.sec)
ew.y5$MSFT.idx <- (y5.inv/num.sec)*(ew.y5$MSFT)
ew.y5$AAPL.idx <- (y5.inv/num.sec)*(ew.y5$AAPL)
ew.y5$NFLX.idx <- (y5.inv/num.sec)*(ew.y5$NFLX)

ew.y5$BRK_B.idx <- (y5.inv/num.sec)*(ew.y5$BRK_B)
ew.y5$JPM.idx <- (y5.inv/num.sec)*(ew.y5$JPM)
ew.y5$C.idx <- (y5.inv/num.sec)*(ew.y5$C)
ew.y5$BLK.idx <- (y5.inv/num.sec)*(ew.y5$BLK)

ew.y5$MCD.idx <- (y5.inv/num.sec)*(ew.y5$MCD)
ew.y5$SKX.idx <- (y5.inv/num.sec)*(ew.y5$SKX)
ew.y5$SBUX.idx <- (y5.inv/num.sec)*(ew.y5$SBUX)
ew.y5$NKE.idx <- (y5.inv/num.sec)*(ew.y5$NKE)

# ew.y5[c(1:3, nrow(ew.y5)), ]

y5.val <- data.frame(rowSums(ew.y5[,(ncol(ew.y5)-num.sec+1):ncol(ew.y5)]))
# y5.val[c(1:3,nrow(y5.val)),]
names(y5.val) <- paste("port.val")
y5.val$date <- ew.y5$date
# y5.val[c(1:3,nrow(y5.val)),]

y6.inv <- y5.val[nrow(y5.val),1]
# y6.inv


## Year 6 -2020

ew.y6 <- subset(ewport,
                ewport$date >= as.Date("2020-01-01") &
                ewport$date <= as.Date("2020-12-31"))
# ew.y6[c(1:3,nrow(ew.y6)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y6[columns_to_cumprod2] <- cumprod(ew.y6[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y6$NVDA.idx <- (y6.inv/num.sec)*(ew.y6$NVDA)  ##(q1.inv/num.sec)
ew.y6$MSFT.idx <- (y6.inv/num.sec)*(ew.y6$MSFT)
ew.y6$AAPL.idx <- (y6.inv/num.sec)*(ew.y6$AAPL)
ew.y6$NFLX.idx <- (y6.inv/num.sec)*(ew.y6$NFLX)

ew.y6$BRK_B.idx <- (y6.inv/num.sec)*(ew.y6$BRK_B)
ew.y6$JPM.idx <- (y6.inv/num.sec)*(ew.y6$JPM)
ew.y6$C.idx <- (y6.inv/num.sec)*(ew.y6$C)
ew.y6$BLK.idx <- (y6.inv/num.sec)*(ew.y6$BLK)

ew.y6$MCD.idx <- (y6.inv/num.sec)*(ew.y6$MCD)
ew.y6$SKX.idx <- (y6.inv/num.sec)*(ew.y6$SKX)
ew.y6$SBUX.idx <- (y6.inv/num.sec)*(ew.y6$SBUX)
ew.y6$NKE.idx <- (y6.inv/num.sec)*(ew.y6$NKE)

# ew.y6[c(1:3, nrow(ew.y6)), ]

y6.val <- data.frame(rowSums(ew.y6[,(ncol(ew.y6)-num.sec+1):ncol(ew.y6)]))
# y6.val[c(1:3,nrow(y6.val)),]
names(y6.val) <- paste("port.val")
y6.val$date <- ew.y6$date
# y6.val[c(1:3,nrow(y6.val)),]

y7.inv <- y6.val[nrow(y6.val),1]
# y7.inv


## Year 7 -2021

ew.y7 <- subset(ewport,
                ewport$date >= as.Date("2021-01-01") &
                ewport$date <= as.Date("2021-12-31"))
# ew.y7[c(1:3,nrow(ew.y7)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y7[columns_to_cumprod2] <- cumprod(ew.y7[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y7$NVDA.idx <- (y7.inv/num.sec)*(ew.y7$NVDA)  ##(q1.inv/num.sec)
ew.y7$MSFT.idx <- (y7.inv/num.sec)*(ew.y7$MSFT)
ew.y7$AAPL.idx <- (y7.inv/num.sec)*(ew.y7$AAPL)
ew.y7$NFLX.idx <- (y7.inv/num.sec)*(ew.y7$NFLX)

ew.y7$BRK_B.idx <- (y7.inv/num.sec)*(ew.y7$BRK_B)
ew.y7$JPM.idx <- (y7.inv/num.sec)*(ew.y7$JPM)
ew.y7$C.idx <- (y7.inv/num.sec)*(ew.y7$C)
ew.y7$BLK.idx <- (y7.inv/num.sec)*(ew.y7$BLK)

ew.y7$MCD.idx <- (y7.inv/num.sec)*(ew.y7$MCD)
ew.y7$SKX.idx <- (y7.inv/num.sec)*(ew.y7$SKX)
ew.y7$SBUX.idx <- (y7.inv/num.sec)*(ew.y7$SBUX)
ew.y7$NKE.idx <- (y7.inv/num.sec)*(ew.y7$NKE)

# ew.y7[c(1:3, nrow(ew.y7)), ]

y7.val <- data.frame(rowSums(ew.y7[,(ncol(ew.y7)-num.sec+1):ncol(ew.y7)]))
# y7.val[c(1:3,nrow(y7.val)),]
names(y7.val) <- paste("port.val")
y7.val$date <- ew.y7$date
# y7.val[c(1:3,nrow(y7.val)),]

y8.inv <- y7.val[nrow(y7.val),1]
# y8.inv


## Year 8 -2022

ew.y8 <- subset(ewport,
                ewport$date >= as.Date("2022-01-01") &
                ewport$date <= as.Date("2022-12-31"))
# ew.y8[c(1:3,nrow(ew.y8)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y8[columns_to_cumprod2] <- cumprod(ew.y8[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y8$NVDA.idx <- (y8.inv/num.sec)*(ew.y8$NVDA)  ##(q1.inv/num.sec)
ew.y8$MSFT.idx <- (y8.inv/num.sec)*(ew.y8$MSFT)
ew.y8$AAPL.idx <- (y8.inv/num.sec)*(ew.y8$AAPL)
ew.y8$NFLX.idx <- (y8.inv/num.sec)*(ew.y8$NFLX)

ew.y8$BRK_B.idx <- (y8.inv/num.sec)*(ew.y8$BRK_B)
ew.y8$JPM.idx <- (y8.inv/num.sec)*(ew.y8$JPM)
ew.y8$C.idx <- (y8.inv/num.sec)*(ew.y8$C)
ew.y8$BLK.idx <- (y8.inv/num.sec)*(ew.y8$BLK)

ew.y8$MCD.idx <- (y8.inv/num.sec)*(ew.y8$MCD)
ew.y8$SKX.idx <- (y8.inv/num.sec)*(ew.y8$SKX)
ew.y8$SBUX.idx <- (y8.inv/num.sec)*(ew.y8$SBUX)
ew.y8$NKE.idx <- (y8.inv/num.sec)*(ew.y8$NKE)

# ew.y8[c(1:3, nrow(ew.y8)), ]

y8.val <- data.frame(rowSums(ew.y8[,(ncol(ew.y8)-num.sec+1):ncol(ew.y8)]))
# y8.val[c(1:3,nrow(y8.val)),]
names(y8.val) <- paste("port.val")
y8.val$date <- ew.y8$date
# y8.val[c(1:3,nrow(y8.val)),]

y9.inv <- y8.val[nrow(y8.val),1]
# y9.inv

## Year 9 -2023

ew.y9 <- subset(ewport,
                ewport$date >= as.Date("2023-01-01") &
                ewport$date <= as.Date("2023-12-31"))
# ew.y9[c(1:3,nrow(ew.y9)),]

columns_to_cumprod2 <- c("NVDA", "MSFT", "AAPL", "NFLX",
                        "BRK_B",  "JPM", "C",  "BLK",
                        "MCD",  "SKX", "SBUX",  "NKE")
ew.y9[columns_to_cumprod2] <- cumprod(ew.y9[columns_to_cumprod2])   ## Simplified previous code

# Select specific rows and columns

ew.y9$NVDA.idx <- (y9.inv/num.sec)*(ew.y9$NVDA)  ##(q1.inv/num.sec)
ew.y9$MSFT.idx <- (y9.inv/num.sec)*(ew.y9$MSFT)
ew.y9$AAPL.idx <- (y9.inv/num.sec)*(ew.y9$AAPL)
ew.y9$NFLX.idx <- (y9.inv/num.sec)*(ew.y9$NFLX)

ew.y9$BRK_B.idx <- (y9.inv/num.sec)*(ew.y9$BRK_B)
ew.y9$JPM.idx <- (y9.inv/num.sec)*(ew.y9$JPM)
ew.y9$C.idx <- (y9.inv/num.sec)*(ew.y9$C)
ew.y9$BLK.idx <- (y9.inv/num.sec)*(ew.y9$BLK)

ew.y9$MCD.idx <- (y9.inv/num.sec)*(ew.y9$MCD)
ew.y9$SKX.idx <- (y9.inv/num.sec)*(ew.y9$SKX)
ew.y9$SBUX.idx <- (y9.inv/num.sec)*(ew.y9$SBUX)
ew.y9$NKE.idx <- (y9.inv/num.sec)*(ew.y9$NKE)

# ew.y9[c(1:3, nrow(ew.y9)), ]

y9.val <- data.frame(rowSums(ew.y9[,(ncol(ew.y9)-num.sec+1):ncol(ew.y9)]))
# y9.val[c(1:3,nrow(y9.val)),]
names(y9.val) <- paste("port.val")
y9.val$date <- ew.y9$date
# y9.val[c(1:3,nrow(y9.val)),]

y10.inv <- y9.val[nrow(y9.val),1]
# y10.inv



```






```{r}
ew.portval <- rbind(y1.val,y2.val,y3.val,y4.val,y5.val,y6.val,y7.val,y8.val,y9.val)
ew.portval[c(1:3,nrow(ew.portval)),]


```

```{r}
# library(FRAPO)

ew.portval<-ew.portval[, c("date", "port.val")]

ew.portval$Return<-returnseries(ew.portval$port.val)

# library(timeSeries)
date<-ew.portval$date
str(date)

EW.ts<-timeSeries(ew.portval[,-1], charvec = date)
head(EW.ts)


plot(EW.ts)
```


```{r}

acf(EW.ts$Return, na.action = na.pass)
pacf(EW.ts$Return, na.action = na.pass)
acf(abs(EW.ts$Return), na.action = na.pass)
pacf(abs(EW.ts$Return), na.action = na.pass)
mean(EW.ts$Return, na.rm = TRUE)


```

ARIMA model
Load package: forecast

auto.arima: Returns best ARIMA model according to either the Akaike information criterion (AIC), AICc or Bayesian information criterion (BIC) or Schwarz information criterion value. The function conducts a search over possible model within the order constraints provided.

AICc: adds a correction term that converges to the AIC answer for large samples, but gives a more accurate answer for smaller samples

predict is a generic function for predictions from the results of various model fitting functions. The function invokes particular methods which depend on the class of the first argument

Time series prediction methods in package stats have an argument n.ahead specifying how many time steps ahead to predict

Value: A time series of predictions, or if se.fit = TRUE, a list with components pred, the predictions, and se, the estimated standard errors. Both components are time series.

```{r}
library(forecast)

EW.ts.arima<-auto.arima(EW.ts$Return)
class(EW.ts.arima)
predict(EW.ts.arima, n.ahead=2)
```
```{r}
str(EW.ts$Return)
EW.tsComp<-removeNA(EW.ts)
head(EW.tsComp)

```




```{r}
library(fGarch)
garchEW.ts<-garchFit(~garch(1,1), data=EW.tsComp[,2])
a<-coef(garchEW.ts)
b<-formula(garchEW.ts)
c<-volatility(garchEW.ts)

# c(a,b,c)
```

```{r}
a
b
c
```
```{r}
plot(c)
predict(garchEW.ts)
predict(garchEW.ts, n.ahead = 1)
```
GARCH fit using std distribution
cond.dist: a character string naming the desired conditional distribution. Valid values are “dnorm”, “dged”, “dstd”, “dsnorm”, “dsged”, “dsstd” and “QMLE”. The default value is the normal distribution.
```{r}

# garchEW.ts<-garchFit(~garch(1,1), data=EW.tsComp[,2])
garchEW.ts2<-garchFit(~garch(1,1), data=EW.tsComp[,2], cond.dist = "std")

```

EW.tsComp[,2]

```{r}
sigma <-  as.numeric(predict(garchEW.ts2, n.ahead = 1)[3])
df <- as.numeric(coef(garchEW.ts2)["shape"])
rand<-rt(100000, df=df)
hist(rand, breaks=100)
```




VaR
```{r}
quant<-qt(.01, df=df)
a<-sigma*quant #VaR
b<-max(tail(sort(rand, decreasing = T),1000))*sigma #VaR
a/b


```
ES
```{r}
d<-mean(tail(sort(rand, decreasing = T),1000))*sigma #ES
head(d/c)

```

EXAMPLE 2: 


```{r}
EW.ts_garch<-garchFit(~garch(1,1), data=EW.tsComp[,2],trace=FALSE)
predict(EW.ts_garch, n.ahead = 20, plot = TRUE)

```

The prediction is that the series will decrease slightly in the next few time periods. Note how the GARCH component of our model causes our confidence interval to widen significantly over the next few time intervals.



EXAMPLE 3: 

ACF in waves, and first spike of PACF is significant. AR(1) is recommended.

The second spike of PACF is significant too, but is just marginally significant. For model simplicity purpose, AR(1) is recommended.

Lower order GARCH such as GARCH(1,1),GARCH(2,1),and GARCH(1,2) are recommended for testing.


```{r}
library(astsa)
EW_ret <- EW.ts$Return[-1]

acf2(EW_ret)
```
ACF in waves, and first spike of PACF is significant. AR(1) is recommended.

The second spike of PACF is significant too. For model simplicity purpose, AR(1) is recommended.

Lower order GARCH such as GARCH(1,1),GARCH(2,1),and GARCH(1,2) are recommended for testing.


```{r}
summary(EW_ret.g1<-garchFit(~arma(1,0)+garch(1,1),data=EW_ret,cond.dist="std"))

```

You can also try other model like GARCH(1,2), but notice that beta2 in the final result is not significant. Thus, we still need to use GARCH(1,1)


```{r}
summary(EW_ret.g2<-garchFit(~arma(1,0)+garch(1,2),data=EW_ret,cond.dist="std"))
```

```{r}
predict(EW_ret.g1,n.ahead=10,plot = TRUE)
predict(EW_ret.g2,n.ahead=10,plot = TRUE)
```















